### 2015-11-22 paper/paper.tex
news

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{wrapfig}
\usepackage{afterpage}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{ulem}
\usepackage{multirow}

\def\B#1{\bm{#1}}
%\def\B#1{\mathbf{#1}}
\def\trans{\mathsf{T}}

%\renewcommand{\labelitemi}{--}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}{Remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Introducing region-network priors
to statistical estimators for fMRI data}

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\softmax}{softmax}
\DeclareMathOperator{\prox}{prox}
\DeclareMathOperator{\Prox}{Prox}
\DeclareMathOperator{\im}{im}

% macros from michael's .tex
\DeclareMathOperator{\dist}{dist} % The distance.
\DeclareMathOperator{\argmin}{argmin}
\DeclareMathOperator{\argmax}{argmax}
\DeclareMathOperator{\Id}{Id}
\DeclareMathOperator{\abs}{abs}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

\newcommand{\suggestadd}[1]{{\color{blue} #1}}
\newcommand{\suggestremove}[1]{{\color{red} \sout{#1}}}

% \nipsfinalcopy % Uncomment for camera-ready version
\nipsfinaltrue
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\author{Danilo Bzdok, Michael Eickenberg, Olivier Grisel,
  Bertrand Thirion,
  Ga\"el Varoquaux\\
  INRIA, Parietal team, Saclay, France\\
  CEA, Neurospin, Gif-sur-Yvette, France\\
  firstname.lastname@inria.fr}

\maketitle

\begin{abstract}
Imaging neuroscience links human behavior to aspects of brain
biology in ever-increasing datasets.

% OUR keywords
%\textbf{\\keywords}: curse of dimensionality; semi-supervised learning;
%fMRI; systems neuroscience

% official NIPS keywords
\textbf{\\keywords}: Brain Imaging, Functional Specialization,
Functional Integration,
Sparsity-inducing Norms, Systems Biology

\end{abstract}

\section{Introduction}
%
Many quantitative scientific domains underwent a
recent passage from the classical regime (i.e., "long data")  to
the high-dimensional regime (i.e., "wide data")
\citep{jordan2015massive}.
Also in the brain imaging domain,
many contemporary methods for acquiring brain signals yield
more variables per observation than
total observations available in a data sample.
This scenario challenges many statistical estimators from
classical statistics.
For instance,
linear regression models without any additional assumptions
yield an infinity of possible coefficients
and, thus, no solutions.
%
\textit{Sparsity} assumptions have consequently been
introduced and made many ill-posed estimation problems tractable
\cite{hastie2015statistical}.
Domain-specific structural knowledge can be imposed on the 
statistical estimation by preassuming that not all variables will be
equally important.
Sparsified statistical estimators have proven to yield
statistical relationships that can be
estimated, reproduced, and interpreted
\cite{giraud2014introduction}.
%
Yet, what would be the most pertinent neurobiological structure
that can successfully tackle the curse of dimensionality in
functional neuroimaging research?

abc
in current fMRI,
large-scale integration prevails over regional specialization,
although both notions are inextricably linked (Tononi et al., 1998).

It however remains elusive how brain regions and networks relate to
the organism's repertoire of mental operations.

Both regions and netoworks are
probably mechanistically relevant for emerging behavior.

The organization of the cerebral cortex into distinct modules may be described along several dimensions, most importantly, structure, connectivity and function. This conclusion was mainly derived from concurrent invasive examination of microstructure (histological preparation), connectivity (axonal tracing) and functional properties (single cell recordings) in same animals. 
Regarding the (micro-)structural dimension, early histological investigations into the microscopic heterogeneity of the human cerebral cortex have resulted in several detailed, though partially incongruent, anatomical maps (Brodmann 1909; Vogt and Vogt 1919). More recent advances in structural brain mapping have led to the development of observer-independent probabilistic cytoarchitectonic maps in stereotaxic space (Zilles and Amunts 2010). Moreover, the constantly growing field strength of fMRI scanners permits increasingly fin-grained microstructural recordings of the living human brain (Walters et al. 2007).
Regarding the connectional dimension, each cortical area is assumed to possess a unique set of input and output connections. Axonal connectivity between areas can be revealed by injection of a tracing dye that is transported to interconnected brain regions in animals. Axonal tracing studies in primates suggest that cortical areas tend to be connected hierarchically and reciprocally by feed-forward and feed-backward connections (Maunsell and van Essen 1983). Mapping connectivity patterns of a particular part of the cortex may thus allow identifying cortical areas by demonstrating differences between the connections of neighbouring grey matter locations.

Slightly reframing the concept of structure, connectivity and function as three pillars of brain organization, regional specialization of computational processes (i.e., function) can be conceived as being a consequence of both the local (micro-)structural and global connectional properties, as suggested by research in animals. That is, specialization of a particular function is not regarded as an intrinsic property of a brain region that is independent of its connectivity. Rather, input and output connectivity of an area in combination with the local "infrastructure" provided, e.g., by cyto- and chemoarchitecture, crucially determine what particular functions that area can perform (Passingham et al. 2002). Conversely, each particular cortical module is probably characterized by a unique set of input and output connections, which is supported by statistical analyses of cortical connectivity in the primate (Young 1993) and feline (Scannell et al. 1995) cortex. More generally, cortical modules and connections between those actually reflect functional segregation and functional integration, respectively (Friston 2002). In sum, a cortical module of functional specialization is likely to be defined by the intersection of regionally specific microstructure and connectivity patterns.

SPECIAL

Functional
specialization emphasizes that microanatomically distinguishable brain
regions realize distinct functions (Brodmann 1909; Zeki 1978). Indeed,
each microanatomical cortical area has a unique connectional, and thus
perhaps functional, profile in cats (Scannell et al. 1995), monkeys
(Young et al., 1993), and humans (Passingham et al., 2002).

Consistently, early lesion studies of induced behavioral
impairments in rats challenged the dogmatic localization of brain
function (Franz \& Lashley, 1917). Analogously in humans, even
extensive prefrontal lesions do not necessarily become apparant in
everyday behavior (Mesulam, 1990). An implicit preference for
functional specialization might therefore hinder consensus in
fundamental, still unresolved questions in neuroscience, such as the
relation between cognition and emotion (cf. Pessoa 2010, Overwalle
2011).

locally characteristic neuronal populations

INTEGRAL

Hebb, D. O. The Organization Of Behaviour (Wiley,
1949).

Only recently we have shifted the main interpretational focus
from single region to macroscopical networks
in systems neuroscience \citep{yuste2015}.

eemrgent properties emerge from the interaction

In
contrast, functional integration emphasizes that function is an
emergent property of collaborating areas. In fact, the higher the
hierarchical level, the more one cortical area connects to different
large-scale networks, which makes their boundaries less clear
(Yeo/Buckner 2011). The above network-network models naturally embody
functional integration as they capture (partially overlapping)
patterns of spatial coherence.

Systems neuroscience has established existence of a
set of fluctuating yet robust brain networks in humans.

Identical neural networks have reappeared across cognitive domains
using diverging methods. These observations prompted widely-adopted
notions, including the ``default-mode network'' \cite{raichle2001} (DMN; Raichle et al.,
2001), ``salience network'' (SN; Seeley et al., 2007), and ``dorsal
attention network'' (DAN; Corbetta and Shulmann,
2002). Developmentally, such large-scale networks emerge during late
fetal growth (Doria et al., 2010), before cognitive capacities mature
in childhood. In adults, nodes of a same cohesive network have more
similar functional profiles than nodes from different networks
(Anderson et al., 2013).
This
suggests network-network relationships as an under-appreciated unit of
functional brain organization.

Onset of a given cognitive task might induce
characteristic changes in functional coupling between large-scale
networks. Indeed, a working-memory task entailed increase in metabolic
activity in DAN regions but decrease in default-mode regions (Fransson
et al., 2006). Notably, the functional connectivity did not change
significantly within either DAN or DMN. Additionally, during auditory
event transitions in another experimental fMRI study, both DAN and SN
increased in activity, whereas the DMN decreased in activity
(Sridharan et al., 2008).

Such mediation between supraordinate networks
has been proposed to involve the right anterior insula (Sridharan et
al., 2008) and right temporo-parietal junction (Bzdok et al.,
2013).
The relevance of networks
possibly extends to psychiatric, neurological, and neurodegenerative
disorders (Seeley et al., 2009; Menon 2011).

STUDY

The present investigation reframed network-network dynamics as a
multivariate statistical learning problem.
capitalized on two independent, large datasets (n=500 and n=80) with
18 typical neuroimaging tasks each, covering a spectrum of humans'
cognitive apparatus.

determined a plausible, quantitative
combination of the brain signal's modes of variation. This allowed
avoiding the curse of dimensionality and making the machine-learning
results human-interpretable by quantitative association with
psychological concepts.

neurobiologically motivated restrictions to complexity circumvented the curse of dimensionality and allowed for useful, simplified views on brain function.

\section{Methods}
%
\paragraph{Data.}
As the currently biggest openly-accessible reference dataset,
we chose resources from the Human Connectome Project (HCP)
\cite{barch2013}.
Neuroimaging task data with labels of ongoing cognitive processes
were drawn from 500
healthy HCP participants (cf. Appendix for details on datasets).
18 HCP tasks 
were selected that are known to elicit reliable neural activity
across participants (Table \ref{table_tasks}).
In sum, the HCP task data incorporated 8650 first-level activity maps
from 18 diverse paradigms administered to 498 participants (2 removed
due to incomplete data).
All maps were resampled to a common $60\times72\times60$ space of
3mm isotropic voxels and gray-matter masked (at least 10\% tissue
probability).
The supervised analyses were thus based on labeled HCP task maps with
79,941 voxels of interest representing z-values in gray matter.

\begin{table}[h]
  \resizebox{0.98\textwidth}{!}{%
  \begin{tabular}{l|l|l}
    \hline
  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
  2 Punish             &                                       &                                                                                   \\ \hline
  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
  6 Theory of mind     &                                       &                                                                                   \\ \hline
  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
  \end{tabular}
}
\vspace{-0.2cm}
\caption{\textbf{Description of psychological tasks to predict.}}
\label{table_tasks}
\end{table}

These labeled data were complemented by unlabeled activity maps
from HCP acquisitions of unconstrained resting-state activity
\cite{smith2013resting}.
These reflect brain activity in the absence of controlled thought.
In sum, the HCP rest data concatenated
8000 unlabeled, noise-cleaned rest maps with
40 brain maps from each of 200 randomly selected participants.

We were further interested in the utility of the
optimized low-rank projection
in one task dataset for dimensionality reduction in another task dataset.
To this end, the HCP-derived network decompositions were used as preliminary
step in the classification problem of another large sample.
The ARCHI dataset \cite{pinel07} provides activity maps from
diverse experimental tasks, including auditory and visual perception, motor action,
reading, language comprehension and mental calculation.
Analogous to HCP data, the second task dataset thus incorporated 1404
labeled, grey-matter masked, and z-scored activity maps
from 18 diverse tasks acquired in 78 participants.

sparse statistical models have only few nonzero parameters

\paragraph{Implementation.}
The analyses were performed in Python.
We used \textit{nilearn} to handle
the large quantities of neuroimaging data 
\cite{abrah14}
and
\textit{Theano} for automatic, numerically stable
differentiation of symbolic computation graphs
\cite{bastien2012theano, bergstra2010theano}.
All Python scripts that generated the results are
accessible online for reproducibility and reuse
% (\url{http://github.com/anonymous/anonymous}).
(\url{http://github.com/banilo/nips2015}).

\section{Experimental Results}
\paragraph{Serial versus parallel structure discovery and classification.}

\section{Discussion}

neurobiologically motivated restrictions to complexity circumvented the curse of dimensionality and allowed for useful, simplified views on brain function.

\paragraph{Acknowledgment}
{\small The research leading to these results has received funding from the
European Union Seventh Framework Programme (FP7/2007-2013)
under grant agreement no. 604102 (Human Brain Project).
Data were provided by the Human Connectome Project.
Further support was received from
the German National Academic Foundation (D.B.)
and the MetaMRI associated team (B.T., G.V.).
}

\small
\bibliographystyle{splncs03}
\bibliography{paper_refs}

\end{document}

### 2015-11-22 struct_estimator.py

@@ -17,6 +17,7 @@ contjoint reg/net ratio
 - test max_it=100 versus max_it=500
 - 2-class versus 18-class problems
 - test known inseparable 2-class problem
+- spacenet versus treel2 in HCP/regression: age
 """
 import spams
 
@@ -54,7 +55,7 @@ MY_DATA_RATIO = 100
 N_JOBS = 5
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
-RES_NAME = 'srne_benchmark_zeroreglevel'
+RES_NAME = 'srne_benchmark_zerobrainlevel'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
@@ -521,6 +522,19 @@ import matplotlib.pyplot as plt
 import re
 %matplotlib qt
 
+plt.close('all')
+contrasts_names = [
+    'REWARD-PUNISH', 'PUNISH-REWARD', 'SHAPES-FACES', 'FACES-SHAPES',
+    'RANDOM-TOM', 'TOM-RANDOM',
+
+    'MATH-STORY', 'STORY-MATH',
+    'T-AVG', 'F-H', 'H-F',
+    'MATCH-REL', 'REL-MATCH',
+
+    'BODY-AVG', 'FACE-AVG', 'PLACE-AVG', 'TOOL-AVG',
+    '2BK-0BK'
+]
+
 for reg in [REGS[0]]:
     anal_str = '%s_dataratio%i_maxit%i' % (reg, MY_DATA_RATIO, MY_MAX_IT)
     tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
@@ -545,8 +559,24 @@ for reg in [REGS[0]]:
     plt.ylabel('accuracy (mean)')
     plt.ylim(0.0, 1.0)
     plt.xticks(lbds)
+    plt.text(0.50, 0.95, 'Final train-set acc: %.2f%%' % (clf_ovr_gs.train_acc * 100),
+             fontsize=18)
+    plt.text(0.50, 0.90, 'Final test-set acc: %.2f%%' % (clf_ovr_gs.test_acc * 100),
+             fontsize=18)
     plt.title('GridSearch: ' + anal_str)
     plt.savefig(tar_dump_file + '_gs.png')
+
+    # PRFS
+    plt.figure(figsize=(8, 6))
[…]

### 2015-11-22 struct_estimator_nonetgroups.py

@@ -51,7 +51,7 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 5
+N_JOBS = 15
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
 RES_NAME = 'srne_benchmark_nonetgroups'
@@ -519,9 +519,7 @@ def dump_comps(masker, compressor, components, threshold=2, fwhm=None,
 # dump_comps(nifti_masker, 'trace_dataratio%i_maxit100', coef_per_class, threshold=0.0)
 
 
-
-# rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark/* /git/srne/srne_benchmark
-# rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark_2cl/* /git/srne/srne_benchmark_2cl
+# rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark_nonetgroups/* /git/srne/srne_benchmark_nonetgroups/
 
 import matplotlib
 matplotlib.style.use('ggplot')

### 2015-11-22 struct_estimator_space_ovr_gs.py

@@ -51,10 +51,10 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 30
+N_JOBS = 5
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
-RES_NAME = 'srne_benchmark_space'
+RES_NAME = 'srne_benchmark_space_ovr_gs'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
@@ -162,10 +162,8 @@ X_test_nii = nifti_masker.inverse_transform(X_test)
 
 clf = SpaceNetClassifier(
     penalty='tv-l1', loss='logistic',
-    max_iter=100, n_jobs=N_JOBS,
-    standardize=False, screening_percentile=100,  # keep ALL voxels
-    verbose=True, l1_ratios=0.5
-    # verbose=True, l1_ratios=LAMBDA_GRID
+    max_iter=100, n_jobs=1,
+    verbose=True
 )
 
 from sklearn.grid_search import GridSearchCV
@@ -177,23 +175,21 @@ param_grid = {'estimator__l1_ratios': LAMBDA_GRID}
 # start time
 start_time = time.time()
 
-clf.fit(X_train_nii, Y_train)
+clf_ovr = OneVsRestClassifier(clf, n_jobs=1)
+clf_ovr_gs = GridSearchCV(clf_ovr, param_grid, n_jobs=N_JOBS, cv=3)
+clf_ovr_gs.fit(X_train_nii, Y_train)
 
-# clf_ovr = OneVsRestClassifier(clf, n_jobs=1)
-# clf_ovr_gs = GridSearchCV(clf_ovr, param_grid, n_jobs=N_JOBS, cv=3)
-# clf_ovr_gs.fit(X_train, Y_train)
-
-train_acc = clf.score(X_train_nii, Y_train)
+train_acc = clf_ovr_gs.score(X_train_nii, Y_train)
 print('Train-Accuracy: %.2f' % train_acc)
 
-test_acc = clf.score(X_test_nii, Y_test)
+test_acc = clf_ovr_gs.score(X_test_nii, Y_test)
 print('Test-Accuracy: %.2f' % test_acc)
-y_pred = clf.predict(X_test_nii)
[…]

### 2015-11-22 struct_estimator_zeroreglevel.py

@@ -17,6 +17,7 @@ contjoint reg/net ratio
 - test max_it=100 versus max_it=500
 - 2-class versus 18-class problems
 - test known inseparable 2-class problem
+- spacenet versus treel2 in HCP/regression: age
 """
 import spams
 
@@ -51,10 +52,10 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 15
+N_JOBS = 1
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
-RES_NAME = 'srne_benchmark_noreggroups'
+RES_NAME = 'srne_benchmark_zeroreglevel2'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
@@ -216,6 +217,9 @@ class StructuredEstimator(BaseEstimator):
                 self.own_variables = []
                 self.eta_g = np.array(np.ones(13 + n_regions - 1), dtype=np.float32)
                 
+                # HACK
+                self.eta_g[13:] = 0
+                
                 self.groups = np.asfortranarray(np.zeros((13 + n_regions - 1, 13 + n_regions - 1)), dtype=np.bool)
 
                 # add net info
@@ -244,9 +248,7 @@ class StructuredEstimator(BaseEstimator):
                         reg_inds = np.where(self.net_reg_map[i_net, :] == reg_label)[0]
                         n_reg_vox = len(reg_inds)
                         self.own_variables += [np.int32(cur_ind)]
-                        
-                        # HACK!
-                        self.N_own_variables[i_net + 1] += n_reg_vox  # no region voxels have decendences
+                        self.N_own_variables += [n_reg_vox]  # no region voxels have decendences
                         
                         self.groups[i_gr, i_net + 1] = True  # cur reg belongs to cur net
                         i_gr += 1
@@ -259,7 +261,7 @@ class StructuredEstimator(BaseEstimator):
                 assert cur_ind == len(net_reg_map_summed) - (net_reg_map_summed == 0).sum()
[…]

### 2015-11-24 paper/paper.tex
news

@@
 
-\title{Introducing region-network priors
-to statistical estimators for fMRI data}
+\title{Introducing region-network priors to statistical estimators for fMRI data}
 
@@
 \author{Danilo Bzdok, Michael Eickenberg, Olivier Grisel,
-  Bertrand Thirion,
-  Ga\"el Varoquaux\\
+  Ga\"el Varoquaux, Bertrand Thirion
   INRIA, Parietal team, Saclay, France\\
@@
 
-% OUR keywords
-%\textbf{\\keywords}: curse of dimensionality; semi-supervised learning;
-%fMRI; systems neuroscience
-
-% official NIPS keywords
-\textbf{\\keywords}: Brain Imaging, Functional Specialization,
-Functional Integration,
-Sparsity-inducing Norms, Systems Biology
+\textbf{\\keywords}:
+Brain Imaging, Functional Specialization, Functional Integration,
+Sparsity-inducing Norms, Numerical Optimization, Systems Neuroscience
 
@@
 \section{Introduction}
-%
+% sparsity
 Many quantitative scientific domains underwent a
@@
 For instance,
-linear regression models without any additional assumptions
+linear regression models without additional assumptions
 yield an infinity of possible coefficients
-and, thus, no solutions.
+and, thus, no solution.
 %
@@
 introduced and made many ill-posed estimation problems tractable
-\cite{hastie2015statistical}.
+\cite{buhlmann2011statistics, hastie2015statistical}.
 Domain-specific structural knowledge can be imposed on the 
 statistical estimation by preassuming that not all variables will be
-equally important.
-Sparsified statistical estimators have proven to yield
-statistical relationships that can be
+equally important
+\citep{bach2012optimization}.
+Sparsified supervised and unsupervised
+learning algorithms have proven to yield
+statistical relationships that can be readily
 estimated, reproduced, and interpreted
@@
 %
-Yet, what would be the most pertinent neurobiological structure
-that can successfully tackle the curse of dimensionality in
+Yet, what is the most pertinent neurobiological structure
+that can successfully tackle the
+\textit{curse of dimensionality} in
 functional neuroimaging research?
 
-abc
-in current fMRI,
-large-scale integration prevails over regional specialization,
-although both notions are inextricably linked (Tononi et al., 1998).
+% specialization & integration
+Concepts on human brain organization have long been torn
+between the two extremes
+\textit{functional specialization} and \textit{functional integration}.
+Functional specialization emphasizes that microscopically distinguishable
+brain regions probably solve distinct classes of computational processes
+\citep{kanwisher2010functional}.
+Functional integration, in turn, emphasizes that brain function
+is probably enabled by complex connections between these
+distinct brain regions.
+%
+This notion was predominantly derived from
+invasive examination of \textit{structure} (i.e., histological preparation),
+\textit{connectivity}, (i.e., axonal tracing),
+and \textit{functional properties}
+(i.e., single cell recordings) in same animals.
+Regarding functional segregation into specialized regions,
+early histological investigations into the microscopic heterogeneity of
+the human cerebral cortex have resulted
+in several detailed anatomical maps
+\citep{{brodmann1909vergleichende, vogt1919allgemeine}.
+Regarding axonal connections,
+each such cortical area has been observed
+to possess a unique set of incoming and outgoing connections
+\citep{passingham2002, young93monkey, scannell95cat}.
+%
+In particular,
+the realization of computational processes (i.e., function)
+is probably a consequence of both
+local cyto- and chemoarchitectonic infrastructure
+and its unique global connectivity profile.
+While
+cortical modules versus connections between those
+reflect 
+functional specialization versus functional integration,
+\citep{friston2002beyond},
+these architectural principles are conceptually inextricable in
+the realization of mental operations
+\citep{tononi1998complexity}.
 
-It however remains elusive how brain regions and networks relate to
-the organism's repertoire of mental operations.
-
-Both regions and netoworks are
-probably mechanistically relevant for emerging behavior.
-
-The organization of the cerebral cortex into distinct modules may be described along several dimensions, most importantly, structure, connectivity and function.
-This conclusion was mainly derived from concurrent invasive examination of microstructure (histological preparation), connectivity (axonal tracing) and functional properties (single cell recordings) in same animals.
-Regarding the (micro-)structural dimension, early histological investigations into the microscopic heterogeneity of the human cerebral cortex have resulted in several detailed, though partially incongruent, anatomical maps (Brodmann 1909; Vogt and Vogt 1919).
-More recent advances in structural brain mapping have led to the development of observer-independent probabilistic cytoarchitectonic maps in stereotaxic space (Zilles and Amunts 2010).
-Moreover, the constantly growing field strength of fMRI scanners permits increasingly fin-grained microstructural recordings of the living human brain (Walters et al.
-2007).
-Regarding the connectional dimension, each cortical area is assumed to possess a unique set of input and output connections.
-Axonal connectivity between areas can be revealed by injection of a tracing dye that is transported to interconnected brain regions in animals.
-Axonal tracing studies in primates suggest that cortical areas tend to be connected hierarchically and reciprocally by feed-forward and feed-backward connections (Maunsell and van Essen 1983).
-Mapping connectivity patterns of a particular part of the cortex may thus allow identifying cortical areas by demonstrating differences between the connections of neighbouring grey matter locations.
-
-Slightly reframing the concept of structure, connectivity and function as three pillars of brain organization, regional specialization of computational processes (i.e., function) can be conceived as being a consequence of both the local (micro-)structural and global connectional properties, as suggested by research in animals.
-That is, specialization of a particular function is not regarded as an intrinsic property of a brain region that is independent of its connectivity.
-Rather, input and output connectivity of an area in combination with the local "infrastructure" provided, e.g., by cyto- and chemoarchitecture, crucially determine what particular functions that area can perform (Passingham et al.
-2002).
-Conversely, each particular cortical module is probably characterized by a unique set of input and output connections, which is supported by statistical analyses of cortical connectivity in the primate (Young 1993) and feline (Scannell et al.
-1995) cortex.
-More generally, cortical modules and connections between those actually reflect functional segregation and functional integration, respectively (Friston 2002).
-In sum, a cortical module of functional specialization is likely to be defined by the intersection of regionally specific microstructure and connectivity patterns.
+method -> type of discovery
 
 SPECIAL
+Functional specialization has been investigated in many ways.
+%
+Single cell recordings and microscopic examination
+revealed, for instance, the
+specialization in the visual cortex into V1, V2, V3, V3A, and V4
+\citep{hubel1962receptive, zeki1978functional}.
 
-Functional
-specialization emphasizes that microanatomically distinguishable brain
-regions realize distinct functions (Brodmann 1909; Zeki 1978). Indeed,
-each microanatomical cortical area has a unique connectional, and thus
-perhaps functional, profile in cats (Scannell et al. 1995), monkeys
-(Young et al., 1993), and humans (Passingham et al., 2002).
+example: fusiform gyrus
+-> lesion -> does not work anymore
 
-Consistently, early lesion studies of induced behavioral
-impairments in rats challenged the dogmatic localization of brain
-function (Franz \& Lashley, 1917). Analogously in humans, even
-extensive prefrontal lesions do not necessarily become apparant in
-everyday behavior (Mesulam, 1990). An implicit preference for
-functional specialization might therefore hinder consensus in
-fundamental, still unresolved questions in neuroscience, such as the
-relation between cognition and emotion (cf. Pessoa 2010, Overwalle
-2011).
+Non-invasive brain imaging with
+functional magnetic resonance imaging (fMRI) and
+positron emission tomography (PET)
+enabled the localization of
+sensory, motor, and emotional functions to cortical areas
+in the living brain
+\citep{fristen1997imaging}.
 
-locally characteristic neuronal populations
+Radioactive mapping the distribution of
+neurotransmitter receptors added yet another
+local characteristic of neuronal populations
+\citep{zilles2009receptor}.
+
+clustering
+\citep{behrens03}
+
+High-thoughput computing enabled an 
+ultahigh-resolution 3D model of brain anatomy
+at macroscopical to near-cellular scale
+\citep{amunts2013bigbrain}.
+
+=> methods: non-overlapping, discrete region units
 
 INTEGRAL
-
-Hebb, D. O. The Organization Of Behaviour (Wiley,
-1949).
 
@@
 set of fluctuating yet robust brain networks in humans.
+
+example: DMN network?
 
@@
 
-STUDY
+=> methods: overlapping, continuous network units
+invasive axonal tracing studies,
+ICA,
+seed-based analyses of BOLD fluctations or
+electrophysiological oscillations,
+as well as
+effective connectivity models
+and
+graph-theoretical measurements
+\citep{friston03dcm, buzsaki2004neuronal,
+beckmann2005, bullmore2009complex, jbabdi2013long}.
+
+analysis and integration of information
+
+% study
+The present study attempts a combination of specialization and
+integration aspects by means of structured sparsity
+for high-dimensional inference.
+%
+
+adaptive estimator
+biologically plausible
+
+recent advances in high-dimensional statistics enable
 
@@
 
-neurobiologically motivated restrictions to complexity circumvented the curse of dimensionality and allowed for useful, simplified views on brain function.
+neurobiologically motivated restrictions to complexity circumvented
+the curse of dimensionality and
+allowed for useful, simplified views on brain function.
+
+importance of brain regions and networks is probably a matter of
+degree.
+We estimate that degree from the data
+
+help reintegrate the divorced
+interpretational streams based on
+region- and network-focused neuroscientific investigations.
 
 \section{Methods}
+%
+\paragraph{Rationale}
+
+we need to inject domain knowledge into
+statistical estimations to harness the curse of dimensionality.
+
+should be able to estimate voxel level
+while taking into account known supravoxel structure.
+
 %
@@
 
-neurobiologically motivated restrictions to complexity circumvented the curse of dimensionality and allowed for useful, simplified views on brain function.
+Functional specialization and functional integration
+in the human brain are
+probably both mechanistically relevant for emerging behavior.
+However, there is a scarcity of statistical methods
+that concomitantly relate brain regions and networks to
+an organism's repertoire of mental operations.
+
+neurobiologically motivated restrictions to
+complexity circumvented the curse of dimensionality and allowed
+for useful, simplified views on brain function.
 

### 2015-11-24 struct_estimator.py

@@ -18,6 +18,11 @@ contjoint reg/net ratio
 - 2-class versus 18-class problems
 - test known inseparable 2-class problem
 - spacenet versus treel2 in HCP/regression: age
+- run on structure/VBM with regression -> nilearn example
+- introduce reg-net hyperparameter 0..1 [only regs -> only nets] to be
+gridsearched (cf. Lin/Yuan 2007)
+- inverse gridsearch layer and one-versus-rest layer in wrappers to
+get optimal reg-net ratio for each class
 """
 import spams
 
@@ -53,9 +58,10 @@ FORCE_TWO_CLASSES = False
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
 N_JOBS = 5
-LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
+# LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
+LAMBDA_GRID = np.logspace(-2, 1, 11)
 
-RES_NAME = 'srne_benchmark_zerobrainlevel'
+RES_NAME = 'srne_benchmark_loggrid_zerobrainlevel_weighted'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
@@ -179,8 +185,8 @@ class StructuredEstimator(BaseEstimator):
     def fit(self, X, y):
         if self.verbose:
             print(self)
-            print('Unique Y: ')
-            print(np.unique(y))
+            # print('Unique Y: ')
+            # print(np.unique(y))
         
         # SPAMS expects -1/+1 labelling
         y[y == 0] = -1
@@ -216,9 +222,6 @@ class StructuredEstimator(BaseEstimator):
                 self.N_own_variables = []
                 self.own_variables = []
                 self.eta_g = np.array(np.ones(13 + n_regions - 1), dtype=np.float32)
-                
-                # HACK
-                self.eta_g[13:] = 0
                 
                 self.groups = np.asfortranarray(np.zeros((13 + n_regions - 1, 13 + n_regions - 1)), dtype=np.bool)
 
@@ -282,10 +285,20 @@ class StructuredEstimator(BaseEstimator):
 
                     cur_ind += n_reg_vox  # move behind size of current net
             X = X_task_tree
+            
[…]

### 2015-11-24 struct_estimator_nonetgroups.py

@@ -51,7 +51,7 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 15
+N_JOBS = 5
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
 RES_NAME = 'srne_benchmark_nonetgroups'

### 2015-11-24 struct_estimator_noreggroups.py

@@ -51,7 +51,7 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 15
+N_JOBS = 20
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
 RES_NAME = 'srne_benchmark_noreggroups'

### 2015-11-24 struct_estimator_space.py

@@ -51,7 +51,7 @@ FORCE_TWO_CLASSES = False
 # REG_PEN = 'trace-norm'
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
-N_JOBS = 30
+N_JOBS = 10
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
 RES_NAME = 'srne_benchmark_space'
@@ -161,18 +161,14 @@ X_train_nii = nifti_masker.inverse_transform(X_train)
 X_test_nii = nifti_masker.inverse_transform(X_test)
 
 clf = SpaceNetClassifier(
-    penalty='tv-l1', loss='logistic',
-    max_iter=100, n_jobs=N_JOBS,
+    penalty='tv-l1', loss='logistic', mask=nifti_masker,
+    max_iter=100, n_jobs=N_JOBS, cv=3,
     standardize=False, screening_percentile=100,  # keep ALL voxels
-    verbose=True, l1_ratios=0.5
-    # verbose=True, l1_ratios=LAMBDA_GRID
+    verbose=True, l1_ratios=LAMBDA_GRID
 )
 
 from sklearn.grid_search import GridSearchCV
 from sklearn.multiclass import OneVsRestClassifier
-
-param_grid = {'estimator__l1_ratios': LAMBDA_GRID}
-# param_grid = {'estimator__lambda1': [0.1]}
 
 # start time
 start_time = time.time()
@@ -292,7 +288,7 @@ contrasts_names = [
 ]
 
 for reg in [REGS[0]]:
-    anal_str = '%s_dataratio%i_maxit%i' % (reg, MY_DATA_RATIO, MY_MAX_IT)
+    anal_str = 'l1%.2f_maxit%i' % (0.5, MY_MAX_IT)
     tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
     if not op.exists(tar_dump_file):
         print('SKIPPED: %s' % tar_dump_file)

### 2015-11-24 struct_estimator_zeroreglevel.py

@@ -55,7 +55,7 @@ MY_DATA_RATIO = 100
 N_JOBS = 1
 LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
-RES_NAME = 'srne_benchmark_zeroreglevel2'
+RES_NAME = 'srne_benchmark_zeronetlevel'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
@@ -218,7 +218,7 @@ class StructuredEstimator(BaseEstimator):
                 self.eta_g = np.array(np.ones(13 + n_regions - 1), dtype=np.float32)
                 
                 # HACK
-                self.eta_g[13:] = 0
+                self.eta_g[1:13] = np.finfo(float).eps
                 
                 self.groups = np.asfortranarray(np.zeros((13 + n_regions - 1, 13 + n_regions - 1)), dtype=np.bool)
 
@@ -516,109 +516,4 @@ def dump_comps(masker, compressor, components, threshold=2, fwhm=None,
 # rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark/* /git/srne/srne_benchmark
 # rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark_2cl/* /git/srne/srne_benchmark_2cl
 
-import matplotlib
-matplotlib.style.use('ggplot')
-import matplotlib.pyplot as plt
-import re
-%matplotlib qt
-
-plt.close('all')
-contrasts_names = [
-    'REWARD-PUNISH', 'PUNISH-REWARD', 'SHAPES-FACES', 'FACES-SHAPES',
-    'RANDOM-TOM', 'TOM-RANDOM',
-
-    'MATH-STORY', 'STORY-MATH',
-    'T-AVG', 'F-H', 'H-F',
-    'MATCH-REL', 'REL-MATCH',
-
-    'BODY-AVG', 'FACE-AVG', 'PLACE-AVG', 'TOOL-AVG',
-    '2BK-0BK'
-]
-
-for reg in [REGS[0]]:
-    anal_str = '%s_dataratio%i_maxit%i' % (reg, MY_DATA_RATIO, MY_MAX_IT)
-    tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
-    if not op.exists(tar_dump_file):
-        print('SKIPPED: %s' % tar_dump_file)
-        # continue
[…]

### 2015-11-25 paper/paper.tex
intro outline standing

@@
 
-\title{Introducing region-network priors to statistical estimators for fMRI data}
+\title{Region-network sparsity priors for high-dimensional inference in fMRI data}
 
@@
 
-\author{Danilo Bzdok, Michael Eickenberg, Olivier Grisel,
+\author{Danilo Bzdok, Karl Zilles, Michael Eickenberg,
   Ga\"el Varoquaux, Bertrand Thirion
@@
 SPECIAL
-Functional specialization has been investigated in many ways.
+Functional specialization has been
+explored with many different research methods.
 %
@@
 \citep{hubel1962receptive, zeki1978functional}.
-
-example: fusiform gyrus
--> lesion -> does not work anymore
-
-Non-invasive brain imaging with
+Tissue lesion reports of the mid-fusiform gyrus of the visual system
+frequently indicated impaired
+recognition of others' identity from faces
+\citep{iaria2008contribution}.
+The localization of
+sensory, motor, and emotional cognitive functions to cortical areas
+in the living brain
+has later been enabled by
+non-invasive brain imaging with
 functional magnetic resonance imaging (fMRI) and
 positron emission tomography (PET)
-enabled the localization of
-sensory, motor, and emotional functions to cortical areas
-in the living brain
 \citep{fristen1997imaging}.
-
-Radioactive mapping the distribution of
-neurotransmitter receptors added yet another
+Further,
+radioactive mapping the distribution of
+neurotransmitter receptors rendered accessible yet another
 local characteristic of neuronal populations
 \citep{zilles2009receptor}.
-
-clustering
-\citep{behrens03}
-
-High-thoughput computing enabled an 
-ultahigh-resolution 3D model of brain anatomy
+% allude to our many-regions layer in the methods
+In the computational era,
+automatic clustering methods are increasingly employed to
+regionally differentiation of the cerebral cortex,
+which partly turned out to be more fine-grained than
+classical cytoarchitectonic mapping
+\citep{behrens03, cbp2015review}.
+Today,
+high-thoughput computing enables 
+ultahigh-resolution 3D models of brain anatomy
 at macroscopical to near-cellular scale
 \citep{amunts2013bigbrain}.
-
-=> methods: non-overlapping, discrete region units
+%
+As a crucial common point,
+all these methodological classes
+yielded neuroscientific findings
+that were naturally interpreted
+non-overlapping, discrete region compartments
+as the basic architectonic framework of cortical organization.
 
@@
 region- and network-focused neuroscientific investigations.
+
+a compartmental model of
+functional organization in the cerebral cortex can be derived
 
@@
 
+We assume regions and networks but can estimate 
+importance of each voxel.
+
 neurobiologically motivated restrictions to
@@
 for useful, simplified views on brain function.
+
+curse of dimensionality has classically been circumvented
+by treating a high-dimensional problem
+as a mass-univariate problem.
+Problem was postponed to the inference step
+this is why we never solved the multiple comparisons problem in fMRI
+
+regularization with sparsity penalties
+restrictions to complexity according to neurobiological facts
+-> bias-variance tradeoff: negigible increase in bias but large decrease in variance
+-> VC: decrease complexitiy capactiy -> better chance for generalization out of sample
+
+multiple comparisons problem has the curse of dimensionality
+as its close correspondence in statistical learning
+sparsity -> solves the curse at the estimation level
+
+OUTLOOK:
+robust high-dimensional inference will be key
+to prediction in single individual,
+such as for personalized medicine
+\citep{gabrieli2015prediction}
 

### 2015-11-25 struct_estimator_space.py

@@ -52,9 +52,10 @@ FORCE_TWO_CLASSES = False
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
 N_JOBS = 10
-LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
+LAMBDA_GRID = [0.5]
+# LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
 
-RES_NAME = 'srne_benchmark_space'
+RES_NAME = 'srne_benchmark_space_alpha0.5'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)

### 2015-11-26 paper/paper.tex
rnratio slides add

@@
 \usepackage{multirow}
+\usepackage{comment}
 
@@
 
-\title{Region-network sparsity priors for high-dimensional inference in fMRI data}
+\title{Region-network sparsity priors for\\
+high-dimensional inference in fMRI data}
 
@@
 \author{Danilo Bzdok, Karl Zilles, Michael Eickenberg,
-  Ga\"el Varoquaux, Bertrand Thirion
+  Ga\"el Varoquaux, Bertrand Thirion\\
+  Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
   INRIA, Parietal team, Saclay, France\\
@@
 \begin{abstract}
-Imaging neuroscience links human behavior to aspects of brain
-biology in ever-increasing datasets.
+% Imaging neuroscience links human behavior to aspects of brain
+% biology in ever-increasing datasets.
 
@@
 the high-dimensional regime (i.e., "wide data")
-\citep{jordan2015massive}.
+\cite{jordan2015massive}.
 Also in the brain imaging domain,
@@
 \cite{buhlmann2011statistics, hastie2015statistical}.
-Domain-specific structural knowledge can be imposed on the 
-statistical estimation by preassuming that not all variables will be
-equally important
-\citep{bach2012optimization}.
+Domain-specific structure can be imposed on the 
+statistical estimation,
+thus preassuming that variables have unequal importance
+and follow existing knowledge
+\cite{bach2012optimization}.
 Sparsified supervised and unsupervised
@@
 %
-Yet, what is the most pertinent neurobiological structure
-that can successfully tackle the
+Yet, what neurobiological structure suggests itself
+to successfully tackle the
 \textit{curse of dimensionality} in
@@
 brain regions probably solve distinct classes of computational processes
-\citep{kanwisher2010functional}.
+\cite{kanwisher2010functional}.
 Functional integration, in turn, emphasizes that brain function
 is probably enabled by complex connections between these
-distinct brain regions.
+distinct brain regions \cite{sporns14nn}.
 %
-This notion was predominantly derived from
+These notions were predominantly derived from
 invasive examination of \textit{structure} (i.e., histological preparation),
@@
 in several detailed anatomical maps
-\citep{{brodmann1909vergleichende, vogt1919allgemeine}.
+\cite{brodmann1909vergleichende, vogt1919allgemeine}.
 Regarding axonal connections,
@@
 to possess a unique set of incoming and outgoing connections
-\citep{passingham2002, young93monkey, scannell95cat}.
+\cite{passingham2002, young93monkey, scannell95cat}.
 %
-In particular,
-the realization of computational processes (i.e., function)
-is probably a consequence of both
+Both
 local cyto- and chemoarchitectonic infrastructure
-and its unique global connectivity profile.
+and its unique global connectivity profile
+together realize computational processes (i.e., function).
 While
@@
 reflect 
-functional specialization versus functional integration,
-\citep{friston2002beyond},
-these architectural principles are conceptually inextricable in
-the realization of mental operations
-\citep{tononi1998complexity}.
+functional specialization versus functional integration
+\cite{friston2002beyond, mesulam_sensation},
+both architectural principles are conceptually inextricable when
+explaining the emergence of mental operations
+\cite{tononi1998complexity}.
 
-method -> type of discovery
-
-SPECIAL
+% SPECIAL
 Functional specialization has been
-explored with many different research methods.
+explored and interpreted based on many different research methods.
 %
@@
 specialization in the visual cortex into V1, V2, V3, V3A, and V4
-\citep{hubel1962receptive, zeki1978functional}.
-Tissue lesion reports of the mid-fusiform gyrus of the visual system
-frequently indicated impaired
+\cite{hubel1962receptive, zeki1978functional}.
+Tissue lesion of the mid-fusiform gyrus of the visual system
+were frequently reported to impair
 recognition of others' identity from faces
-\citep{iaria2008contribution}.
+\cite{iaria2008contrib}.
 The localization of
@@
 positron emission tomography (PET)
-\citep{fristen1997imaging}.
+\cite{fristen1997imaging}.
 Further,
-radioactive mapping the distribution of
-neurotransmitter receptors rendered accessible yet another
+radioactive mapping of neurotransmitter receptor distributions
+rendered accessible yet another
 local characteristic of neuronal populations
-\citep{zilles2009receptor}.
-% allude to our many-regions layer in the methods
+\cite{zilles2009receptor}.
+% allude to our many-regions layer in our methods
 In the computational era,
 automatic clustering methods are increasingly employed to
-regionally differentiation of the cerebral cortex,
-which partly turned out to be more fine-grained than
-classical cytoarchitectonic mapping
-\citep{behrens03, cbp2015review}.
+regionally differentiate the cerebral cortex,
+which can partly be more fine-grained than
+classical cytoarchitectonic borders
+\cite{behrens03, cbp2015review}.
 Today,
@@
 at macroscopical to near-cellular scale
-\citep{amunts2013bigbrain}.
+\cite{amunts2013bigbrain}.
 %
 As a crucial common point,
-all these methodological classes
-yielded neuroscientific findings
-that were naturally interpreted
+all these methodological approaches
+yield neuroscientific findings
+that are naturally interpreted according to
 non-overlapping, discrete region compartments
-as the basic architectonic framework of cortical organization.
+as the basic architectonic framework of brain organization.
 
-INTEGRAL
-
-Only recently we have shifted the main interpretational focus
-from single region to macroscopical networks
-in systems neuroscience \citep{yuste2015}.
-
-eemrgent properties emerge from the interaction
-
-In
-contrast, functional integration emphasizes that function is an
-emergent property of collaborating areas. In fact, the higher the
-hierarchical level, the more one cortical area connects to different
-large-scale networks, which makes their boundaries less clear
-(Yeo/Buckner 2011). The above network-network models naturally embody
-functional integration as they capture (partially overlapping)
-patterns of spatial coherence.
-
-Systems neuroscience has established existence of a
-set of fluctuating yet robust brain networks in humans.
-
-example: DMN network?
-
-Identical neural networks have reappeared across cognitive domains
-using diverging methods. These observations prompted widely-adopted
-notions, including the ``default-mode network'' \cite{raichle2001} (DMN; Raichle et al.,
-2001), ``salience network'' (SN; Seeley et al., 2007), and ``dorsal
-attention network'' (DAN; Corbetta and Shulmann,
-2002). Developmentally, such large-scale networks emerge during late
-fetal growth (Doria et al., 2010), before cognitive capacities mature
-in childhood. In adults, nodes of a same cohesive network have more
-similar functional profiles than nodes from different networks
-(Anderson et al., 2013).
-This
-suggests network-network relationships as an under-appreciated unit of
-functional brain organization.
-
-Onset of a given cognitive task might induce
-characteristic changes in functional coupling between large-scale
-networks. Indeed, a working-memory task entailed increase in metabolic
-activity in DAN regions but decrease in default-mode regions (Fransson
-et al., 2006). Notably, the functional connectivity did not change
-significantly within either DAN or DMN. Additionally, during auditory
-event transitions in another experimental fMRI study, both DAN and SN
-increased in activity, whereas the DMN decreased in activity
-(Sridharan et al., 2008).
-
-Such mediation between supraordinate networks
-has been proposed to involve the right anterior insula (Sridharan et
-al., 2008) and right temporo-parietal junction (Bzdok et al.,
-2013).
-The relevance of networks
-possibly extends to psychiatric, neurological, and neurodegenerative
-disorders (Seeley et al., 2009; Menon 2011).
-
-=> methods: overlapping, continuous network units
-invasive axonal tracing studies,
-ICA,
-seed-based analyses of BOLD fluctations or
-electrophysiological oscillations,
-as well as
-effective connectivity models
+% INTEGRAL
+It is more recent
+that the main interpretational focus has shifted
+from circumscribed regions to network stratifications
+in systems neuroscience \cite{yuste2015, stephan_dys}.
+The higher the processing hierarchy level,
+the more a cortical area is known to
+connect to different large-scale networks
+\cite{yeo11}.
+%
+Invasive axonal tracing studies in monkeys were complemented
+by in-vivo diffusion MRI tractography in humans
+as a now frequently employed method to
+outline fiber bundles between brain regions
+\cite{jbabdi2013long}.
+Besides analyses of
+electrophysiological oscillations
+\cite{buzsaki2004neuronal}
 and
-graph-theoretical measurements
-\citep{friston03dcm, buzsaki2004neuronal,
-beckmann2005, bullmore2009complex, jbabdi2013long}.
-
-analysis and integration of information
+graph-theoretical properties \cite{bullmore2009complex},
+studies of
+functional connectivity \cite{buckner2013opportunities} and
+independent component analysis (ICA) \cite{beckmann2005}
+became the workhorses of network discovery
+in functional neuroimaging.
+These revealed the important implication of
+canonical brain networks across cognitive domains,
+including the so-called
+``default-mode network'' \cite{raichle2001pnas},
+``salience network'' \cite{seeley2007dissociable},
+and ``dorsal attention network'' \cite{corbettashul2008}. 
+Characteristic changes in the configuration of
+these large-scale networks
+were repeatedly observed to be induced
+by the onset of given cognitive tasks \cite{fransson2006}.
+Such task-induced mechanisms orchastrating supraordinate networks
+might be subserved by the right anterior insula \cite{sridh2008}
+and temporo-parietal junction \cite{bzdok2013tpj}.
+%
+Ultimately,
+interpretation of findings from all these methods naturally embraces
+cross-regional integration by
+overlapping network compartments
+as the basic architectonic framework of brain organization,
+in stark constrast to methods examining regional specialization.
 
 % study
-The present study attempts a combination of specialization and
-integration aspects by means of structured sparsity
-for high-dimensional inference.
-%
+Building on these interpretational traditions,
+the present study proposes to incorporate
+known architectonic aspects from both
+anatomical segregation and integration
+into unified classification and regression algorithms
+by means  of structured sparsity assumptions.
+The "true" relative importance of 
+local region compartments and global network compartments
+is typically unknown
+but
+probably varying in degree
+across diverse neuroscientific questions.
+Recent advances in multivariate statistical learning techniques
+enable such adaptive estimators with
+neurobiologically plausible region and network priors.
+Using a large reference dataset,
+we demonstrated that domain-informed supervised models
+gracefully handle the curse of dimensionality,
+yield many more human-interpretable results,
+and generalize better to new samples
+than domain-na\"ive models.
 
-adaptive estimator
-biologically plausible
-
-recent advances in high-dimensional statistics enable
-
-The present investigation reframed network-network dynamics as a
-multivariate statistical learning problem.
-capitalized on two independent, large datasets (n=500 and n=80) with
-18 typical neuroimaging tasks each, covering a spectrum of humans'
-cognitive apparatus.
-
-determined a plausible, quantitative
-combination of the brain signal's modes of variation. This allowed
-avoiding the curse of dimensionality and making the machine-learning
-results human-interpretable by quantitative association with
-psychological concepts.
-
-neurobiologically motivated restrictions to complexity circumvented
-the curse of dimensionality and
-allowed for useful, simplified views on brain function.
-
-importance of brain regions and networks is probably a matter of
-degree.
-We estimate that degree from the data
-
-help reintegrate the divorced
-interpretational streams based on
-region- and network-focused neuroscientific investigations.
-
-a compartmental model of
-functional organization in the cerebral cortex can be derived
+\begin{comment}
 
@@
 statistical estimations to harness the curse of dimensionality.
+two neurobiological design principles
+
+integrative processes
 
@@
 while taking into account known supravoxel structure.
+is instrumental in
+Developmentally, such large-scale networks emerge during late
+fetal growth (Doria et al., 2010), before cognitive capacities mature
+in childhood.
+
+In adults, nodes of a same cohesive network have more
+similar functional profiles than nodes from different networks
+(Anderson et al., 2013).
+
+neurobiologically motivated restrictions to complexity circumvented
+the curse of dimensionality
 
@@
 such as for personalized medicine
-\citep{gabrieli2015prediction}
+\cite{gabrieli2015prediction}
 
@@
 
+\end{comment}
+
 \small
+% \bibliographystyle{plainnat}
 \bibliographystyle{splncs03}

### 2015-11-26 struct_estimator.py

@@ -23,6 +23,8 @@ contjoint reg/net ratio
 gridsearched (cf. Lin/Yuan 2007)
 - inverse gridsearch layer and one-versus-rest layer in wrappers to
 get optimal reg-net ratio for each class
+- for each task a histogramm: f1 score across reg-net ratios -> haights
+probably at different positions
 """
 import spams
 

### 2015-11-26 struct_estimator_space.py

@@ -289,7 +289,7 @@ contrasts_names = [
 ]
 
 for reg in [REGS[0]]:
-    anal_str = 'l1%.2f_maxit%i' % (0.5, MY_MAX_IT)
+    anal_str = 'l1%.2f_grid_maxit%i' % (0.5, MY_MAX_IT)
     tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
     if not op.exists(tar_dump_file):
         print('SKIPPED: %s' % tar_dump_file)
@@ -332,7 +332,7 @@ for reg in [REGS[0]]:
     plt.savefig(tar_dump_file + '_precrec.png')
 
 for reg in [REGS[0]]:
-    anal_str = 'l1%.2f_maxit%i' % (0.5, MY_MAX_IT)
+    anal_str = 'l1%.2f_grid_maxit%i' % (0.5, MY_MAX_IT)
     tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
     if not op.exists(tar_dump_file):
         print('SKIPPED: %s' % tar_dump_file)

### 2015-11-29 paper/paper.tex
new adventures

@@
 \def\trans{\mathsf{T}}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 
-\begin{comment}
-
 \section{Methods}
@@
 
+data exhibit natural correlations between neighboring voxels forming clusters
+
 neurobiologically motivated restrictions to complexity circumvented
 the curse of dimensionality
+
+\paragraph{Numerical Optimization}
+
+for every column u of U, it compute a column v of V solving
+
+we aim at learning a weight vector w ∈ Rp and an intercept b ∈ R
+such that the prediction of y can be based on the value of w⊤x + b.
+
+We omit a bias term, since the data were mean-centered
+and unit-variance scaled.
+The scalar b is not particularly informative
+
+however the vector w corresponds to a volume that
+can be represented in brain space as a volume
+
+more precisely, we denote by X ∈ Rn×p the design matrix
+assembled from n fMRI volumes and by y ∈ Rn the corresponding n targets.
+In other words, each row of X is a p-dimensional sample,
+i.e., an activation map of p voxels related to one stimulus presentation.
+for visualization of the predictive pattern of voxels.
+
+Learning the parameters (w, b) remains challenging
+since the number of features (104 to 105 voxels) exceeds
+by far the number of samples (a few hundreds of volumes).
+
+To address this issue, dimensionality reduction attempts to
+find a low dimensional subspace that concentrates
+as much of the predictive power of
+the original set as possible for the problem at hand.
+-> we do not want to do preliminary feature selection or
+dimensionality reduction
+or feature agglomeration because we want to fit one model parameter
+to each brain voxel for maximal interpretability
+This corresponds to discarding some columns of X.
+
+\begin{equation}
+  \argmin 0.5||u-v||_2^2 + \lambda\sum_{g \in T} \eta_g||v_g||_2
+\end{equation}
+
+\begin{comment}
 
@@
 
+The same classification performance can be reached by
+many different models -> we naturally want to priviledge those
+among the equally performing models that are closest to
+what we know about the brain
+
+-> interpreta bility and accuracy typically exclude each other
+(cf. Hastie)
+
 curse of dimensionality has classically been circumvented

### 2015-11-29 struct_estimator.py

@@ -61,16 +61,17 @@ MY_MAX_IT = 100
 MY_DATA_RATIO = 100
 N_JOBS = 5
 # LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
-LAMBDA_GRID = np.logspace(-2, 1, 11)
+LAMBDA_GRID = np.logspace(-4, 0, 9)
+# LAMBDA_GRID = [0.1]
 
-RES_NAME = 'srne_benchmark_loggrid_zerobrainlevel_weighted'
+RES_NAME = 'srne_benchmark_l1_regloggrid'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)
 if not op.exists(WRITE_DIR):
     os.mkdir(WRITE_DIR)
 
-REGS = ['tree-l2']
+REGS = ['l1']
 
 # REGS = ['tree-l0', 'tree-l2',
 #     'sparse-group-lasso-linf', 'sparse-group-lasso-l2',
@@ -533,7 +534,7 @@ def dump_comps(masker, compressor, components, threshold=2, fwhm=None,
 # rsync -vza dbzdok@drago:/storage/workspace/danilo/srne/srne_benchmark_2cl/* /git/srne/srne_benchmark_2cl
 
 import matplotlib
-# matplotlib.style.use('ggplot')
+matplotlib.style.use('ggplot')
 import matplotlib.pyplot as plt
 import re
 %matplotlib qt
@@ -551,7 +552,7 @@ contrasts_names = [
     '2BK-0BK'
 ]
 
-LOG_LBD = False
+LOG_LBD = True
 for reg in [REGS[0]]:
     anal_str = '%s_dataratio%i_maxit%i' % (reg, MY_DATA_RATIO, MY_MAX_IT)
     tar_dump_file = '%s/%s' % (WRITE_DIR, anal_str)
@@ -585,9 +586,9 @@ for reg in [REGS[0]]:
         plt.xticks(np.log10(lbds))
     else:
         plt.xticks(lbds)
-    plt.text(0.5, 0.95, 'Final train-set acc: %.2f%%' % (clf_ovr_gs.train_acc * 100),
+    plt.text(-2, 0.95, 'Final train-set acc: %.2f%%' % (clf_ovr_gs.train_acc * 100),
              fontsize=18)
[…]

### 2015-12-03 paper/paper.tex
interm

@@
 Brain Imaging, Functional Specialization, Functional Integration,
-Sparsity-inducing Norms, Numerical Optimization, Systems Neuroscience
+Sparsity-inducing Norms, Structured Sparsity,
+Numerical Optimization, Systems Neuroscience
 
@@
 explaining the emergence of mental operations
-\cite{tononi1998complexity}.
+\cite{tononi1998complexity, saygin2012}.
 
@@
 
+higher-order prior knowledge
+
+structured sparsity
+extend trend in stastical modelling from
+genetics \cite{rapaport2008classification, kim2012tree},
+natural image processing \cite{harzallah2009combining}
+
+to brain imaging domain.
+
 \section{Methods}
@@
 the curse of dimensionality
+three-dimensional spatial arrangement that respects
+the functional anatomy of the brain
+not ignore the spatial configuration
 
-\paragraph{Numerical Optimization}
+incorporate rich prior knowledge
+
+If meaningful structures exist,
+ÇÇçwe show that one can take advantage of such structures
+
+\paragraph{Problem formulation}
+
+Sparse linear models
+encode geometric prior information
+topology
+local sets of voxels
+
+structured regularization
+We might therefore gain in the quality of the factors
+induced by enforcing directly this a priori
+
+l1 = unstructured sparsity-inducing penalty
 
@@
 
+hierarchial tree = more generally into a directed acyclic graph
+
 more precisely, we denote by X ∈ Rn×p the design matrix
@@
 by far the number of samples (a few hundreds of volumes).
+
+The scalar b is not particularly informative,
+however the vector w corresponds to a volume that
+can be represented in brain space as a volume
+for visualization of the predictive pattern of voxels.
+
+each row of X is a p-dimensional sample,
+i.e., an activation map of p voxels related to one stimulus presentation.
 
@@
 
+The essential shortcoming of the Elastic net is that
+it does not take into account the spatial structure of the data,
+which is crucial in this context
+
+Craddock clusters are often used for feature agglomeration
+into parcels
+-> exploits only a part of the data
+
+dual-level spatial structure
+sparse hierarchical regularization
+structured sparsity-inducing regularization
+the root of the tree T is the unique cluster that gathers all the voxels,
+
+It is a generalization of the traditional $\ell_1$-norm
+$\Omega(\mathbf{w}) = \sum_{j=1}^p|\mathbf{w}_j|$
+ignores structure
+
+\cite{jenatton2011multi}
+
+\textit{structured sparsity}
+
+\cite{huang2011learning, morales2010family, jenatton2011structured}
+
+a node $j$ of $\mathcal{T}$,
+we denote by $g_j \subseteq \{1,..,q\}$ the set of indices that record
+all the descendants of $j$ in $\mathcal{T}$
+
+the family of sparsity-inducing norms has recently been extended
+by hierarchical sparsity penalty terms
+\cite{zhao2009composite}.
+
 \begin{equation}
-  \argmin 0.5||u-v||_2^2 + \lambda\sum_{g \in T} \eta_g||v_g||_2
+  \Omega(\mathbf{w}) = \sum_{g \in G}||\mathbf{w}_g||_2 = \sum_{g \in G}\sqrt{\sum_{j \in g}\mathbf{w}_j^2}
 \end{equation}
 
+For example, when G is the set of all singletons, Ω is the
+usual l1 norm (assuming that all the weights are equal to 1).
+
+l1/l2 mixed norm is convex
+
+Discarding coefficients belonging to a network group will naturally enforce
+discarding the coefficients belonging to each of its descendent region groups.
+Conversely,
+variable selection of a network group will also enforce
+selection of all voxel of its descendent group regions.
+Single region groups can however be set to zero (unselected)
+or non-zero (selected)
+without analogous effect on the parent network group.
+
+At the between-group level,...
+$\Omega$ exerts $\ell_1$-like variable selection on
+the (||\mathbf{w}_g||_2)_{g\inG} groups,
+yielding a maximum of $g \in G$ to be zeroed out
+\cite{jenatton2011structured}.
+The important consequence is that also all descentes of such a zeroed
+group $g \in G$ will be descarded.
+Conversely,
+if one group $g$ is selected,
+then all the ancestral groups will also be selected.
+Thus, statistical estimation will be improved by enticing
+entire voxel sets to be selected or discarded as predictive, 
+although one individual coefficient is computed for each voxel.
+
+-> it is a $(\ell_1, \ell_2)$-mixed norm
+-> between-group sparsity effect by l1
+-> within-group shrinkage effect by l2
+
+\begin{equation}
+  \Omega(\mathbf{w}) = \sum_{g \in G} \eta_g ||\mathbf{w}_g||_2
+\end{equation}
+
+(\eta_g)_{g \in G} are positive weights for the groups
+
+fit to the data is measured through
+a convex loss function (w, b) 􏰀→ L(y, X, w, b) ∈ R+.
+
+\paragraph{Classification}
+
+logistic loss function
+
+\begin{equation}
+  P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
+
+  \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
+
+\end{equation}
+
+\lambda > 0.
+
+bias is omitted because \mathbf{X} and \mathbf{y}
+are mean-centered and unit-variance scaled.
+
+In this setting, and given a new fMRI volume x,
+we make predictions by choosing the label that maximizes
+the class-conditional probabil- ities (3.1), that is, argmaxk∈{1,...,c}Prob(y = k|x; W∗, b∗)
+
+One-versus-rest scheme
+
+\paragraph{Regression}
+
+squared error as loss
+
+\begin{equation}
+  \argmin \frac{1}{2}||\mathbf{y - Xw}||_2^2 + \lambda\Omega(\mathbf{w})
+\end{equation}
+
+\lambda > 0.
+
+Prediction for a new fMRI volume x is then simply performed by computing
+the dot product x⊤w∗
+
+\paragraph{Numerical optimization}
+
+Difficult because high-dimensional setting
+
+empirical risk minimization was performed by
+
+The intercept $b$ is left unregularized
+
 \begin{comment}
+
+\paragraph{Implementation.}
+The analyses were performed in Python.
+We used \textit{nilearn} to handle
+the large quantities of neuroimaging data 
+\cite{abrah14}
+and
+\textit{Theano} for automatic, numerically stable
+differentiation of symbolic computation graphs
+\cite{bastien2012theano, bergstra2010theano}.
+All Python scripts that generated the results are
+accessible online for reproducibility and reuse
+% (\url{http://github.com/anonymous/anonymous}).
+(\url{http://github.com/banilo/nips2015}).
 
@@
 
-\paragraph{Implementation.}
-The analyses were performed in Python.
-We used \textit{nilearn} to handle
-the large quantities of neuroimaging data 
-\cite{abrah14}
-and
-\textit{Theano} for automatic, numerically stable
-differentiation of symbolic computation graphs
-\cite{bastien2012theano, bergstra2010theano}.
-All Python scripts that generated the results are
-accessible online for reproducibility and reuse
-% (\url{http://github.com/anonymous/anonymous}).
-(\url{http://github.com/banilo/nips2015}).
-
 \section{Experimental Results}
@@
 \section{Discussion}
+
+exploit known structure for variable selection and prediction
+in classification and regression
 
@@
 
+alternatives would be dimensionality reduction
+and dictionary learning
+
 curse of dimensionality has classically been circumvented
@@
 
+More generally, our regularization scheme could also be used for various
+learning tasks, as soon
+as prior knowledge on the structure of the sparse representation
+is available, e.g.,
+for multiple kernel learning (Micchelli and Pontil, 2006),
+multi-task learning (Argyriou et al., 2008; Obozinski et al., 2009;
+Kim and Xing, 2009) and sparse matrix factorization
+problems (Mairal et al., 2010; Jenatton et al., 2010).
+
+this type of prior knowledge is of clear interest for the spatially and tempo-
+rally structured data typical in bioinformatics, computer vision and neuroscience applications
+
+structured sparsity can even be used for
+unsupervised data modelling,
+such as in PCA \cite{jenatton2009structured}
+
 \paragraph{Acknowledgment}

### 2015-12-08 paper/paper.tex
last

@@
 extend trend in stastical modelling from
-genetics \cite{rapaport2008classification, kim2012tree},
-natural image processing \cite{harzallah2009combining}
+processing of auditory signals \cite{daudet2004sparse},
+natural images \cite{harzallah2009combining} and
+videos \cite{kang2015structured, kim2010sparse}
+to
+genetics \cite{rapaport2008classification, kim2012tree}
+and
+conformational dynamics of protein complexes \cite{jenatton2009structured}.
+
+tructured-sparsity-inducing penalty
 
@@
 
+imposing parsimony
 integrative processes
@@
 
+representing some phenomenon with as few variables as possible
+
 neurobiologically motivated restrictions to complexity circumvented
@@
 If meaningful structures exist,
-ÇÇçwe show that one can take advantage of such structures
+we show that one can take advantage of such structures
+
+Statistically,
+l1 and l2 are local sparsity priors
+-> resulting sparsity does yield structure
+we want to priviledge representations with structure
+
+=> 
+ a biologically and statistically desirable bias
 
@@
 
+Group-sparsity is a first step towards the more general idea that
+a regularization function can encourage sparse solutions with a particular structure.
+
 structured regularization
@@
 
+groups at multiple granularity
+
+tree-guided group lasso
+
+encourage structured shrinkage effect
+
 l1 = unstructured sparsity-inducing penalty
+
+Our method extends the L1/L2 penalty to the tree-lasso penalty
+by letting the hierarchically-defined groups overlap. 
+the tree lasso is a special case of overlapping group lasso
 
@@
 
+Among a collection of plausible models,
+the simplest one should be preferred
+
 curse of dimensionality has classically been circumvented
@@
 
+Differences to Bertrands structured sparsity paper:
+- they derive the tree from the data, we use a priori knowledge from
+the existing literature
+-
+
 \paragraph{Acknowledgment}

### 2015-12-31 paper/paper.tex
blah

@@
 to
-genetics \cite{rapaport2008classification, kim2012tree}
+genetics \cite{rapaport2008classification, kim2012tree},
+astrophysics \cite{vinci2014estimating},
 and
@@
 integrative processes
+
+ This L1/L2 norm for group lasso has been extended to a more general setting to
+
+designed groups
+ the child nodes enter the set of relevant inputs only if its parent node does.
 
@@
 a regularization function can encourage sparse solutions with a particular structure.
+
+it is not realistic to assume that all of the tasks share the same set of rele- vant inputs as in the L1/L2-regularized regression.
+A subset of highly related outputs may share a common set of relevant inputs, whereas weakly related outputs are less likely to be affected by the same inputs.
 
@@
 
+Among a collection of plau- sible models, the simplest one is often preferred
+
 Functional specialization and functional integration
@@
 an organism's repertoire of mental operations.
+
+However, in the problem of multi-task regression, where the output is a multivariate vector with an internal sparsity struc- ture, the estimation of the regression parameters can potentially benefit from taking into account this spar- sity structure in the estimation process.
+This will allow the strongly related output variables to be mapped to the input factors in a synergistic way, which is not possible in the standard lasso.
 

### 2016-01-19 paper/paper.tex
added 3 figs+captions

@@
 
-\title{Region-network sparsity priors for\\
-high-dimensional inference in fMRI data}
+\title{Region-network hierarchical sparsity priors for\\
+high-dimensional inference in brain imaging}
 
@@
 
-\author{Danilo Bzdok, Karl Zilles, Michael Eickenberg,
+\author{Danilo Bzdok, Michael Eickenberg,
   Ga\"el Varoquaux, Bertrand Thirion\\
@@
 \textbf{\\keywords}:
-Brain Imaging, Functional Specialization, Functional Integration,
-Sparsity-inducing Norms, Structured Sparsity,
-Numerical Optimization, Systems Neuroscience
+Sparsity-inducing Norms, Structured Sparsity, Numerical Optimization,
+Systems Neuroscience, Brain Imaging,
+Functional Specialization, Functional Integration
 
@@
 
-\begin{comment}
-
 \paragraph{Implementation.}
@@
 \paragraph{Serial versus parallel structure discovery and classification.}
+\paragraph{Serial versus parallel structure discovery and classification.}
+\paragraph{Serial versus parallel structure discovery and classification.}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_prior.pdf}
+\end{centering}
+\vspace{-0.5cm}
+\caption{\textbf{Building blocks of the region-network tree.}
+Depicts neurobiological priors introduced into supervised estimation
+by means of hierarchical structured sparsity.
+\textit{Left:} Continuous, partially overlapping brain network priors
+(\textit{hot-colored}, taken from \cite{smith2009})
+accommodate the functional integration
+perspective of functional brain organization.
+\textit{Right:} Discrete, non-overlapping brain region priors
+(\textit{single-colored}, taken from \cite{crad12})
+accommodate the functional segregation perspective.
+\textit{Middle:} These predefined voxel groups are incorporated
+into hierarchical priors of brain networks with their
+assigned brain regions.
+\textit{Top to bottom:} Four examplary region-network priors
+are shown.
+They include the early cortex that processes
+visual and sound information from the environment,
+a well-known attentional circuit in the left brain hemisphere,
+and
+the cerebellum that realizes motor behavior.
+}
+\label{fig_priors}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/dataratio.pdf}
+\end{centering}
+\vspace{-0.5cm}
+\caption{\textbf{Ordinary versus structured sparse model estimation
+as a function of training set size.}
+Ordinary $ell_1$-penalized logistic regression
+(\textit{upper row})
+is compared
+to logistic regression estimation structured
+by hierarchical tree prior
+(\textit{lower row})
+with increasing fraction (\textit{columns})
+of the available training data.
+Unthresholded coronal maps of model weights are
+shown for comparison against
+the class-wise mean neural activty
+in the \textit{rightmost column}.
+The 18-class out-of-sample performance in percent.
+%
+In the data-scarce scenario,
+typical for common brain imaging studies,
+hierarchical tree sparsity achieves
+better support recovery with the biggest difference
+in model performance comparing to
+$ell_1$-penalized logistic regression.
+%
+In the data-riche scenario,
+neurobiologically informed logistic regression
+profits more from the increased information quantities than
+neurobiologically naive logistic regression.
+}
+\label{fig_dataratio}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
+\end{centering}
+\vspace{-0.5cm}
+\caption{\textbf{Support recovery as a function of
+region and network emphasis.}
+The relative impact of the region and network priors
+on model selection
+is systematically varied against each other.
+This region-network ratio (\textit{upper row}) weighted voxel groups
+to priviledge sparse models in function space
+that acknowledge known data neighborhoods underlying brain region
+(\textit{left columns}) or
+known compartments in the data that correspond to brain networks
+(\textit{right columns}).
+Among the 18 classes, the model weights are shown for the
+tasks (\textit{from top to bottom}) tongue movement, listening stories,
+taking somebody else's perspective (ToM, "theory of mind"),
+as well as
+perceiving locations and tools.
+The 18-class out-of-sample performance is indicated
+on the \textit{bottom} and
+the class-wise mean neural activty
+in the \textit{rightmost column}.
+%
+Different emphasis on regions versus networks
+in hierarchical structured sparsity can
+yield essentially similar model performance.
+%
+Priviledging region versus network structure during model selection
+recovers complementary aspects of the brain activity pattern.
+%
+Equal region and network emphasis yields more dispersed,
+less interpretable predictive model choices.
+}
+\label{fig_ratio}
+\end{figure}
+
+DATARATIO
+
+tell #maps per percent
 
@@
 Further support was received from
-the German National Academic Foundation (D.B.)
+the German National Academic Foundation (D.B.),
+the German Research Foundation (BZ2/2-1 and BZ2/3-1 to D.B.),
 and the MetaMRI associated team (B.T., G.V.).
 }
-
-\end{comment}
 

### 2016-01-21 paper/paper.tex
intro+disc somewhat done

@@
 \textbf{\\keywords}:
-Sparsity-inducing Norms, Structured Sparsity, Numerical Optimization,
-Systems Neuroscience, Brain Imaging,
-Functional Specialization, Functional Integration
+Sparsity-inducing norms, hierarchical structured sparsity,
+numerical optimization,
+systems neuroscience, brain imaging,
+functional specialization, functional integration
 
@@
 more variables per observation than
-total observations available in a data sample.
-This scenario challenges many statistical estimators from
+total observations per data sample.
+This high-dimensional scenario challenges many statistical estimators from
 classical statistics.
 For instance,
-linear regression models without additional assumptions
-yield an infinity of possible coefficients
+the general linear model without additional assumptions
+yields an infinity of possible coefficients
 and, thus, no solution.
 %
-\textit{Sparsity} assumptions have consequently been
-introduced and made many ill-posed estimation problems tractable
+Many such ill-posed estimation problems
+have become tractable by means of
+\textit{sparsity} assumptions
 \cite{buhlmann2011statistics, hastie2015statistical}.
-Domain-specific structure can be imposed on the 
-statistical estimation,
-thus preassuming that variables have unequal importance
-and follow existing knowledge
-\cite{bach2012optimization}.
 Sparsified supervised and unsupervised
@@
 %
+Further, \textit{structured sparsity} can impose
+domain knowledge on the 
+statistical estimation,
+thus preassuming the variables to have unequal importance
+and to obey expected data distributions
+\cite{bach2012optimization}.
 Yet, what neurobiological structure suggests itself
-to successfully tackle the
-\textit{curse of dimensionality} in
-functional neuroimaging research?
+to harness the
+\textit{curse of dimensionality} with
+$\textgreater$100,000 variables
+in neuroimaging research?
 
@@
 Functional specialization emphasizes that microscopically distinguishable
-brain regions probably solve distinct classes of computational processes
+brain regions solve distinct classes of computational processes
 \cite{kanwisher2010functional}.
 Functional integration, in turn, emphasizes that brain function
-is probably enabled by complex connections between these
+is enabled by complex connections between these
 distinct brain regions \cite{sporns14nn}.
@@
 These notions were predominantly derived from
-invasive examination of \textit{structure} (i.e., histological preparation),
-\textit{connectivity}, (i.e., axonal tracing),
-and \textit{functional properties}
-(i.e., single cell recordings) in same animals.
+invasive examination of anatomy (i.e., histological preparation),
+connectivity, (i.e., axonal tracing),
+and functional properties
+(i.e., single cell recordings) in animals.
 Regarding functional segregation into specialized regions,
@@
 Both
-local cyto- and chemoarchitectonic infrastructure
+local
+%cyto- and chemoarchitectonic
+infrastructure
 and its unique global connectivity profile
-together realize computational processes (i.e., function).
-While
-cortical modules versus connections between those
+together are thought to realize brain function.
+%
+In sum,
+cortical brain modules versus connections between those
 reflect 
 functional specialization versus functional integration
-\cite{friston2002beyond, mesulam_sensation},
-both architectural principles are conceptually inextricable when
-explaining the emergence of mental operations
+\cite{friston2002beyond, mesulam_sensation}.
+Importantly,
+probably no existing brain analysis method acknowledges that
+both architectural principles are inextricably involved
+in the realization of mental operations
 \cite{tononi1998complexity, saygin2012}.
@@
 \cite{hubel1962receptive, zeki1978functional}.
-Tissue lesion of the mid-fusiform gyrus of the visual system
-were frequently reported to impair
+Tissue lesion of the mid-fusiform gyrus of the visual system,
+for instance,
+was frequently reported to impair
 recognition of others' identity from faces
 \cite{iaria2008contrib}.
-The localization of
-sensory, motor, and emotional cognitive functions to cortical areas
-in the living brain
+The whole-brain localization of
+sensory, motor, and emotional functions to cortical areas
+% in the living brain
 has later been enabled by
@@
 Further,
-radioactive mapping of neurotransmitter receptor distributions
+radioactive mapping of neurotransmitter receptors
 rendered accessible yet another
@@
 which can partly be more fine-grained than
-classical cytoarchitectonic borders
+classical microscopical borders
 \cite{behrens03, cbp2015review}.
 Today,
-high-thoughput computing enables 
+high-thoughput approaches enable
 ultahigh-resolution 3D models of brain anatomy
-at macroscopical to near-cellular scale
+at near-cellular scale
 \cite{amunts2013bigbrain}.
@@
 non-overlapping, discrete region compartments
-as the basic architectonic framework of brain organization.
+as the basic architecture of brain organization.
 
@@
 in systems neuroscience \cite{yuste2015, stephan_dys}.
-The higher the processing hierarchy level,
-the more a cortical area is known to
-connect to different large-scale networks
-\cite{yeo11}.
 %
 Invasive axonal tracing studies in monkeys were complemented
-by in-vivo diffusion MRI tractography in humans
+by diffusion MRI tractography in humans
 as a now frequently employed method to
@@
 became the workhorses of network discovery
-in functional neuroimaging.
+in neuroimaging.
 These revealed the important implication of
@@
 Characteristic changes in the configuration of
-these large-scale networks
+these macroscopical networks
 were repeatedly observed to be induced
@@
 overlapping network compartments
-as the basic architectonic framework of brain organization,
+as the basic architecture of brain organization,
 in stark constrast to methods examining regional specialization.
@@
 % study
-Building on these interpretational traditions,
+Building on these two major interpretational streams in systems neuroscience,
 the present study proposes to incorporate
-known architectonic aspects from both
-anatomical segregation and integration
-into unified classification and regression algorithms
-by means  of structured sparsity assumptions.
-The "true" relative importance of 
-local region compartments and global network compartments
-is typically unknown
-but
-probably varying in degree
-across diverse neuroscientific questions.
-Recent advances in multivariate statistical learning techniques
-enable such adaptive estimators with
-neurobiologically plausible region and network priors.
-Using a large reference dataset,
-we demonstrated that domain-informed supervised models
-gracefully handle the curse of dimensionality,
-yield many more human-interpretable results,
-and generalize better to new samples
-than domain-na\"ive models.
-
-higher-order prior knowledge
-
-structured sparsity
-extend trend in stastical modelling from
-processing of auditory signals \cite{daudet2004sparse},
+established neurobiological structure underlying
+functional segregation and integration
+into supervised estimators
+by hierarchical structured sparsity.
+% The "true" relative importance of 
+% local region compartments and global network compartments
+% is typically unknown
+% but
+% probably varying in degree
+% across diverse neuroscientific questions.
+%
+Learning techniques
+exploiting structured sparsity 
+have recently made much progress in various application domains
+from processing of auditory signals \cite{daudet2004sparse},
 natural images \cite{harzallah2009combining} and
@@
 conformational dynamics of protein complexes \cite{jenatton2009structured}.
-
-tructured-sparsity-inducing penalty
-
-to brain imaging domain.
+%
+This is extended by the present work that
+enables neuroscience-specific estimators capitalizing on
+neurobiologically plausible region and network priors.
+%
+Using a large reference dataset,
+we demonstrated that domain-informed supervised models
+gracefully tackle the curse of dimensionality,
+yield more human-interpretable results,
+and generalize better to new samples
+than domain-na\"ive estimators.
 
@@
 \section{Discussion}
+Relevant structure in brain imaging data has long been
+separately investigated
+along two distinct organizational principles:
+functional segregation into discrete brain regions
+and functional integration by inter-regional brain networks.
+%
+This paper demonstrates the simultaneous exploitation of
+both these neurobiological compartments
+for sparse variable selection and high-dimensional prediction.
+%
+Introducing existing domain knowledge into model selection
+naturally priviledges model hypotheses in the function space
+that are most neurobiologically plausible.
+%
+The neurobiologically informed
+hierarchical structured sparsity penalty is shown to enhance
+model interpretability and generalization performance,
+although these statistical goals are typically in conflict.
 
-exploit known structure for variable selection and prediction
-in classification and regression
-
-Among a collection of plau- sible models, the simplest one is often preferred
-
-Functional specialization and functional integration
-in the human brain are
-probably both mechanistically relevant for emerging behavior.
-However, there is a scarcity of statistical methods
-that concomitantly relate brain regions and networks to
-an organism's repertoire of mental operations.
-
-However, in the problem of multi-task regression, where the output is a multivariate vector with an internal sparsity struc- ture, the estimation of the regression parameters can potentially benefit from taking into account this spar- sity structure in the estimation process.
-This will allow the strongly related output variables to be mapped to the input factors in a synergistic way, which is not possible in the standard lasso.
-
+1) each voxel
 We assume regions and networks but can estimate 
 importance of each voxel.
-
 neurobiologically motivated restrictions to
@@
 for useful, simplified views on brain function.
+previously laborious feature engineering / selection procedures
 
-The same classification performance can be reached by
-many different models -> we naturally want to priviledge those
-among the equally performing models that are closest to
-what we know about the brain
-
--> interpreta bility and accuracy typically exclude each other
-(cf. Hastie)
-
-alternatives would be dimensionality reduction
-and dictionary learning
-
-Among a collection of plausible models,
-the simplest one should be preferred
-
-curse of dimensionality has classically been circumvented
-by treating a high-dimensional problem
-as a mass-univariate problem.
-Problem was postponed to the inference step
-this is why we never solved the multiple comparisons problem in fMRI
-
-regularization with sparsity penalties
-restrictions to complexity according to neurobiological facts
+2) restrictions to complexity according to neurobiological facts
 -> bias-variance tradeoff: negigible increase in bias but large decrease in variance
@@
 
+3)
 multiple comparisons problem has the curse of dimensionality
@@
 
-OUTLOOK:
-robust high-dimensional inference will be key
-to prediction in single individual,
-such as for personalized medicine
-\cite{gabrieli2015prediction}
+4) region-constrained or network-constrained model estimation
+can lead to similar predictive performance
 
-More generally, our regularization scheme could also be used for various
-learning tasks, as soon
-as prior knowledge on the structure of the sparse representation
-is available, e.g.,
-for multiple kernel learning (Micchelli and Pontil, 2006),
-multi-task learning (Argyriou et al., 2008; Obozinski et al., 2009;
-Kim and Xing, 2009) and sparse matrix factorization
-problems (Mairal et al., 2010; Jenatton et al., 2010).
-
-this type of prior knowledge is of clear interest for the spatially and tempo-
-rally structured data typical in bioinformatics, computer vision and neuroscience applications
-
-structured sparsity can even be used for
-unsupervised data modelling,
-such as in PCA \cite{jenatton2009structured}
-
-Differences to Bertrands structured sparsity paper:
-- they derive the tree from the data, we use a priori knowledge from
-the existing literature
--
+In the future,
+the proposed regularization scheme can be used for various
+learning tasks in systems neuroscience.
+This includes supervised classification and regression
+with one or several target variables.
+%
+Region-network sparsity priors could even be used to inform
+unsupervised statistical estimators,
+including principal component analysis
+\cite{jenatton2009structured}
+and
+k-means clustering \cite{???}.
+%
+Additionally,
+the structured sparsity penalty could be extended
+from the spatial domain of neural activity to
+spatiotemporally coherent neural activity patterns
+\cite{gramfort2011tracking}.
+%
+Ultimately,
+successful high-dimensional inference is
+an important prerequisite
+for prediction of diagnosis,
+disease trajectories, and treatment responses
+for personalized medicine in psychiatry and neurology
+\cite{gabrieli2015prediction}.
 

### 2016-01-23 paper/paper.tex
temp

@@
 
+all algorithm from a same software library -> SPAMs
+
 %
@@
 \end{centering}
-\vspace{-0.5cm}
+\vspace{-0.6cm}
 \caption{\textbf{Building blocks of the region-network tree.}
-Depicts neurobiological priors introduced into supervised estimation
-by means of hierarchical structured sparsity.
+Depicts neurobiological priors introduced into the supervised classification
+by hierarchical structured sparsity.
 \textit{Left:} Continuous, partially overlapping brain network priors
@@
 accommodate the functional integration
-perspective of functional brain organization.
+perspective of brain organization.
 \textit{Right:} Discrete, non-overlapping brain region priors
@@
 accommodate the functional segregation perspective.
-\textit{Middle:} These predefined voxel groups are incorporated
-into hierarchical priors of brain networks with their
-assigned brain regions.
+\textit{Middle:} These two types of predefined voxel groups are incorporated
+into hierarchical priors of parent networks with their
+descending region nodes.
 \textit{Top to bottom:} Four examplary region-network priors
-are shown.
-They include the early cortex that processes
+are shown, including
+the early cortex that processes
 visual and sound information from the environment,
@@
 \end{centering}
-\vspace{-0.5cm}
-\caption{\textbf{Ordinary versus structured sparse model estimation
-as a function of training set size.}
-Ordinary $ell_1$-penalized logistic regression
+\vspace{-0.6cm}
+\caption{\textbf{Na\"ive versus informed sparse model selection
+across training set sizes.}
+Ordinary $\ell_1$-penalized logistic regression
 (\textit{upper row})
 is compared
-to logistic regression estimation structured
-by hierarchical tree prior
+to hierarchical-tree-penalized logistic regression
 (\textit{lower row})
-with increasing fraction (\textit{columns})
-of the available training data.
-Unthresholded coronal maps of model weights are
-shown for comparison against
-the class-wise mean neural activty
+with increasing fraction
+of the available training data (\textit{columns}).
+For one example from 18 classes,
+unthresholded coronal maps of model weights
+are shown for comparison against
+the class sample average
 in the \textit{rightmost column}.
-The 18-class out-of-sample performance in percent.
+The corresponding 18-class (``View tools'')
+out-of-sample accuracy
+is given in percent.
 %
 In the data-scarce scenario,
-typical for common brain imaging studies,
+typical for brain imaging,
 hierarchical tree sparsity achieves
 better support recovery with the biggest difference
-in model performance comparing to
-$ell_1$-penalized logistic regression.
+in model performance.
 %
-In the data-riche scenario,
+In the data-rich scenario,
 neurobiologically informed logistic regression
@@
 \end{centering}
-\vspace{-0.5cm}
+\vspace{-0.6cm}
 \caption{\textbf{Support recovery as a function of
@@
 to priviledge sparse models in function space
-that acknowledge known data neighborhoods underlying brain region
+that acknowledge known brain region neighborhoods
 (\textit{left columns}) or
-known compartments in the data that correspond to brain networks
+known brain networks compartments
 (\textit{right columns}).
 Among the 18 classes, the model weights are shown for the
-tasks (\textit{from top to bottom}) tongue movement, listening stories,
+tasks (\textit{from top to bottom}): tongue movement, listening stories,
 taking somebody else's perspective (ToM, "theory of mind"),
 as well as
-perceiving locations and tools.
-The 18-class out-of-sample performance is indicated
+viewing locations and tools.
+The 18-class out-of-sample accuracy is indicated
 on the \textit{bottom} and
@@
 
-DATARATIO
+\paragraph{Sample complexity of na\"ive versus informed sparse model selection.}
+Subsequently, the sample complexity of
+$\ell_1$-penalized and hierarchical-tree-penalized logistic regression
+were quantitatively compared (Figure \ref{fig_dimred}).
+Region-network priors should bias/guide model selection towards more
+neurobiologically plausible classification estimators.
+This should yield better out-of-sample generalization and
+support recovery than
+$\ell_1$-constrained logistic regression na\"ive to neurobiology
+in the data-scarce and data-rich scenarios.
+%
+The HCP task data from 18 tasks was first divided into
+90\% training set (i.e., 7584 maps) and
+10\% test set (i.e., 842 maps).
+Both learning algorithms were fed by the
+training set that was subsampled to fractions of
+25\% (X neural activity maps),
+50\% (Y maps),
+75\% (Z maps).
+The estimators were submitted to a nested cross-validation scheme
+for model selection and assessment.
 
-tell #maps per percent
+In the inner CV layer, the logistic regression estimators
+have been fitted in a one-versus-rest design that
+distinguishes each class from
+the respective other 17 classes
+(number of maximal iterations=100, tolerance=$0.001$).
+
+In the out CV layer, grid search
+
+A grid of $\lambda$ candidates was searched between $10^-2$ and $10$
+in 9 steps on a log scale.
+
+evaluated on the allows same test set
+
+\paragraph{Support recovery as a function of region and network emphasis.}
 
@@
 -> VC: decrease complexitiy capactiy -> better chance for generalization out of sample
+
+guide model selection
 
@@
 
-\paragraph{Acknowledgment}
+\paragraph{Acknowledgment.}
 {\small The research leading to these results has received funding from the

### 2016-01-23 struct_estimator_zeroreglevel.py

@@ -53,9 +53,10 @@ FORCE_TWO_CLASSES = False
 MY_MAX_IT = 100
 MY_DATA_RATIO = 100
 N_JOBS = 1
-LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
+# LAMBDA_GRID = np.linspace(0.1, 1.0, 10)
+LAMBDA_GRID = np.logspace(-2, 1, 9)
 
-RES_NAME = 'srne_benchmark_zeronetlevel'
+RES_NAME = 'srne_benchmark_zeronetlevel_loggrid'
 if FORCE_TWO_CLASSES:
     RES_NAME += '_2cl'
 WRITE_DIR = op.join(os.getcwd(), RES_NAME)

### 2016-01-23 paper/paper.tex
1st results passage done

@@
 $\ell_1$-penalized and hierarchical-tree-penalized logistic regression
-were quantitatively compared (Figure \ref{fig_dimred}).
-Region-network priors should bias/guide model selection towards more
+were quantitatively compared (Figure \ref{fig_dataratio}).
+Region-network priors should bias model selection towards more
 neurobiologically plausible classification estimators.
@@
 %
-The HCP task data from 18 tasks was first divided into
-90\% training set (i.e., 7584 maps) and
-10\% test set (i.e., 842 maps).
-Both learning algorithms were fed by the
-training set that was subsampled to fractions of
-25\% (X neural activity maps),
-50\% (Y maps),
-75\% (Z maps).
-The estimators were submitted to a nested cross-validation scheme
-for model selection and assessment.
-
+The HCP task data with examples from 18 classes were first divided into
+90\% of training set (i.e., 7584 neural activity maps) and
+10\% of test set (i.e., 842 maps).
+Both learning algorithms were fitted based on the
+training set at different subsampling fractions:
+20\% (1516 maps),
+40\% (3033 maps),
+60\% (4550 maps),
+80\% (6067 maps), and
+100\% (7584 maps).
+The stratified and shuffled training data were submitted to
+to a nested cross-validation scheme
+for model selection and model assessment.
 In the inner CV layer, the logistic regression estimators
-have been fitted in a one-versus-rest design that
+have been trained in a one-versus-rest design that
 distinguishes each class from
-the respective other 17 classes
-(number of maximal iterations=100, tolerance=$0.001$).
-
-In the out CV layer, grid search
-
-A grid of $\lambda$ candidates was searched between $10^-2$ and $10$
-in 9 steps on a log scale.
-
-evaluated on the allows same test set
+the respective 17 other classes
+(number of maximal iterations=$100$, tolerance=$0.001$).
+In the outer CV layer, grid search
+selected among candidates for the respective $\lambda$ parameter
+by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
+Importantly, the thus selected sparse logistic regression classifier was
+evaluated on an identical test set in all settings.
+%
+Three observation have been made.
+In the data-scarce scenario (i.e., 1/5 of actual training data),
+hierarchical tree sparsity achieved the biggest advantage
+in out-of-sample performance by 5,11\% as well as
+better support recovery with weight maps already much closer
+to the training data average.
+In the case of scarce training data, which is typical for the brain imaging domain,
+regularization by region-network priors indeed allowed for
+more effective extraction of classification-relevant structure
+from the neural activity scans.
+%
+Across scenarios,
+the weight maps from ordinary logistic regression exhibit
+higher variance and many more zero coefficients
+than hierarchical tree logistic regression.
+Given the usually high multicollinearity in neuroimaging data,
+this observation is likely to reflect instable selection of
+representatives among class-responsive predictor groups
+due to the $\ell_1$-norm penalization.
+%
+In the data-rich scenario (i.e., entire training data used for model fitting),
+neurobiologically informed logistic regression
+profits more from the increased information quantities than
+neurobiologically naive logistic regression.
+That is, the region-network priors actually further enhance the similarity
+to the weight maps even in abundant input data.
+This was the case although
+the maximal classification performance of $\approx$90\% has already
+been reached with small training data fractions by the structured estimator.
+In contrast, 
+the unstructured estimator reached this generalization performance
+only with bigger input data quantities.
 

### 2016-01-24 paper/paper.tex
make it compile

@@
 \DeclareMathOperator{\dist}{dist} % The distance.
-\DeclareMathOperator{\argmin}{argmin}
+%\DeclareMathOperator{\argmin}{argmin}
 \DeclareMathOperator{\argmax}{argmax}
@@
 $\Omega$ exerts $\ell_1$-like variable selection on
-the (||\mathbf{w}_g||_2)_{g\inG} groups,
+the $(||\mathbf{w}_g||_2)_{g\in G}$ groups,
 yielding a maximum of $g \in G$ to be zeroed out
@@
 
-(\eta_g)_{g \in G} are positive weights for the groups
+$(\eta_g)_{g \in G}$ are positive weights for the groups
 
@@
   P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
-
   \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
-
 \end{equation}
 
-\lambda > 0.
+$\lambda > 0$
 
-bias is omitted because \mathbf{X} and \mathbf{y}
+bias is omitted because $\mathbf{X} and \mathbf{y}$
 are mean-centered and unit-variance scaled.
@@
 
-\lambda > 0.
+$\lambda > 0$
 

### 2016-01-24 paper/paper.tex
cosm

@@
 Many quantitative scientific domains underwent a
-recent passage from the classical regime (i.e., "long data")  to
-the high-dimensional regime (i.e., "wide data")
+recent passage from the classical regime (i.e., ``long data")  to
+the high-dimensional regime (i.e., ``wide data")
 \cite{jordan2015massive}.

### 2016-01-24 paper/paper.tex
comment

@@
 For instance,
-the general linear model without additional assumptions
-yields an infinity of possible coefficients
-and, thus, no solution.
+the estimation of any generalized linear model without additional assumptions
+becomes underdetermined, i.e. yields full subspace of possible solutions, many or most of which will not generalize well in a predictive setting.
 %
 Many such ill-posed estimation problems
-have become tractable by means of
+have benefited from
 \textit{sparsity} assumptions
-\cite{buhlmann2011statistics, hastie2015statistical}.
-Sparsified supervised and unsupervised
+\cite{buhlmann2011statistics, hastie2015statistical}, which act as a 
+regularizer and can be used for model selection.
+Sparse supervised and unsupervised
 learning algorithms have proven to yield
@@
 %
-Further, \textit{structured sparsity} can impose
+Generally, \textit{structured sparsity} can impose
 domain knowledge on the 
@@
 \cite{bach2012optimization}.
+{\color{red}Michael: This is the definition of a prior, not of strutured sparsity}
 Yet, what neurobiological structure suggests itself

### 2016-01-24 paper/paper.tex
rephrased

@@
 {\color{red}Michael: This is the definition of a prior, not of strutured sparsity}
-Yet, what neurobiological structure suggests itself
-to harness the
-\textit{curse of dimensionality} with
-$\textgreater$100,000 variables
-in neuroimaging research?
+
+%% Yet, what neurobiological structure suggests itself
+%% to harness the
+%% \textit{curse of dimensionality} with
+%% $\textgreater$100,000 variables
+%% in neuroimaging research?
+In neuroimaging research, generalized linear models predicting external 
+variables from brain images, which can reach a dimensionality of several
+hundreds of thousands of voxels, necessarily need appropriate regularization.
+Which neurobiological prior knowledge lends itself to the construction of a
+structured sparse prior?
 

### 2016-01-24 paper/paper.tex
detail

@@
 In sum,
-cortical brain modules versus connections between those
+cortical brain modules versus connections between them
 reflect 
@@
 % in the living brain
-has later been enabled by
+was later enabled by
 non-invasive brain imaging with

### 2016-01-24 paper/paper.tex
typo

@@
 high-thoughput approaches enable
-ultahigh-resolution 3D models of brain anatomy
+ultrahigh-resolution 3D models of brain anatomy
 at near-cellular scale
@@
 by the onset of given cognitive tasks \cite{fransson2006}.
-Such task-induced mechanisms orchastrating supraordinate networks
+Such task-induced mechanisms orchestrating supraordinate networks
 might be subserved by the right anterior insula \cite{sridh2008}

### 2016-01-24 paper/paper.tex
small correction

@@
 For one example from 18 classes,
-unthresholded coronal maps of model weights
+unthresholded axial maps of model weights
 are shown for comparison against
-the class sample average
+the class sample average {\color{red} thresholded at p $<$ 0.01 ???}
 in the \textit{rightmost column}.

### 2016-01-24 paper/paper.tex
typos

@@
 on model selection
-is systematically varied against each other.
+is systematically varied against each other {\color{red} HOW??}.
 This region-network ratio (\textit{upper row}) weighted voxel groups
-to priviledge sparse models in function space
+to privilege sparse models in function space
 that acknowledge known brain region neighborhoods
@@
 on the \textit{bottom} and
-the class-wise mean neural activty
+the class-wise mean neural activity
 in the \textit{rightmost column}.
@@
 %
-Priviledging region versus network structure during model selection
+Privileging region versus network structure during model selection
 recovers complementary aspects of the brain activity pattern.

### 2016-01-25 paper/paper.tex
blah

--- 2016-01-24 paper/paper.tex
@@
 \DeclareMathOperator{\dist}{dist} % The distance.
-%\DeclareMathOperator{\argmin}{argmin}
+\DeclareMathOperator{\argmin}{argmin}
 \DeclareMathOperator{\argmax}{argmax}
@@
 Many quantitative scientific domains underwent a
-recent passage from the classical regime (i.e., ``long data")  to
-the high-dimensional regime (i.e., ``wide data")
+recent passage from the classical regime (i.e., "long data")  to
+the high-dimensional regime (i.e., "wide data")
 \cite{jordan2015massive}.
@@
 For instance,
-the estimation of any generalized linear model without additional assumptions
-becomes underdetermined, i.e. yields full subspace of possible solutions, many or most of which will not generalize well in a predictive setting.
+the general linear model without additional assumptions
+yields an infinity of possible coefficients
+and, thus, no solution.
 %
 Many such ill-posed estimation problems
-have benefited from
+have become tractable by means of
 \textit{sparsity} assumptions
-\cite{buhlmann2011statistics, hastie2015statistical}, which act as a 
-regularizer and can be used for model selection.
-Sparse supervised and unsupervised
+\cite{buhlmann2011statistics, hastie2015statistical}.
+Sparsified supervised and unsupervised
 learning algorithms have proven to yield
@@
 %
-Generally, \textit{structured sparsity} can impose
+Further, \textit{structured sparsity} can impose
 domain knowledge on the 
@@
 \cite{bach2012optimization}.
-{\color{red}Michael: This is the definition of a prior, not of strutured sparsity}
-
-%% Yet, what neurobiological structure suggests itself
-%% to harness the
-%% \textit{curse of dimensionality} with
-%% $\textgreater$100,000 variables
-%% in neuroimaging research?
-In neuroimaging research, generalized linear models predicting external 
-variables from brain images, which can reach a dimensionality of several
-hundreds of thousands of voxels, necessarily need appropriate regularization.
-Which neurobiological prior knowledge lends itself to the construction of a
-structured sparse prior?
+Yet, what neurobiological structure suggests itself
+to harness the
+\textit{curse of dimensionality} with
+$\textgreater$100,000 variables
+in neuroimaging research?
 
@@
 In sum,
-cortical brain modules versus connections between them
+cortical brain modules versus connections between those
 reflect 
@@
 % in the living brain
-was later enabled by
+has later been enabled by
 non-invasive brain imaging with
@@
 high-thoughput approaches enable
-ultrahigh-resolution 3D models of brain anatomy
+ultahigh-resolution 3D models of brain anatomy
 at near-cellular scale
@@
 by the onset of given cognitive tasks \cite{fransson2006}.
-Such task-induced mechanisms orchestrating supraordinate networks
+Such task-induced mechanisms orchastrating supraordinate networks
 might be subserved by the right anterior insula \cite{sridh2008}
@@
 $\Omega$ exerts $\ell_1$-like variable selection on
-the $(||\mathbf{w}_g||_2)_{g\in G}$ groups,
+the (||\mathbf{w}_g||_2)_{g\inG} groups,
 yielding a maximum of $g \in G$ to be zeroed out
@@
 
-$(\eta_g)_{g \in G}$ are positive weights for the groups
+(\eta_g)_{g \in G} are positive weights for the groups
 
@@
   P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
+
   \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
+
 \end{equation}
 
-$\lambda > 0$
+\lambda > 0.
 
-bias is omitted because $\mathbf{X} and \mathbf{y}$
+bias is omitted because \mathbf{X} and \mathbf{y}
 are mean-centered and unit-variance scaled.
@@
 
-$\lambda > 0$
+\lambda > 0.
 
@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
-\end{centering}
-\vspace{-0.6cm}
-\caption{\textbf{Support recovery as a function of
-region and network emphasis.}
-The relative impact of the region and network priors
-on model selection
-is systematically varied against each other.
-This region-network ratio (\textit{upper row}) weighted voxel groups
-to priviledge sparse models in function space
-that acknowledge known brain region neighborhoods
-(\textit{left columns}) or
-known brain networks compartments
-(\textit{right columns}).
-Among the 18 classes, the model weights are shown for the
-tasks (\textit{from top to bottom}): tongue movement, listening stories,
-taking somebody else's perspective (ToM, "theory of mind"),
-as well as
-viewing locations and tools.
-The 18-class out-of-sample accuracy is indicated
-on the \textit{bottom} and
-the class-wise mean neural activty
-in the \textit{rightmost column}.
-%
-Different emphasis on regions versus networks
-in hierarchical structured sparsity can
-yield essentially similar model performance.
-%
-Priviledging region versus network structure during model selection
-recovers complementary aspects of the brain activity pattern.
-%
-Equal region and network emphasis yields more dispersed,
-less interpretable predictive model choices.
-}
-\label{fig_ratio}
-\end{figure}
-
 \paragraph{Sample complexity of na\"ive versus informed sparse model selection.}
@@
 only with bigger input data quantities.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
+\end{centering}
+\vspace{-0.6cm}
+\caption{\textbf{Support recovery as a function of
+region and network emphasis.}
+The relative impact of the region and network priors
+on model selection
+is systematically varied against each other.
+This region-network ratio (\textit{upper row}) weighted voxel groups
+to priviledge sparse models in function space
+that acknowledge known brain region neighborhoods
+(\textit{left columns}) or
+known brain networks compartments
+(\textit{right columns}).
+Among the 18 classes, the model weights are shown for the
+tasks (\textit{from top to bottom}): tongue movement, listening stories,
+taking somebody else's perspective (ToM, "theory of mind"),
+as well as
+viewing locations and tools.
+The 18-class out-of-sample accuracy is indicated
+on the \textit{bottom} and
+the class-wise mean neural activty
+in the \textit{rightmost column}.
+%
+Different emphasis on regions versus networks
+in hierarchical structured sparsity can
+yield essentially similar model performance.
+%
+Priviledging region versus network structure during model selection
+recovers complementary aspects of the brain activity pattern.
+%
+Equal region and network emphasis yields more dispersed,
+less interpretable predictive model choices.
+}
+\label{fig_regnetratio}
+\end{figure}
 

### 2016-01-26 paper/paper.tex
first complete results

--- 2016-01-24 paper/paper.tex
@@
 \section{Experimental Results}
-\paragraph{Serial versus parallel structure discovery and classification.}
-\paragraph{Serial versus parallel structure discovery and classification.}
-\paragraph{Serial versus parallel structure discovery and classification.}
 
@@
 \end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/sparsities.pdf}
+\end{centering}
+\vspace{-0.6cm}
+\caption{\textbf{Model performance across sparsity priors.}
+Compares the performance of 4 logistic regression estimators
+with different structured and unstructered sparsity terms
+in classifying neural activity from 18 psychological tasks.
+The class-wise precision and recall metrics
+were obtained on the test set.
+%
+Unstructured $\ell_1$-penalized logistic regression (\textit{upper left})
+imposed a minimum of relevant brain voxels without
+assuming special structure.
+Structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
+(\textit{lower left})
+imposed region compartments, but na\"ive to network structure.
+Structured trace-norm penalization (\textit{lower tight})
+imposed low-rank structure
+with sparsity of network patterns, but na\"ive to region structure.
+Structured $\ell_1/\ell_2$ block norm with a hierarchy of
+both region and network priors (\textit{upper tight})
+exhibited the best out-of-sample performance.
+%
+Consequently, a priori knowledge of both region and network neighborhoods
+was the most beneficial structured sparsity penalty.
+}
+\label{fig_sparsities}
+\end{figure}
+
+\paragraph{Benchmarking hierarchical tree sparsity against
+common sparsity penalties.}
+Hierarchical region-network priors have been systematically
+evaluated against other popular choices of sparse classification algorithms
+in an 18-class scenario
+(Figure \ref{fig_sparsities}).
+%
+Logistic regression with $\ell_1/\ell_2$ block norm penalization
+incorporated a hierarchy of previously known region and network neighborhoods
+for a neurobiological bias of the statistical estimation.
+%
+Vanilla logistic regression with $\ell_1$-penalization
+does not assume any previously known special structure.
+This classification estimator embraces a vision of neural activity structure
+that expectes a minimum of
+topographically and functionally independent brain voxel to be relevant.
+%
+Logistic regression with sparse group sparsity
+imposes a structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
+with a known atlas of region voxel groups onto the statistical estimation process.
+This supervised estimator shrinks and selects the coefficients
+of topographically compact voxel groups expected to be relevant together.
+%
+Logistic regression with trace-norm penalization
+imposed low-rank structure.
+This supervised classification algorithm
+expected a minimum of unknown network patterns
+to be relevant.
+%
+The stratified and shuffled training data were submitted to
+to a nested cross-validation scheme
+for model selection and model assessment.
+In the inner CV layer, the logistic regression estimators
+have been trained in a one-versus-rest design that
+distinguishes each class from
+the respective 17 other classes
+(number of maximal iterations=$100$, tolerance=$0.001$).
+In the outer CV layer, grid search
+selected among candidates for the respective $\lambda$ parameter
+by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
+Importantly, the thus selected sparse logistic regression classifier was
+evaluated on an identical test set in all settings.
+%
+Hierarchial tree sparsity demonstrated the best generalization
+in distinguihsing unseen neural activity maps from 18 tasks
+(89.67\%, mean recall XX.YY, mean precision XX.YY).
+It was closely followed by logistic regression with trace-norm
+regularization that is structured but not neurobiologically informed
+(89.43\%, mean recall XX.YY, mean precision XX.YY).
+Lasso featured an average performance comparing to the other sparse estimators
+(88.60\%, mean recall XX.YY, mean precision XX.YY)
+Introduced a priori knowledge of brain region compartments
+by sparse group sparsity performed worst
+(87.89\%, mean recall XX.YY, mean precision XX.YY).
+%
+In sum,
+biasing sparse model selection by domain knowledge of region-network hierarchies
+outperformed other types of frequently used sparse penalization techniques.
 
@@
 100\% (7584 maps).
+%
 The stratified and shuffled training data were submitted to
@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
+\end{centering}
+\vspace{-0.6cm}
+\caption{\textbf{Support recovery as a function of
+region and network emphasis.}
+The relative impact of the region and network priors
+on model selection
+is systematically varied against each other.
+This region-network ratio (\textit{upper row}) weighted voxel groups
+to priviledge sparse models in function space
+that acknowledge known brain region neighborhoods
+(\textit{left columns}) or
+known brain networks compartments
+(\textit{right columns}).
+Among the 18 classes, the model weights are shown for the
+tasks (\textit{from top to bottom}): tongue movement, listening stories,
+taking somebody else's perspective (ToM, "theory of mind"),
+as well as
+viewing locations and tools.
+The 18-class out-of-sample accuracy is indicated
+on the \textit{bottom} and
+the class-wise mean neural activty
+in the \textit{rightmost column}.
+%
+Different emphasis on regions versus networks
+in hierarchical structured sparsity can
+yield essentially similar model performance.
+%
+Priviledging region versus network structure during model selection
+recovers complementary aspects of the brain activity pattern.
+%
+Equal region and network emphasis yields more dispersed,
+less interpretable predictive model choices.
+}
+\label{fig_regnetratio}
+\end{figure}
+
 \paragraph{Support recovery as a function of region and network emphasis.}
+Finally, the relative importance of the
+region and network priors within the hierarchical tree prior
+was quantified (Figure \ref{fig_regnetratio}).
+The $\eta_g$ group of region priors was multiplied with a
+region-network ratio, while the
+$\eta_g$ group of network priors was biased by the corresponding
+network-region ratio. A region-network ratio of 3, for instance,
+increased the relative importance of known region structure
+by multiplying \frac{3}{1} to the
+$\eta_g$ factor of all region groups
+and multiplying
+\frac{1}{3} to all network groups.
+The data splitting cross-validation scheme was identical to the
+above modelling experiments.
+%
+As the most important observation,
+a range between region-dominant and network-dominant structured penalties
+yields quantitatively almost identical generalization to new data
+but qualitatively different decision functions manifested in the weight maps
+(Figure \ref{fig_regnetratio}, 2. and 4. column).
+Classification models with many zero coefficients but high absolute
+coefficients in either region compartments or network compartments
+can similarly extrapolation to unseen neural activity maps.
+Second,
+these perform similar to equilibrated region-network priors
+that set less voxel coefficients to zero and spread the
+probability mass with lower absolute coefficients across the whole brain
+(Figure \ref{fig_regnetratix}, 3. column in the middle).
+Third,
+overly strong emphasis on either level of the hierarchical prior
+can yield the neurobiologically informative maps
+of the most necessary region or network structure for
+statistically significant out-of-sample performance
+(Figure \ref{fig_regnetratix}, leftmost and rightmost columns).
+%
+In sum,
+stratifying the hierarchical tree penalty between region and network emphasis
+suggests that \textit{class-specific region-network weights}
+might offer more performant and more interpretable classification models
+in the future.
 

### 2016-01-26 paper/paper.tex
interm

@@
 increased the relative importance of known region structure
-by multiplying \frac{3}{1} to the
+by multiplying $\frac{3}{1}$ to the
 $\eta_g$ factor of all region groups
 and multiplying
-\frac{1}{3} to all network groups.
+$\frac{1}{3}$ to all network groups.
 The data splitting cross-validation scheme was identical to the
@@
 but qualitatively different decision functions manifested in the weight maps
-(Figure \ref{fig_regnetratio}, 2. and 4. column).
+(Figure \ref{fig_regnetratio}, second and forth column).
 Classification models with many zero coefficients but high absolute
@@
 probability mass with lower absolute coefficients across the whole brain
-(Figure \ref{fig_regnetratix}, 3. column in the middle).
+(Figure \ref{fig_regnetratio}, third column in the middle).
 Third,
@@
 statistically significant out-of-sample performance
-(Figure \ref{fig_regnetratix}, leftmost and rightmost columns).
+(Figure \ref{fig_regnetratio}, leftmost and rightmost columns).
 %

### 2016-01-26 paper/paper.tex
first complete discussion

@@
 \section{Discussion}
-Relevant structure in brain imaging data has long been
-separately investigated
-along two distinct organizational principles:
+Relevant structure in brain imaging data has long been investigated
+separately
+according to two distinct organizational principles:
 functional segregation into discrete brain regions
-and functional integration by inter-regional brain networks.
+and functional integration by interregional brain networks.
 %
@@
 both these neurobiological compartments
-for sparse variable selection and high-dimensional prediction.
+for sparse variable selection and high-dimensional prediction
+in a reference dataset.
 %
 Introducing existing domain knowledge into model selection
-naturally priviledges model hypotheses in the function space
+allowed privileging members of the function space
 that are most neurobiologically plausible.
 %
-The neurobiologically informed
-hierarchical structured sparsity penalty is shown to enhance
-model interpretability and generalization performance,
-although these statistical goals are typically in conflict.
-
-1) each voxel
-We assume regions and networks but can estimate 
-importance of each voxel.
-neurobiologically motivated restrictions to
-complexity circumvented the curse of dimensionality and allowed
-for useful, simplified views on brain function.
-previously laborious feature engineering / selection procedures
-
-2) restrictions to complexity according to neurobiological facts
--> bias-variance tradeoff: negigible increase in bias but large decrease in variance
--> VC: decrease complexitiy capactiy -> better chance for generalization out of sample
-
-guide model selection
-
-3)
-multiple comparisons problem has the curse of dimensionality
-as its close correspondence in statistical learning
-sparsity -> solves the curse at the estimation level
-
-4) region-constrained or network-constrained model estimation
-can lead to similar predictive performance
+Domain-informed hierarchical structured sparsity is shown to enhance
+both model interpretability and generalization performance,
+although these statistical-learning goals are typically in conflict.
+
+The present approach has important advantages over previous
+neuroimaging studies that capitalized on dimensionality reduction to harness
+the curse of dimensionality.
+They often used preliminary region-wise pooling functions
+or regression against network templates
+for subsequent supervised learning on the aggregated feature space.
+Such two-step approaches of feature engineering and inference
+\textit{i)} can only account for either functional specialization or
+functional integration of brain organization,
+\textit{ii)} depend on the ground truth being a region or network effect,
+and
+\textit{iii)} cannot issue individual coefficients for every brain voxels.
+%
+Hierarchical region-network sparsity overcomes these shortcomings
+by estimating individual voxel contributions
+while benefitting from their functional segregation and integration
+to restrict statistical complexity.
+%
+Viewed from the bias-variance tradeoff,
+our modification to logistic regression estimators
+entailed a large decrease in model variance but only a modest
+increase in model bias.
+Viewed from the Vapnik-Chervonenkis dimensions,
+this entailed a healthy decrease in the complexity capactity of the prediction model
+with a higher chance of generalizing to unobserved data.
 
 In the future,
-the proposed regularization scheme can be used for various
-learning tasks in systems neuroscience.
-This includes supervised classification and regression
+region-network sparsity priors could be incorporated into various
+pattern-learning methods in systems neuroscience.
+%
+This includes supervised methods for whole-brain classification and regression
 with one or several target variables.
-%
-Region-network sparsity priors could even be used to inform
-unsupervised statistical estimators,
-including principal component analysis
+The principled regularization scheme could even inform
+unsupervised structure discovery methods,
+such as principal component analysis
 \cite{jenatton2009structured}
 and
-k-means clustering \cite{???}.
+k-means clustering \cite{witten2010framework}.
 %
 Additionally,
-the structured sparsity penalty could be extended
+model regularization by hierarchical structured sparsity could be extended
 from the spatial domain of neural activity to
-spatiotemporally coherent neural activity patterns
+priors of coherent spatiotemporal activity structure
 \cite{gramfort2011tracking}.
@@
 an important prerequisite
-for prediction of diagnosis,
+for predicting diagnosis,
 disease trajectories, and treatment responses
-for personalized medicine in psychiatry and neurology
-\cite{gabrieli2015prediction}.
+in personalized psychiatry and neurology.
 

### 2016-01-27 paper/paper.tex
started writing a little two days ago

--- 2016-01-26 paper/paper.tex
@@
 \section{Methods}
+We make use of the hierarchical group lasso as introduced by Jennaton and 
+others in \cite{jenatton2011structured} to create a set of convex penalties
+with which we can probe the interplay between regional specificity and 
+inter-regional functional integration during different cognitive tasks.
 %
 \paragraph{Rationale}
+Th
 
-we need to inject domain knowledge into
-statistical estimations to harness the curse of dimensionality.
-two neurobiological design principles
-
-imposing parsimony
-integrative processes
-
- This L1/L2 norm for group lasso has been extended to a more general setting to
-
-designed groups
- the child nodes enter the set of relevant inputs only if its parent node does.
-
-should be able to estimate voxel level
-while taking into account known supravoxel structure.
-is instrumental in
-Developmentally, such large-scale networks emerge during late
-fetal growth (Doria et al., 2010), before cognitive capacities mature
-in childhood.
-
-In adults, nodes of a same cohesive network have more
-similar functional profiles than nodes from different networks
-(Anderson et al., 2013).
-
-data exhibit natural correlations between neighboring voxels forming clusters
-
-representing some phenomenon with as few variables as possible
-
-neurobiologically motivated restrictions to complexity circumvented
-the curse of dimensionality
-three-dimensional spatial arrangement that respects
-the functional anatomy of the brain
-not ignore the spatial configuration
-
-incorporate rich prior knowledge
-
-If meaningful structures exist,
-we show that one can take advantage of such structures
-
-Statistically,
-l1 and l2 are local sparsity priors
--> resulting sparsity does yield structure
-we want to priviledge representations with structure
-
-=> 
- a biologically and statistically desirable bias
+%% we need to inject domain knowledge into
+%% statistical estimations to harness the curse of dimensionality.
+%% two neurobiological design principles 
+%% 
+%% imposing parsimony
+%% integrative processes
+%% 
+%%  This L1/L2 norm for group lasso has been extended to a more general setting to
+%% 
+%% designed groups
+%%  the child nodes enter the set of relevant inputs only if its parent node does. 
+%%  
+%% should be able to estimate voxel level
+%% while taking into account known supravoxel structure.
+%% is instrumental in
+%% Developmentally, such large-scale networks emerge during late
+%% fetal growth (Doria et al., 2010), before cognitive capacities mature
+%% in childhood. 
+%% 
+%% In adults, nodes of a same cohesive network have more
+%% similar functional profiles than nodes from different networks
+%% (Anderson et al., 2013).
+%% 
+%% data exhibit natural correlations between neighboring voxels forming clusters
+%% 
+%% representing some phenomenon with as few variables as possible
+%% 
+%% neurobiologically motivated restrictions to complexity circumvented
+%% the curse of dimensionality
+%% three-dimensional spatial arrangement that respects
+%% the functional anatomy of the brain
+%% not ignore the spatial configuration
+%% 
+%% incorporate rich prior knowledge
+%% 
+%% If meaningful structures exist,
+%% we show that one can take advantage of such structures
+%% 
+%% Statistically,
+%% l1 and l2 are local sparsity priors
+%% -> resulting sparsity does yield structure
+%% we want to priviledge representations with structure
+%% 
+%% 
+%% => 
+%%  a biologically and statistically desirable bias
 
@@
 \section{Experimental Results}
+\paragraph{Serial versus parallel structure discovery and classification.}
+\paragraph{Serial versus parallel structure discovery and classification.}
+\paragraph{Serial versus parallel structure discovery and classification.}
 
@@
 \end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/sparsities.pdf}
-\end{centering}
-\vspace{-0.6cm}
-\caption{\textbf{Model performance across sparsity priors.}
-Compares the performance of 4 logistic regression estimators
-with different structured and unstructered sparsity terms
-in classifying neural activity from 18 psychological tasks.
-The class-wise precision and recall metrics
-were obtained on the test set.
-%
-Unstructured $\ell_1$-penalized logistic regression (\textit{upper left})
-imposed a minimum of relevant brain voxels without
-assuming special structure.
-Structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
-(\textit{lower left})
-imposed region compartments, but na\"ive to network structure.
-Structured trace-norm penalization (\textit{lower tight})
-imposed low-rank structure
-with sparsity of network patterns, but na\"ive to region structure.
-Structured $\ell_1/\ell_2$ block norm with a hierarchy of
-both region and network priors (\textit{upper tight})
-exhibited the best out-of-sample performance.
-%
-Consequently, a priori knowledge of both region and network neighborhoods
-was the most beneficial structured sparsity penalty.
-}
-\label{fig_sparsities}
-\end{figure}
-
-\paragraph{Benchmarking hierarchical tree sparsity against
-common sparsity penalties.}
-Hierarchical region-network priors have been systematically
-evaluated against other popular choices of sparse classification algorithms
-in an 18-class scenario
-(Figure \ref{fig_sparsities}).
-%
-Logistic regression with $\ell_1/\ell_2$ block norm penalization
-incorporated a hierarchy of previously known region and network neighborhoods
-for a neurobiological bias of the statistical estimation.
-%
-Vanilla logistic regression with $\ell_1$-penalization
-does not assume any previously known special structure.
-This classification estimator embraces a vision of neural activity structure
-that expectes a minimum of
-topographically and functionally independent brain voxel to be relevant.
-%
-Logistic regression with sparse group sparsity
-imposes a structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
-with a known atlas of region voxel groups onto the statistical estimation process.
-This supervised estimator shrinks and selects the coefficients
-of topographically compact voxel groups expected to be relevant together.
-%
-Logistic regression with trace-norm penalization
-imposed low-rank structure.
-This supervised classification algorithm
-expected a minimum of unknown network patterns
-to be relevant.
-%
-The stratified and shuffled training data were submitted to
-to a nested cross-validation scheme
-for model selection and model assessment.
-In the inner CV layer, the logistic regression estimators
-have been trained in a one-versus-rest design that
-distinguishes each class from
-the respective 17 other classes
-(number of maximal iterations=$100$, tolerance=$0.001$).
-In the outer CV layer, grid search
-selected among candidates for the respective $\lambda$ parameter
-by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
-Importantly, the thus selected sparse logistic regression classifier was
-evaluated on an identical test set in all settings.
-%
-Hierarchial tree sparsity demonstrated the best generalization
-in distinguihsing unseen neural activity maps from 18 tasks
-(89.67\%, mean recall XX.YY, mean precision XX.YY).
-It was closely followed by logistic regression with trace-norm
-regularization that is structured but not neurobiologically informed
-(89.43\%, mean recall XX.YY, mean precision XX.YY).
-Lasso featured an average performance comparing to the other sparse estimators
-(88.60\%, mean recall XX.YY, mean precision XX.YY)
-Introduced a priori knowledge of brain region compartments
-by sparse group sparsity performed worst
-(87.89\%, mean recall XX.YY, mean precision XX.YY).
-%
-In sum,
-biasing sparse model selection by domain knowledge of region-network hierarchies
-outperformed other types of frequently used sparse penalization techniques.
 
@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
+\end{centering}
+\vspace{-0.6cm}
+\caption{\textbf{Support recovery as a function of
+region and network emphasis.}
+The relative impact of the region and network priors
+on model selection
+is systematically varied against each other {\color{red} HOW??}.
+This region-network ratio (\textit{upper row}) weighted voxel groups
+to privilege sparse models in function space
+that acknowledge known brain region neighborhoods
+(\textit{left columns}) or
+known brain networks compartments
+(\textit{right columns}).
+Among the 18 classes, the model weights are shown for the
+tasks (\textit{from top to bottom}): tongue movement, listening stories,
+taking somebody else's perspective (ToM, "theory of mind"),
+as well as
+viewing locations and tools.
+The 18-class out-of-sample accuracy is indicated
+on the \textit{bottom} and
+the class-wise mean neural activity
+in the \textit{rightmost column}.
+%
+Different emphasis on regions versus networks
+in hierarchical structured sparsity can
+yield essentially similar model performance.
+%
+Privileging region versus network structure during model selection
+recovers complementary aspects of the brain activity pattern.
+%
+Equal region and network emphasis yields more dispersed,
+less interpretable predictive model choices.
+}
+\label{fig_ratio}
+\end{figure}
+
 \paragraph{Sample complexity of na\"ive versus informed sparse model selection.}
@@
 100\% (7584 maps).
-%
 The stratified and shuffled training data were submitted to
@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
-\end{centering}
-\vspace{-0.6cm}
-\caption{\textbf{Support recovery as a function of
-region and network emphasis.}
-The relative impact of the region and network priors
-on model selection
-is systematically varied against each other.
-This region-network ratio (\textit{upper row}) weighted voxel groups
-to priviledge sparse models in function space
-that acknowledge known brain region neighborhoods
-(\textit{left columns}) or
-known brain networks compartments
-(\textit{right columns}).
-Among the 18 classes, the model weights are shown for the
-tasks (\textit{from top to bottom}): tongue movement, listening stories,
-taking somebody else's perspective (ToM, "theory of mind"),
-as well as
-viewing locations and tools.
-The 18-class out-of-sample accuracy is indicated
-on the \textit{bottom} and
-the class-wise mean neural activty
-in the \textit{rightmost column}.
-%
-Different emphasis on regions versus networks
-in hierarchical structured sparsity can
-yield essentially similar model performance.
-%
-Priviledging region versus network structure during model selection
-recovers complementary aspects of the brain activity pattern.
-%
-Equal region and network emphasis yields more dispersed,
-less interpretable predictive model choices.
-}
-\label{fig_regnetratio}
-\end{figure}
-
 \paragraph{Support recovery as a function of region and network emphasis.}
-Finally, the relative importance of the
-region and network priors within the hierarchical tree prior
-was quantified (Figure \ref{fig_regnetratio}).
-The $\eta_g$ group of region priors was multiplied with a
-region-network ratio, while the
-$\eta_g$ group of network priors was biased by the corresponding
-network-region ratio. A region-network ratio of 3, for instance,
-increased the relative importance of known region structure
-by multiplying \frac{3}{1} to the
-$\eta_g$ factor of all region groups
-and multiplying
-\frac{1}{3} to all network groups.
-The data splitting cross-validation scheme was identical to the
-above modelling experiments.
-%
-As the most important observation,
-a range between region-dominant and network-dominant structured penalties
-yields quantitatively almost identical generalization to new data
-but qualitatively different decision functions manifested in the weight maps
-(Figure \ref{fig_regnetratio}, 2. and 4. column).
-Classification models with many zero coefficients but high absolute
-coefficients in either region compartments or network compartments
-can similarly extrapolation to unseen neural activity maps.
-Second,
-these perform similar to equilibrated region-network priors
-that set less voxel coefficients to zero and spread the
-probability mass with lower absolute coefficients across the whole brain
-(Figure \ref{fig_regnetratix}, 3. column in the middle).
-Third,
-overly strong emphasis on either level of the hierarchical prior
-can yield the neurobiologically informative maps
-of the most necessary region or network structure for
-statistically significant out-of-sample performance
-(Figure \ref{fig_regnetratix}, leftmost and rightmost columns).
-%
-In sum,
-stratifying the hierarchical tree penalty between region and network emphasis
-suggests that \textit{class-specific region-network weights}
-might offer more performant and more interpretable classification models
-in the future.
 

### 2016-01-27 paper/paper.tex

--- 2016-01-26 paper/paper.tex
@@
 \section{Methods}
+We make use of the hierarchical group lasso as introduced by Jennaton and 
+others in \cite{jenatton2011structured} to create a set of convex penalties
+with which we can probe the interplay between regional specificity and 
+inter-regional functional integration during different cognitive tasks.
 %
 \paragraph{Rationale}
-
-we need to inject domain knowledge into
-statistical estimations to harness the curse of dimensionality.
-two neurobiological design principles
-
-imposing parsimony
-integrative processes
-
- This L1/L2 norm for group lasso has been extended to a more general setting to
-
-designed groups
- the child nodes enter the set of relevant inputs only if its parent node does.
-
-should be able to estimate voxel level
-while taking into account known supravoxel structure.
-is instrumental in
-Developmentally, such large-scale networks emerge during late
-fetal growth (Doria et al., 2010), before cognitive capacities mature
-in childhood.
-
-In adults, nodes of a same cohesive network have more
-similar functional profiles than nodes from different networks
-(Anderson et al., 2013).
-
-data exhibit natural correlations between neighboring voxels forming clusters
-
-representing some phenomenon with as few variables as possible
-
-neurobiologically motivated restrictions to complexity circumvented
-the curse of dimensionality
-three-dimensional spatial arrangement that respects
-the functional anatomy of the brain
-not ignore the spatial configuration
-
-incorporate rich prior knowledge
-
-If meaningful structures exist,
-we show that one can take advantage of such structures
-
-Statistically,
-l1 and l2 are local sparsity priors
--> resulting sparsity does yield structure
-we want to priviledge representations with structure
-
-=> 
- a biologically and statistically desirable bias
+Th
+
+%% we need to inject domain knowledge into
+%% statistical estimations to harness the curse of dimensionality.
+%% two neurobiological design principles 
+%% 
+%% imposing parsimony
+%% integrative processes
+%% 
+%%  This L1/L2 norm for group lasso has been extended to a more general setting to
+%% 
+%% designed groups
+%%  the child nodes enter the set of relevant inputs only if its parent node does. 
+%%  
+%% should be able to estimate voxel level
+%% while taking into account known supravoxel structure.
+%% is instrumental in
+%% Developmentally, such large-scale networks emerge during late
+%% fetal growth (Doria et al., 2010), before cognitive capacities mature
+%% in childhood. 
+%% 
+%% In adults, nodes of a same cohesive network have more
+%% similar functional profiles than nodes from different networks
+%% (Anderson et al., 2013).
+%% 
+%% data exhibit natural correlations between neighboring voxels forming clusters
+%% 
+%% representing some phenomenon with as few variables as possible
+%% 
+%% neurobiologically motivated restrictions to complexity circumvented
+%% the curse of dimensionality
+%% three-dimensional spatial arrangement that respects
+%% the functional anatomy of the brain
+%% not ignore the spatial configuration
+%% 
+%% incorporate rich prior knowledge
+%% 
+%% If meaningful structures exist,
+%% we show that one can take advantage of such structures
+%% 
+%% Statistically,
+%% l1 and l2 are local sparsity priors
+%% -> resulting sparsity does yield structure
+%% we want to priviledge representations with structure
+%% 
+%% 
+%% => 
+%%  a biologically and statistically desirable bias
 

### 2016-01-27 paper/paper.tex
final touches in intro+disc

--- 2016-01-26 paper/paper.tex
@@
 total observations per data sample.
-This high-dimensional scenario challenges many statistical estimators from
+This high-dimensional scenario challenges various statistical methods from
 classical statistics.
 For instance,
-the estimation of any generalized linear model without additional assumptions
-becomes underdetermined, i.e. yields full subspace of possible solutions, many or most of which will not generalize well in a predictive setting.
+estimating generalized linear models without additional assumptions
+yields an underdetermined system of equations.
 %
@@
 \textit{sparsity} assumptions
-\cite{buhlmann2011statistics, hastie2015statistical}, which act as a 
+\cite{buhlmann2011statistics, hastie2015statistical}.
+They act as a 
 regularizer and can be used for model selection.
@@
 statistical estimation,
-thus preassuming the variables to have unequal importance
-and to obey expected data distributions
+thus shrinking and selecting variables guided by
+expected data distributions
 \cite{bach2012optimization}.
-{\color{red}Michael: This is the definition of a prior, not of strutured sparsity}
-
-%% Yet, what neurobiological structure suggests itself
-%% to harness the
-%% \textit{curse of dimensionality} with
-%% $\textgreater$100,000 variables
-%% in neuroimaging research?
-In neuroimaging research, generalized linear models predicting external 
-variables from brain images, which can reach a dimensionality of several
-hundreds of thousands of voxels, necessarily need appropriate regularization.
-Which neurobiological prior knowledge lends itself to the construction of a
-structured sparse prior?
+Such restrictions to complexity are an attractive plan of attacked
+for the $\textgreater$100,000 variables of brain maps.
+Yet, what generally accepted neurobiological structure lends itself
+to harness the
+\textit{curse of dimensionality} by structured sparsity priors?
 
@@
 invasive examination of anatomy (i.e., histological preparation),
-connectivity, (i.e., axonal tracing),
+connectivity (i.e., axonal tracing),
 and functional properties
-(i.e., single cell recordings) in animals.
+(i.e., single-cell recordings) in animals.
 Regarding functional segregation into specialized regions,
@@
 probably no existing brain analysis method acknowledges that
-both architectural principles are inextricably involved
+both functional organizations are inextricably involved
 in the realization of mental operations
@@
 %
-Single cell recordings and microscopic examination
+Single-cell recordings and microscopic examination
 revealed, for instance, the
@@
 Tissue lesion of the mid-fusiform gyrus of the visual system,
-for instance,
+in turn,
 was frequently reported to impair
@@
 \cite{behrens03, cbp2015review}.
-Today,
-high-thoughput approaches enable
+High-thoughput approaches today enable
 ultrahigh-resolution 3D models of brain anatomy
@@
 These revealed the important implication of
-canonical brain networks across cognitive domains,
+canonical brain networks across psychological tasks,
 including the so-called
@@
 were repeatedly observed to be induced
-by the onset of given cognitive tasks \cite{fransson2006}.
-Such task-induced mechanisms orchestrating supraordinate networks
-might be subserved by the right anterior insula \cite{sridh2008}
-and temporo-parietal junction \cite{bzdok2013tpj}.
-%
-Ultimately,
-interpretation of findings from all these methods naturally embraces
+by the onset of given psychological tasks \cite{fransson2006}.
+% Such task-induced mechanisms orchestrating supraordinate networks
+% might be subserved by the right anterior insula \cite{sridh2008}
+% and temporo-parietal junction \cite{bzdok2013tpj}.
+%
+As a common point of all these methods,
+interpretation of findings naturally embraces
 cross-regional integration by
@@
 to
+astrophysics \cite{vinci2014estimating},
 genetics \cite{rapaport2008classification, kim2012tree},
-astrophysics \cite{vinci2014estimating},
 and
@@
 This is extended by the present work that
-enables neuroscience-specific estimators capitalizing on
+introduced neuroscience-specific estimators capitalizing on
 neurobiologically plausible region and network priors.
 %
-Using a large reference dataset,
+Based on the largest neuroimaging repository,
 we demonstrated that domain-informed supervised models
@@
 \section{Discussion}
-Relevant structure in brain imaging data has long been investigated
-separately
-according to two distinct organizational principles:
+Relevant structure in neuroimaging data has long been investigated
+according to two separate organizational principles:
 functional segregation into discrete brain regions
@@
 for subsequent supervised learning on the aggregated feature space.
-Such two-step approaches of feature engineering and inference
+Such lossy two-step approaches of feature engineering and inference
 \textit{i)} can only account for either functional specialization or
@@
 Viewed from the Vapnik-Chervonenkis dimensions,
-this entailed a healthy decrease in the complexity capactity of the prediction model
+this entailed a healthy decrease in the complexity capacity of the prediction model
 with a higher chance of generalizing to unobserved data.

### 2016-01-27 paper/paper.tex
cosm

--- 2016-01-27 paper/paper.tex
@@
 Functional specialization emphasizes that microscopically distinguishable
-brain regions solve distinct classes of computational processes
+brain regions are responsible distinct classes of computational processes
 \cite{kanwisher2010functional}.
@@
 revealed, for instance, the
-specialization in the visual cortex into V1, V2, V3, V3A, and V4
+specialization in the occipital visual cortex into V1, V2, V3, V3A/B, and V4
 \cite{hubel1962receptive, zeki1978functional}.

### 2016-01-27 paper/paper.tex
typo
rationale

@@
 Further,
-radioactive mapping of neurotransmitter receptors
+radioactive mapping {\color{red} Michael: is this the correct term?} of neurotransmitter receptors
 rendered accessible yet another
@@
 Today,
-high-thoughput approaches enable
+high-throughput approaches enable
 ultrahigh-resolution 3D models of brain anatomy
@@
 \section{Methods}
+Our main contribution is the domain-specific adaptation of sparse structured
+penalties making it possible to jointly incorporate functional 
+specialization and functional integration priors into statistical 
+estimators.
 We make use of the hierarchical group lasso as introduced by Jennaton and 
 others in \cite{jenatton2011structured} to create a set of convex penalties
-with which we can probe the interplay between regional specificity and 
+with which we can probe this interplay between regional specificity and 
 inter-regional functional integration during different cognitive tasks.
@@
 \paragraph{Rationale}
-Th
+Three-dimensional voxel brain images as obtained by various neuroimaging
+techniques are very high-dimensional, but also very highly structured.
+While its explicit dimensionality, the number of voxels, which varies with
+the resolution of the image is generally of the order of 100000, the number
+of samples available for analyses never exceeds hundreds or thousands.
+This \(n << p\) situation immediately implies an underdeterminedness for any
+linear model basing its decisions on dot products with the voxel values.
+
+Luckily, there is and abundance structure to be exploited, which can be
+injected into the estimation as a domain knowledge prior. Here we are 
+interested in incorporating knowledge about both the well-established 
+modules of functional specialization and the interactions of these modules
+amongst each other across the brain.
+%
+Developmentally, such large-scale networks emerge during late
+fetal growth (Doria et al., 2010), before cognitive capacities mature
+in childhood. 
+%
+In adults, nodes of a same cohesive network have more
+similar functional profiles than nodes from different networks
+(Anderson et al., 2013).
+%
+On the signal level, functional modules are localized structures implicating
+neighboring voxels in an image. A variety of known functional modules has
+been compiled into atlases of the brain. Different types of atlases rely on
+different ways of segregating modules from another. For instance, anatomical
+atlases rely on the variation of tissue properties across the brain, which
+can be at the cellular level or based on higher-order structure.
+%
+Global functional networks can be discovered by statistical analysis of
+functional brain imaging data, for example the BOLD contrast in fMRI. A
+well-established method of estimating these networks is independent 
+component analysis \cite{Hamalainen}. It robustly identifies the default
+mode, saliency and attention networks.
+%
+Since these network maps are for the most part disjoint spatially
 
@@
 This classification estimator embraces a vision of neural activity structure
-that expectes a minimum of
+that expects a minimum of
 topographically and functionally independent brain voxel to be relevant.
@@
 Hierarchial tree sparsity demonstrated the best generalization
-in distinguihsing unseen neural activity maps from 18 tasks
+in distinguishing unseen neural activity maps from 18 tasks
 (89.67\%, mean recall XX.YY, mean precision XX.YY).

### 2016-01-27 paper/paper.tex
rationale

@@
 %
-Since these network maps are for the most part disjoint spatially
+Global functional networks as estimated by ICA are contiuous brain maps
+attributing weights to each voxel. Since the regions involved in these
+networks are nevertheless largely disjoint spatially and roughly in
+correspondence with module boundaries {\color{red} Michael: verify this!!!}, 
+it is possible to uniquely associate each module from a region atlas to one
+of the extracted global functional networks.
+
+This correspondence makes it possible to encode our knowledge about the 
+networks and regions into a hierarchy: A brain contains a certain number of
+networks, which in turn consist of the atlas modules as subregions.
+We can use this hierarchy to create a structural prior of expected weight
+maps for classifiers.
+
+The hierarchical group lasso as introduced by \cite{jenatton2011} lends
+itself perfectly to represent this structure. It is based on the group lasso
+\cite{group_lasso} but permits groups to contain each other in a tree
+structure. The first level of the tree are the network groups containing all
+the voxels of the modules associated to them. Then each network contains as
+as subgroups the modules associated with it, grouping the voxels of each of
+these regions together.
+As with the group lasso, it is possible to associate an individual penalty
+to each group. In trading off the penalties on the network level against the
+penalties of the region level, we can create different regimes of 
+estimation: 
+%
+Setting a low penalty on the network groups makes it probable
+that all of them are active in the estimated weight map. If we then select
+higher penalties on region groups, selection of relevant region groups is
+forced without the bias of the network maps.
+%
+Conversely, setting low penalties on the region maps makes it possible for
+all voxels to be active. Selecting higher penalties on the networks then
+leads to a selection of networks with all regions associated to it.
+%
+Taken together and varied smoothly, we can evaluate a tradeoff between the
+relevance of modular regions and functionally integrated networks in 
+statistical estimation of brain activity.
 

### 2016-01-27 paper/paper.tex
some math

@@
 \paragraph{Problem formulation}
-
-Sparse linear models
-encode geometric prior information
-topology
-local sets of voxels
-
-Group-sparsity is a first step towards the more general idea that
-a regularization function can encourage sparse solutions with a particular structure.
-
-it is not realistic to assume that all of the tasks share the same set of rele- vant inputs as in the L1/L2-regularized regression.
+We formulate our estimation problem in the framework of regularized risk
+estimation applied to linear models: 
+We would like to estimate a good predictor of cognitive task
+given a brain image. Let the set \(\mathcal X\subset\R^p\) represent brain
+images of \(p > 0\) voxels.
+
+Then we would like to minimize the risk \(\mathcal L(\hat y, y)\), where
+\(\hat y = X\hat w + \hat b\), while regularizing to incorporate a useful
+prior. Taken together, this can be framed as an optimization problem
+\[\argmin_{w, b} \mathcal L(Xw + b, y) + \lambda\Omega(w),\]
+where \(\lambda > 0\) and \(\Omega\) is the regularizer.
+
+Brain regions are defined as disjoint groups of voxels. Let \(\mathcal G\)
+be a partition of \(\{1, \dots, p\}\), i.e.
+\[  \bigcup_{i} g_i = \{1, \dots, p\} \textrm{ and } g_i\cap g_j=\emptyset
+\quad\forall i\not=j\]
+
+Brain networks consist of regions and are thus super-regions or groups of 
+regions. The set of brain networks \(\mathcal{H}\) is also a partition of 
+\(\{1, \dots, p\}\) and in addition it is consistent with \(\mathcal G\) in
+the sense that
+\[\textrm{for all }g\in\mathcal G, h\in\mathcal H,\quad
+\textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
+This allows a clear association of each region \(g\in\mathcal G\) to a 
+network \(h\in\mathcal H\) and thus establishes a tree structure (up to 
+adding a root node containing all voxels).
+
+For a brain image \(w\in\R^p\) and a group \(g\), the vector 
+\(w_g\in\R^{|g|}\) is defined as the restriction of \(w\) to the coordinates
+ in \(g\). The structured penalty incorporating network
+and region information can then be written as
+\[\Omega(w) = \alpha\sum_{h\in\mathcal H}\eta_h\|w_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|w_g\|_2.\]
+According to \cite{Zhou_or_who_was_that} we set \(\eta_g = 1/\sqrt{|g|}\) to
+account for varying group size. The hierarchy-level-specific factors 
+\(\alpha > 0\) and \(\beta > 0\) are used to trade-off region-weighted and
+network-weighted models against each other.
+
+The prediction problem at hand is a multiclass classification. We choose to
+attack this using one-vs-rest scheme on a binary logistic regression, whose
+loss can be written as
+\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
+if \(y\in{-1, 1}\) and with \(x_i\in\R^p\) the training sample brain images.
+
+{\color{red}
+MISSING
+\begin{itemize}
+\item cross-validation scheme
+\item analysis of penalty tradeoff (CV scheme for that?)
+\item mentioning of control methods in methods. Trace norm, sparse group sparsity. Anything else? ENET?
+\end{itemize}
+}
+
+%% Sparse linear models
+%% encode geometric prior information
+%% topology
+%% local sets of voxels
+%% 
+%% Group-sparsity is a first step towards the more general idea that
+%% a regularization function can encourage sparse solutions with a particular structure. 
+%% 
+%% it is not realistic to assume that all of the tasks share the same set of rele- vant inputs as in the L1/L2-regularized regression.
 A subset of highly related outputs may share a common set of relevant inputs, whereas weakly related outputs are less likely to be affected by the same inputs.
-
-structured regularization
-We might therefore gain in the quality of the factors
-induced by enforcing directly this a priori
-
-groups at multiple granularity
-
-tree-guided group lasso
-
-encourage structured shrinkage effect
-
-l1 = unstructured sparsity-inducing penalty
-
-Our method extends the L1/L2 penalty to the tree-lasso penalty
-by letting the hierarchically-defined groups overlap. 
-the tree lasso is a special case of overlapping group lasso
-
-for every column u of U, it compute a column v of V solving
-
-we aim at learning a weight vector w ∈ Rp and an intercept b ∈ R
-such that the prediction of y can be based on the value of w⊤x + b.
-
-We omit a bias term, since the data were mean-centered
-and unit-variance scaled.
-The scalar b is not particularly informative
-
-however the vector w corresponds to a volume that
-can be represented in brain space as a volume
-
-hierarchial tree = more generally into a directed acyclic graph
-
-more precisely, we denote by X ∈ Rn×p the design matrix
-assembled from n fMRI volumes and by y ∈ Rn the corresponding n targets.
-In other words, each row of X is a p-dimensional sample,
-i.e., an activation map of p voxels related to one stimulus presentation.
-for visualization of the predictive pattern of voxels.
-
-Learning the parameters (w, b) remains challenging
-since the number of features (104 to 105 voxels) exceeds
-by far the number of samples (a few hundreds of volumes).
-
-The scalar b is not particularly informative,
-however the vector w corresponds to a volume that
-can be represented in brain space as a volume
-for visualization of the predictive pattern of voxels.
-
-each row of X is a p-dimensional sample,
-i.e., an activation map of p voxels related to one stimulus presentation.
-
-To address this issue, dimensionality reduction attempts to
-find a low dimensional subspace that concentrates
-as much of the predictive power of
-the original set as possible for the problem at hand.
--> we do not want to do preliminary feature selection or
-dimensionality reduction
-or feature agglomeration because we want to fit one model parameter
-to each brain voxel for maximal interpretability
-This corresponds to discarding some columns of X.
-
-The essential shortcoming of the Elastic net is that
-it does not take into account the spatial structure of the data,
-which is crucial in this context
-
-Craddock clusters are often used for feature agglomeration
-into parcels
--> exploits only a part of the data
-
-dual-level spatial structure
-sparse hierarchical regularization
-structured sparsity-inducing regularization
-the root of the tree T is the unique cluster that gathers all the voxels,
-
-It is a generalization of the traditional $\ell_1$-norm
-$\Omega(\mathbf{w}) = \sum_{j=1}^p|\mathbf{w}_j|$
-ignores structure
-
-\cite{jenatton2011multi}
-
-\textit{structured sparsity}
-
-\cite{huang2011learning, morales2010family, jenatton2011structured}
-
-a node $j$ of $\mathcal{T}$,
-we denote by $g_j \subseteq \{1,..,q\}$ the set of indices that record
-all the descendants of $j$ in $\mathcal{T}$
-
-the family of sparsity-inducing norms has recently been extended
-by hierarchical sparsity penalty terms
-\cite{zhao2009composite}.
-
-\begin{equation}
-  \Omega(\mathbf{w}) = \sum_{g \in G}||\mathbf{w}_g||_2 = \sum_{g \in G}\sqrt{\sum_{j \in g}\mathbf{w}_j^2}
-\end{equation}
-
-For example, when G is the set of all singletons, Ω is the
-usual l1 norm (assuming that all the weights are equal to 1).
-
-l1/l2 mixed norm is convex
-
-Discarding coefficients belonging to a network group will naturally enforce
-discarding the coefficients belonging to each of its descendent region groups.
-Conversely,
-variable selection of a network group will also enforce
-selection of all voxel of its descendent group regions.
-Single region groups can however be set to zero (unselected)
-or non-zero (selected)
-without analogous effect on the parent network group.
-
-At the between-group level,...
-$\Omega$ exerts $\ell_1$-like variable selection on
-the $(||\mathbf{w}_g||_2)_{g\in G}$ groups,
-yielding a maximum of $g \in G$ to be zeroed out
-\cite{jenatton2011structured}.
-The important consequence is that also all descentes of such a zeroed
-group $g \in G$ will be descarded.
-Conversely,
-if one group $g$ is selected,
-then all the ancestral groups will also be selected.
-Thus, statistical estimation will be improved by enticing
-entire voxel sets to be selected or discarded as predictive, 
-although one individual coefficient is computed for each voxel.
-
--> it is a $(\ell_1, \ell_2)$-mixed norm
--> between-group sparsity effect by l1
--> within-group shrinkage effect by l2
-
-\begin{equation}
-  \Omega(\mathbf{w}) = \sum_{g \in G} \eta_g ||\mathbf{w}_g||_2
-\end{equation}
-
-$(\eta_g)_{g \in G}$ are positive weights for the groups
-
-fit to the data is measured through
-a convex loss function (w, b) 􏰀→ L(y, X, w, b) ∈ R+.
-
-\paragraph{Classification}
-
-logistic loss function
-
-\begin{equation}
-  P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
-  \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
-\end{equation}
-
-$\lambda > 0$
-
-bias is omitted because $\mathbf{X} and \mathbf{y}$
-are mean-centered and unit-variance scaled.
-
-In this setting, and given a new fMRI volume x,
-we make predictions by choosing the label that maximizes
-the class-conditional probabil- ities (3.1), that is, argmaxk∈{1,...,c}Prob(y = k|x; W∗, b∗)
-
-One-versus-rest scheme
-
-\paragraph{Regression}
-
-squared error as loss
-
-\begin{equation}
-  \argmin \frac{1}{2}||\mathbf{y - Xw}||_2^2 + \lambda\Omega(\mathbf{w})
-\end{equation}
-
-$\lambda > 0$
-
-Prediction for a new fMRI volume x is then simply performed by computing
-the dot product x⊤w∗
-
-\paragraph{Numerical optimization}
-
-Difficult because high-dimensional setting
-
-empirical risk minimization was performed by
-
-The intercept $b$ is left unregularized
+%% 
+%% structured regularization
+%% We might therefore gain in the quality of the factors
+%% induced by enforcing directly this a priori 
+%% 
+%% groups at multiple granularity
+%% 
+%% tree-guided group lasso
+%% 
+%% encourage structured shrinkage effect 
+%% 
+%% l1 = unstructured sparsity-inducing penalty
+%% 
+%% Our method extends the L1/L2 penalty to the tree-lasso penalty
+%% by letting the hierarchically-defined groups overlap. 
+%% the tree lasso is a special case of overlapping group lasso
+%% 
+%% for every column u of U, it compute a column v of V solving
+%% 
+%% we aim at learning a weight vector w ∈ Rp and an intercept b ∈ R
+%% such that the prediction of y can be based on the value of w⊤x + b.
+%% 
+%% We omit a bias term, since the data were mean-centered
+%% and unit-variance scaled.
+%% The scalar b is not particularly informative
+%% 
+%% however the vector w corresponds to a volume that
+%% can be represented in brain space as a volume
+%% 
+%% hierarchial tree = more generally into a directed acyclic graph
+%% 
+%% more precisely, we denote by X ∈ Rn×p the design matrix
+%% assembled from n fMRI volumes and by y ∈ Rn the corresponding n targets.
+%% In other words, each row of X is a p-dimensional sample,
+%% i.e., an activation map of p voxels related to one stimulus presentation.
+%% for visualization of the predictive pattern of voxels. 
+%% 
+%% Learning the parameters (w, b) remains challenging
+%% since the number of features (104 to 105 voxels) exceeds
+%% by far the number of samples (a few hundreds of volumes). 
+%% 
+%% The scalar b is not particularly informative,
+%% however the vector w corresponds to a volume that
+%% can be represented in brain space as a volume
+%% for visualization of the predictive pattern of voxels.
+%% 
+%% each row of X is a p-dimensional sample,
+%% i.e., an activation map of p voxels related to one stimulus presentation.
+%% 
+%% To address this issue, dimensionality reduction attempts to
+%% find a low dimensional subspace that concentrates
+%% as much of the predictive power of
+%% the original set as possible for the problem at hand.
+%% -> we do not want to do preliminary feature selection or
+%% dimensionality reduction
+%% or feature agglomeration because we want to fit one model parameter
+%% to each brain voxel for maximal interpretability
+%% This corresponds to discarding some columns of X.
+%% 
+%% The essential shortcoming of the Elastic net is that
+%% it does not take into account the spatial structure of the data,
+%% which is crucial in this context
+%% 
+%% Craddock clusters are often used for feature agglomeration
+%% into parcels
+%% -> exploits only a part of the data
+%% 
+%% dual-level spatial structure
+%% sparse hierarchical regularization
+%% structured sparsity-inducing regularization
+%% the root of the tree T is the unique cluster that gathers all the voxels,
+%% 
+%% It is a generalization of the traditional $\ell_1$-norm
+%% $\Omega(\mathbf{w}) = \sum_{j=1}^p|\mathbf{w}_j|$
+%% ignores structure
+%% 
+%% 
+%% \cite{jenatton2011multi}
+%% 
+%% \textit{structured sparsity}
+%% 
+%% \cite{huang2011learning, morales2010family, jenatton2011structured}
+%% 
+%% 
+%% a node $j$ of $\mathcal{T}$,
+%% we denote by $g_j \subseteq \{1,..,q\}$ the set of indices that record
+%% all the descendants of $j$ in $\mathcal{T}$
+%% 
+%% the family of sparsity-inducing norms has recently been extended
+%% by hierarchical sparsity penalty terms
+%% \cite{zhao2009composite}.
+%% 
+%% 
+%% \begin{equation}
+%%   \Omega(\mathbf{w}) = \sum_{g \in G}||\mathbf{w}_g||_2 = \sum_{g \in G}\sqrt{\sum_{j \in g}\mathbf{w}_j^2}
+%% \end{equation}
+%% 
+%% For example, when G is the set of all singletons, Ω is the
+%% usual l1 norm (assuming that all the weights are equal to 1).
+%% 
+%% l1/l2 mixed norm is convex
+%% 
+%% 
+%% Discarding coefficients belonging to a network group will naturally enforce
+%% discarding the coefficients belonging to each of its descendent region groups.
+%% Conversely,
+%% variable selection of a network group will also enforce
+%% selection of all voxel of its descendent group regions.
+%% Single region groups can however be set to zero (unselected)
+%% or non-zero (selected)
+%% without analogous effect on the parent network group.
+%% 
+%% 
+%% 
+%% 
+%% At the between-group level,...
+%% $\Omega$ exerts $\ell_1$-like variable selection on
+%% the $(||\mathbf{w}_g||_2)_{g\in G}$ groups,
+%% yielding a maximum of $g \in G$ to be zeroed out
+%% \cite{jenatton2011structured}.
+%% The important consequence is that also all descentes of such a zeroed
+%% group $g \in G$ will be descarded.
+%% Conversely,
+%% if one group $g$ is selected,
+%% then all the ancestral groups will also be selected.
+%% Thus, statistical estimation will be improved by enticing
+%% entire voxel sets to be selected or discarded as predictive, 
+%% although one individual coefficient is computed for each voxel.
+%% 
+%% -> it is a $(\ell_1, \ell_2)$-mixed norm
+%% -> between-group sparsity effect by l1
+%% -> within-group shrinkage effect by l2
+%% 
+%% 
+%% \begin{equation}
+%%   \Omega(\mathbf{w}) = \sum_{g \in G} \eta_g ||\mathbf{w}_g||_2
+%% \end{equation}
+%% 
+%% $(\eta_g)_{g \in G}$ are positive weights for the groups
+%% 
+%% 
+%% fit to the data is measured through
+%% a convex loss function (w, b) 􏰀→ L(y, X, w, b) ∈ R+. 
+%% 
+%% 
+%% \paragraph{Classification}
+%% 
+%% logistic loss function
+%% 
+%% \begin{equation}
+%%   P(y=k|x, W, b) = \frac{exp\{x^Tw^k + b_k\}}{\sum_{m=1}^cexp\{x^Tw^m + b_m\}}
+%%   \argmin \frac{1}{2}||u-v||_2^2 + \lambda\Omega(\mathbf{w})
+%% \end{equation}
+%% 
+%% $\lambda > 0$
+%% 
+%% bias is omitted because $\mathbf{X} and \mathbf{y}$
+%% are mean-centered and unit-variance scaled.
+%% 
+%% In this setting, and given a new fMRI volume x,
+%% we make predictions by choosing the label that maximizes
+%% the class-conditional probabil- ities (3.1), that is, argmaxk∈{1,...,c}Prob(y = k|x; W∗, b∗)
+%% 
+%% One-versus-rest scheme
+%% 
+%% 
+%% \paragraph{Regression}
+%% 
+%% squared error as loss
+%% 
+%% \begin{equation}
+%%   \argmin \frac{1}{2}||\mathbf{y - Xw}||_2^2 + \lambda\Omega(\mathbf{w})
+%% \end{equation}
+%% 
+%% $\lambda > 0$
+%% 
+%% Prediction for a new fMRI volume x is then simply performed by computing
+%% the dot product x⊤w∗
+%% 
+%% \paragraph{Numerical optimization}
+%% 
+%% Difficult because high-dimensional setting
+%% 
+%% empirical risk minimization was performed by
+%% 
+%% 
+%% The intercept $b$ is left unregularized
 

### 2016-01-28 paper/paper.tex
pass over figures

--- 2016-01-27 paper/paper.tex
@@
 Functional specialization emphasizes that microscopically distinguishable
-brain regions are responsible distinct classes of computational processes
+brain regions solve distinct classes of computational processes
 \cite{kanwisher2010functional}.
@@
 %
-Single cell recordings and microscopic examination
+Single-cell recordings and microscopic examination
 revealed, for instance, the
-specialization in the occipital visual cortex into V1, V2, V3, V3A/B, and V4
+specialization in the visual cortex into V1, V2, V3, V3A, and V4
 \cite{hubel1962receptive, zeki1978functional}.
 Tissue lesion of the mid-fusiform gyrus of the visual system,
-for instance,
+in turn,
 was frequently reported to impair
@@
 Further,
-radioactive mapping {\color{red} Michael: is this the correct term?} of neurotransmitter receptors
+radioactive mapping of neurotransmitter receptors
 rendered accessible yet another
@@
 \cite{behrens03, cbp2015review}.
-Today,
-high-throughput approaches enable
+High-thoughput approaches today enable
 ultrahigh-resolution 3D models of brain anatomy
@@
 \section{Methods}
-Our main contribution is the domain-specific adaptation of sparse structured
-penalties making it possible to jointly incorporate functional 
-specialization and functional integration priors into statistical 
-estimators.
-We make use of the hierarchical group lasso as introduced by Jennaton and 
-others in \cite{jenatton2011structured} to create a set of convex penalties
-with which we can probe this interplay between regional specificity and 
-inter-regional functional integration during different cognitive tasks.
 %
 \paragraph{Rationale}
-Three-dimensional voxel brain images as obtained by various neuroimaging
-techniques are very high-dimensional, but also very highly structured.
-While its explicit dimensionality, the number of voxels, which varies with
-the resolution of the image is generally of the order of 100000, the number
-of samples available for analyses never exceeds hundreds or thousands.
-This \(n << p\) situation immediately implies an underdeterminedness for any
-linear model basing its decisions on dot products with the voxel values.
-
-Luckily, there is and abundance structure to be exploited, which can be
-injected into the estimation as a domain knowledge prior. Here we are 
-interested in incorporating knowledge about both the well-established 
-modules of functional specialization and the interactions of these modules
-amongst each other across the brain.
-%
+
+we need to inject domain knowledge into
+statistical estimations to harness the curse of dimensionality.
+two neurobiological design principles
+
+imposing parsimony
+integrative processes
+
+ This L1/L2 norm for group lasso has been extended to a more general setting to
+
+designed groups
+ the child nodes enter the set of relevant inputs only if its parent node does.
+
+should be able to estimate voxel level
+while taking into account known supravoxel structure.
+is instrumental in
 Developmentally, such large-scale networks emerge during late
@@
 in childhood.
-%
+
 In adults, nodes of a same cohesive network have more
@@
 (Anderson et al., 2013).
-%
-On the signal level, functional modules are localized structures implicating
-neighboring voxels in an image. A variety of known functional modules has
-been compiled into atlases of the brain. Different types of atlases rely on
-different ways of segregating modules from another. For instance, anatomical
-atlases rely on the variation of tissue properties across the brain, which
-can be at the cellular level or based on higher-order structure.
-%
-Global functional networks can be discovered by statistical analysis of
-functional brain imaging data, for example the BOLD contrast in fMRI. A
-well-established method of estimating these networks is independent 
-component analysis \cite{Hamalainen}. It robustly identifies the default
-mode, saliency and attention networks.
-%
-Since these network maps are for the most part disjoint spatially
-
-%% we need to inject domain knowledge into
-%% statistical estimations to harness the curse of dimensionality.
-%% two neurobiological design principles 
-%% 
-%% imposing parsimony
-%% integrative processes
-%% 
-%%  This L1/L2 norm for group lasso has been extended to a more general setting to
-%% 
-%% designed groups
-%%  the child nodes enter the set of relevant inputs only if its parent node does. 
-%%  
-%% should be able to estimate voxel level
-%% while taking into account known supravoxel structure.
-%% is instrumental in
-%% Developmentally, such large-scale networks emerge during late
-%% fetal growth (Doria et al., 2010), before cognitive capacities mature
-%% in childhood. 
-%% 
-%% In adults, nodes of a same cohesive network have more
-%% similar functional profiles than nodes from different networks
-%% (Anderson et al., 2013).
-%% 
-%% data exhibit natural correlations between neighboring voxels forming clusters
-%% 
-%% representing some phenomenon with as few variables as possible
-%% 
-%% neurobiologically motivated restrictions to complexity circumvented
-%% the curse of dimensionality
-%% three-dimensional spatial arrangement that respects
-%% the functional anatomy of the brain
-%% not ignore the spatial configuration
-%% 
-%% incorporate rich prior knowledge
-%% 
-%% If meaningful structures exist,
-%% we show that one can take advantage of such structures
-%% 
-%% Statistically,
-%% l1 and l2 are local sparsity priors
-%% -> resulting sparsity does yield structure
-%% we want to priviledge representations with structure
-%% 
-%% 
-%% => 
-%%  a biologically and statistically desirable bias
+
+data exhibit natural correlations between neighboring voxels forming clusters
+
+representing some phenomenon with as few variables as possible
+
+neurobiologically motivated restrictions to complexity circumvented
+the curse of dimensionality
+three-dimensional spatial arrangement that respects
+the functional anatomy of the brain
+not ignore the spatial configuration
+
+incorporate rich prior knowledge
+
+If meaningful structures exist,
+we show that one can take advantage of such structures
+
+Statistically,
+l1 and l2 are local sparsity priors
+-> resulting sparsity does yield structure
+we want to priviledge representations with structure
+
+=> 
+ a biologically and statistically desirable bias
 
@@
 \caption{\textbf{Building blocks of the region-network tree.}
-Depicts neurobiological priors introduced into the supervised classification
+Depicts neurobiological priors introduced into the classification problem 
 by hierarchical structured sparsity.
@@
 and
-the cerebellum that realizes motor behavior.
+the cerebellum that is involved in motor behavior.
 }
@@
 \caption{\textbf{Model performance across sparsity priors.}
-Compares the performance of 4 logistic regression estimators
-with different structured and unstructered sparsity terms
+Compares the performance of logistic regression estimators
+with 4 different structured and unstructered sparsity terms
 in classifying neural activity from 18 psychological tasks.
 The class-wise precision and recall metrics
-were obtained on the test set.
+were obtained on the same test set.
 %
@@
 imposed region compartments, but na\"ive to network structure.
-Structured trace-norm penalization (\textit{lower tight})
+Structured trace-norm penalization (\textit{lower right})
 imposed low-rank structure
@@
 Structured $\ell_1/\ell_2$ block norm with a hierarchy of
-both region and network priors (\textit{upper tight})
+both region and network priors (\textit{upper right})
 exhibited the best out-of-sample performance.
 %
-Consequently, a priori knowledge of both region and network neighborhoods
-was the most beneficial structured sparsity penalty.
+A priori knowledge of both region and network neighborhoods
+was hence most beneficial for predicting psychological tasks from
+brain maps.
 }
@@
 This classification estimator embraces a vision of neural activity structure
-that expects a minimum of
+that expectes a minimum of
 topographically and functionally independent brain voxel to be relevant.
@@
 Hierarchial tree sparsity demonstrated the best generalization
-in distinguishing unseen neural activity maps from 18 tasks
+in distinguihsing unseen neural activity maps from 18 tasks
 (89.67\%, mean recall XX.YY, mean precision XX.YY).
@@
 with increasing fraction
-of the available training data (\textit{columns}).
-For one example from 18 classes,
+of the available training data (\textit{left to right columns}).
+For one example (i.e., ``View tools'') from 18 psychological tasks,
 unthresholded axial maps of model weights
 are shown for comparison against
-the class sample average {\color{red} thresholded at p $<$ 0.01 ???}
-in the \textit{rightmost column}.
-The corresponding 18-class (``View tools'')
-out-of-sample accuracy
+the sample average of that class
+(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
+The out-of-sample accuracies for predicting all 18 classes
 is given in percent.
@@
 typical for brain imaging,
-hierarchical tree sparsity achieves
+hierarchical tree sparsity achieves much
 better support recovery with the biggest difference
@@
 neurobiologically informed logistic regression
-profits more from the increased information quantities than
+profits more from the available information quantities than
 neurobiologically naive logistic regression.
@@
 is systematically varied against each other.
-This region-network ratio (\textit{upper row}) weighted voxel groups
+This region-network ratio (\textit{upper fractions}) weighted voxel groups
 to priviledge sparse models in function space
@@
 (\textit{left columns}) or
-known brain networks compartments
+known brain networks neighborhoods
 (\textit{right columns}).
-Among the 18 classes, the model weights are shown for the
+Among the 18 classes, the model weights are shown for the psychological
 tasks (\textit{from top to bottom}): tongue movement, listening stories,
@@
 the class-wise mean neural activty
-in the \textit{rightmost column}.
+(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
 %
@@
 in hierarchical structured sparsity can
-yield essentially similar model performance.
-%
-Priviledging region versus network structure during model selection
-recovers complementary aspects of the brain activity pattern.
+yield comparable model performance.
+%
+Favoring region versus network structure during model selection
+recovers complementary aspects of the neural activity pattern.
 %

### 2016-01-28 paper/paper.tex
first abstract

@@
 \begin{abstract}
-% Imaging neuroscience links human behavior to aspects of brain
-% biology in ever-increasing datasets.
+Structured sparsity penalization has recently improved
+statistical models applied to high-dimensional data in various domains.
+As an extension to neuroscience,
+network hierarchies of brain regions have been incorporated as priors into
+brain imaging analysis.
+This remarries the inextricable perspectives of
+functional segregation and functional integration
+that are routinely divorced in neuroscientific research.
+%
+Region-network hierarchical priors for logistic regression classification
+in a reference dataset are
+shown to outperform na\"ive $\ell_1$-norm and
+trace-norm penalization, as well as neurobiologically
+informed $\ell_1/\ell_2$-block-norm group sparsity.
+Varying the relative importance of
+region and network structure within the hierarchical tree prior
+recovered complementary aspects of the neural activity pattern
+with similar predictive accuracies.
+%
+In sum,
+we demonstrate that priors of local and global neurobiological knowledge can enhance
+out-of-sample performance and domain interpretability
+by structed sparsity principles.
 

### 2016-01-29 paper/paper.tex
pass over abstract

--- 2016-01-28 paper/paper.tex
@@
 \begin{abstract}
-% Imaging neuroscience links human behavior to aspects of brain
-% biology in ever-increasing datasets.
+Structured sparsity penalization has recently improved
+statistical models applied to high-dimensional data in various domains.
+As an extension to imaging neuroscience,
+priors on network hierarchies of brain regions have been incorporated into
+logistic-regression estimators for neural activity maps.
+This remarries the perspectives of
+functional segregation and functional integration
+that are routinely divorced in neuroscientific research.
+%
+Region-network hierarchical priors for supervised classification
+of 18 psychological tasks
+from a reference dataset are
+shown to outperform na\"ive $\ell_1$-norm and
+trace-norm penalization, as well as neurobiologically
+informed $\ell_1/\ell_2$-block-norm group sparsity.
+Varying the relative importance of
+region and network structure within the hierarchical tree prior
+recovered complementary aspects of the neural activity pattern
+with similar predictive accuracies.
+%
+In sum,
+we demonstrate that priors of local and global neurobiological knowledge can enhance
+out-of-sample performance and domain interpretability
+by hierarchical tree sparsity.
 
 \textbf{\\keywords}:
-Sparsity-inducing norms, hierarchical structured sparsity,
+Sparsity-inducing norms, hierarchical tree sparsity,
 numerical optimization,
-systems neuroscience, brain imaging,
+systems neuroscience,
 functional specialization, functional integration

### 2016-01-29 paper/paper.tex
small pass on methods

@@
 estimators.
-We make use of the hierarchical group lasso as introduced by Jennaton and 
-others in \cite{jenatton2011structured} to create a set of convex penalties
-with which we can probe this interplay between regional specificity and 
-inter-regional functional integration during different cognitive tasks.
-%
-\paragraph{Rationale}
+We capitalize on hierarchical group lasso as introduced by Jennaton and 
+others in \cite{jenatton2011structured} to create a set of convex penalty terms.
+These can probe the interplay between regional specialization and 
+inter-regional functional integration during defined psychological tasks.
+%
+\paragraph{Rationale.}
 Three-dimensional voxel brain images as obtained by various neuroimaging
 techniques are very high-dimensional, but also very highly structured.
-While its explicit dimensionality, the number of voxels, which varies with
-the resolution of the image is generally of the order of 100000, the number
-of samples available for analyses never exceeds hundreds or thousands.
-This \(n << p\) situation immediately implies an underdeterminedness for any
-linear model basing its decisions on dot products with the voxel values.
-
-Luckily, there is and abundance structure to be exploited, which can be
+While its explicit dimensionality, the number of brain voxels, which varies with
+the resolution of the image is generally of the order of 100,000, the number
+of samples available for analyses rarely exceeds hundreds or thousands.
+This \(n << p\) scenario immediately implies underdetermination of any
+linear model based on dot products with the voxel values.
+
+Yet, there is abundant structure to be exploited, which can be
 injected into the estimation as a domain knowledge prior. Here we are 
 interested in incorporating knowledge about both the well-established 
-modules of functional specialization and the interactions of these modules
-amongst each other across the brain.
+modules of functional specialization and the spatiotemporal interactions
+between these.
 %
 Developmentally, such large-scale networks emerge during late
-fetal growth (Doria et al., 2010), before cognitive capacities mature
+fetal growth (Doria et al., 2010), before mental capacities mature
 in childhood. 
 %
-In adults, nodes of a same cohesive network have more
+In adults, nodes of a such a spatiotemporally cohesive network have more
 similar functional profiles than nodes from different networks
@@
 %
-Global functional networks as estimated by ICA are contiuous brain maps
+Global functional networks as estimated by ICA are continuous brain maps
 attributing weights to each voxel. Since the regions involved in these
 networks are nevertheless largely disjoint spatially and roughly in
-correspondence with module boundaries {\color{red} Michael: verify this!!!}, 
+correspondence with module boundaries {\color{red} Danilo: Ok!}, 
 it is possible to uniquely associate each module from a region atlas to one
@@
 
-This correspondence makes it possible to encode our knowledge about the 
+This correspondence makes it possible to inject established knowledge about the 
 networks and regions into a hierarchy: A brain contains a certain number of
@@
 
-\paragraph{Problem formulation}
+\paragraph{Problem formulation.}
 We formulate our estimation problem in the framework of regularized risk

### 2016-01-30 paper/paper.tex
zeroing subanalysis

@@
 %
+In an important subanalysis,
+the gain of the combined region-network prior was confirmed by
+selectively zeroing the $eta_g$ coefficients of either all region groups
+or all network groups in the hierarchical prior.
+Removing region structure from the prior achieved
+88,84\% accuracy (mean recall XX.YY, mean precision XX.YY),
+while removing network structure from the prior achieved
+87,05\% accuracy (mean recall XX.YY, mean precision XX.YY).
+These results from partial priors are indeed outperformed
+the full region-network tree prior at 89,67\% accuracy
+(mean recall XX.YY, mean precision XX.YY).
+%
 In sum,

### 2016-01-30 paper/paper.tex
reformulate minimally

@@
 \cite{bach2012optimization}.
-Such restrictions to complexity are an attractive plan of attacked
+Such restrictions to complexity are an attractive plan of attack
 for the $\textgreater$100,000 variables of brain maps.
 Yet, what generally accepted neurobiological structure lends itself
-to harness the
-\textit{curse of dimensionality} by structured sparsity priors?
+to fruitful exploitation using structured sparsity priors?
 

### 2016-01-30 paper/paper.tex
big pass over sections

--- 2016-01-30 paper/paper.tex
@@
 region and network structure within the hierarchical tree prior
-recovered complementary aspects of the neural activity pattern
+recovered complementary aspects of the neural activity patterns
 with similar predictive accuracies.
@@
 in several detailed anatomical maps
-\cite{brodmann1909vergleichende, vogt1919allgemeine}.
+\cite{brodmann1909vergleichende}.
 Regarding axonal connections,
@@
 % study
-Building on these two major interpretational streams in systems neuroscience,
+Building on these two major interpretational traditions in systems neuroscience,
 the present study proposes to incorporate
@@
 have recently made much progress in various application domains
-from processing of auditory signals \cite{daudet2004sparse},
+from processing auditory signals \cite{daudet2004sparse},
 natural images \cite{harzallah2009combining} and
@@
 assuming special structure.
-Structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
+Structured $\ell_1/\ell_2$-block norm with additional $\ell_1$ term
 (\textit{lower left})
@@
 with sparsity of network patterns, but na\"ive to region structure.
-Structured $\ell_1/\ell_2$ block norm with a hierarchy of
+Structured $\ell_1/\ell_2$-block-norm with a hierarchy of
 both region and network priors (\textit{upper right})
@@
 %
-The stratified and shuffled training data were submitted to
+The stratified and shuffled training data were submitted
 to a nested cross-validation scheme
@@
 evaluated on an identical test set in all settings.
-%
-Hierarchial tree sparsity demonstrated the best generalization
-in distinguishing unseen neural activity maps from 18 tasks
+
+Across analyses,
+hierarchial tree sparsity was most successful
+in distinguishing unseen neural activity maps from 18 psychological tasks
 (89.67\%, mean recall XX.YY, mean precision XX.YY).
-It was closely followed by logistic regression with trace-norm
-regularization that is structured but not neurobiologically informed
+It was closely followed by logistic regression
+structured by trace-norm regularization
 (89.43\%, mean recall XX.YY, mean precision XX.YY).
 Lasso featured an average performance comparing to the other sparse estimators
-(88.60\%, mean recall XX.YY, mean precision XX.YY)
-Introduced a priori knowledge of brain region compartments
+(88.60\%, mean recall XX.YY, mean precision XX.YY).
+Introducing a priori knowledge of brain region compartments
 by sparse group sparsity performed worst
@@
 In an important subanalysis,
-the gain of the combined region-network prior was confirmed by
-selectively zeroing the $eta_g$ coefficients of either all region groups
+the gain of the combined region-network prior was also confirmed by
+selectively zeroing the $\eta_g$ coefficients of all region groups
 or all network groups in the hierarchical prior.
@@
 biasing sparse model selection by domain knowledge of region-network hierarchies
-outperformed other types of frequently used sparse penalization techniques.
+outcompeted other types of frequently used sparse penalization techniques.
 
@@
 (\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-The out-of-sample accuracies for predicting all 18 classes
+The out-of-sample accuracies for predicting all 18 psychological tasks
 is given in percent.
@@
 support recovery than
-$\ell_1$-constrained logistic regression na\"ive to neurobiology
+neurobiology-na\"ive $\ell_1$-constrained logistic regression
 in the data-scarce and data-rich scenarios.
 %
-The HCP task data with examples from 18 classes were first divided into
+The HCP task data with examples from 18
+psychological tasks were first divided into
 90\% of training set (i.e., 7584 neural activity maps) and
-10\% of test set (i.e., 842 maps).
+10\% of test set (i.e., 842 neural activity maps).
 Both learning algorithms were fitted based on the
@@
 evaluated on an identical test set in all settings.
-%
-Three observation have been made.
-In the data-scarce scenario (i.e., 1/5 of actual training data),
+
+Three observations have been made.
+In the data-scarce scenario (i.e., 1/5 of available training data),
 hierarchical tree sparsity achieved the biggest advantage
@@
 better support recovery with weight maps already much closer
-to the training data average.
+to the class averages.
 In the case of scarce training data, which is typical for the brain imaging domain,
-regularization by region-network priors indeed allowed for
+regularization by region-network priors thus allowed for
 more effective extraction of classification-relevant structure
-from the neural activity scans.
-%
-Across scenarios,
-the weight maps from ordinary logistic regression exhibit
-higher variance and many more zero coefficients
+from the neural activity maps.
+%
+Across training data fractions,
+the weight maps from ordinary logistic regression exhibited
+higher variance and more zero coefficients
 than hierarchical tree logistic regression.
@@
 neurobiologically informed logistic regression
-profits more from the increased information quantities than
-neurobiologically naive logistic regression.
+profited more from the increased information quantities than
+neurobiologically na\"ive logistic regression.
 That is, the region-network priors actually further enhance the similarity
@@
 was quantified (Figure \ref{fig_regnetratio}).
-The $\eta_g$ group of region priors was multiplied with a
+The group weight $\eta_g$ of region priors was multiplied with a
 region-network ratio, while the
-$\eta_g$ group of network priors was biased by the corresponding
-network-region ratio. A region-network ratio of 3, for instance,
+group weight $\eta_g$ of network priors was divided by that
+region-network ratio. For instance, a region-network ratio of 3
 increased the relative importance of known region structure
-by multiplying $\frac{3}{1}$ to the
-$\eta_g$ factor of all region groups
+by multiplying $\frac{3}{1}$ to
+$\eta_g$ of all region group penalties
 and multiplying
-$\frac{1}{3}$ to all network groups.
+$\frac{1}{3}$ to $\eta_g$ of all network group penalties.
 The data splitting cross-validation scheme was identical to the
 above modelling experiments.
-%
+
 As the most important observation,
 a range between region-dominant and network-dominant structured penalties
-yields quantitatively almost identical generalization to new data
+yielded quantitatively almost identical generalization to new data
 but qualitatively different decision functions manifested in the weight maps
@@
 coefficients in either region compartments or network compartments
-can similarly extrapolation to unseen neural activity maps.
+can similarly extrapolate to unseen neural activity maps.
 Second,
-these perform similar to equilibrated region-network priors
+these achieve classification performance
+comparable to equilibrated region-network priors
 that set less voxel coefficients to zero and spread the
@@
 overly strong emphasis on either level of the hierarchical prior
-can yield the neurobiologically informative maps
+can yield the neurobiologically informative results with maps
 of the most necessary region or network structure for
@@
 functional segregation into discrete brain regions
-and functional integration by interregional brain networks.
-%
-This paper demonstrates the simultaneous exploitation of
+\cite{passingham2002}
+and functional integration by interregional brain networks
+\cite{sporns14nn}.
+%
+This proof-of-concept study demonstrates the simultaneous exploitation of
 both these neurobiological compartments
@@
 The present approach has important advantages over previous
-neuroimaging studies that capitalized on dimensionality reduction to harness
-the curse of dimensionality.
-They often used preliminary region-wise pooling functions
+analysis strategies that rely on dimensionality reduction of
+the neuroimaging data to harness the curse of dimensionality.
+They often use preliminary pooling functions within regions
 or regression against network templates
 for subsequent supervised learning on the aggregated feature space.
-Such lossy two-step approaches of feature engineering and inference
-\textit{i)} can only account for either functional specialization or
-functional integration of brain organization,
+Such lossy approaches divided into feature engineering and inference steps
+\textit{i)} can only satisfy the specialization or
+integration account of brain organization,
 \textit{ii)} depend on the ground truth being a region or network effect,
@@
 %
-Hierarchical region-network sparsity overcomes these shortcomings
+Hierarchical region-network sparsity addresses these shortcomings
 by estimating individual voxel contributions
@@
 The principled regularization scheme could even inform
-unsupervised structure discovery methods,
+unsupervised structure-discovery methods,
 such as principal component analysis
@@
 for predicting diagnosis,
-disease trajectories, and treatment responses
+disease trajectories, and treatment response
 in personalized psychiatry and neurology.

### 2016-01-30 paper/paper.tex
typo

@@
 Functional specialization emphasizes that microscopically distinguishable
-brain regions are responsible distinct classes of computational processes
+brain regions are responsible for distinct classes of computational 
+processes
 \cite{kanwisher2010functional}.

### 2016-02-01 paper/paper.tex
started on optimization

@@
 
+One can read off the formula that decreasing \(\alpha\) leads to less 
+penalization of brain networks and thus to tendentially fully active groups
+and dense brain maps. If at the same time \(\beta\) is increased to a point
+of inducing group sparsity, then only the structure of brain regions encoded
+by \(\mathcal G\) is present. Conversely, if \(\beta\) is decreased to 
+become non-selective, and \(\alpha\) is increased to group selectivity,
+then the structure imposed will come from \(\mathcal H\), leading to the
+selection of brain networks rather than regions.
+
+It is important to note that the above trade-off shows that predominance
+can be either attributed to regions or networks, but that nevertheless the
+penalty structure is hierarchical: If the network penalty layer sets a
+network group to zero, then all the contained region groups are forced to
+have activity zero. Conversely, if a brain region has non-zero coefficients,
+then necessarily the network containing it must be active.
+This relation is asymmetric, since when swapping the roles of \(\mathcal G\)
+ and \(\mathcal H\), these statements do not hold true anymore. A brain 
+region can set all its coefficients to zero without forcing the 
+corresponding network to zero. A brain network can be active without its
+subregions necessarily being active.
+When evaluating the trade-off in \((\alpha, \beta)\), this needs to be taken
+into account.
+
 The prediction problem at hand is a multiclass classification. We choose to
@@
 if \(y\in{-1, 1}\) and with \(x_i\in\R^p\) the training sample brain images.
+
+\paragraph{Optimization.}
+We optimize the data loss function using an iterative forward-backward
+scheme analogous to (F)ISTA for the lasso \cite{beck2009}. We divide the
+loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
+logistic regression loss) and a potentially non-smooth, convex 
+regularization term
 

### 2016-02-01 paper/paper.tex
described algorithm

@@
 \[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
-if \(y\in{-1, 1}\) and with \(x_i\in\R^p\) the training sample brain images.
+if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.
 
@@
 We optimize the data loss function using an iterative forward-backward
-scheme analogous to (F)ISTA for the lasso \cite{beck2009}. We divide the
+scheme analogous to (F)ISTA for the lasso \cite{beck2009}. 
+{\color{red} Michael: Algorithm specification to be removed for ICML - supposed known, except possibly for hierarchical prox.}
+We divide the
 loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
 logistic regression loss) and a potentially non-smooth, convex 
-regularization term
+regularization term \(G(w)\). 
+Define \(\prox_{\gamma G}(v) = (\Id + \gamma\partial G)^{-1}(v)\), where \(\partial G\) is the subdifferential of \(G\) and 
+let \(\nabla F(v)\) be the gradient of \(F\) in \(v\). Further let \(L > 0\)
+be a Lipschitz constant of the gradient of \(F\) and choose a step size
+\(\varepsilon\in (0, \frac{2}{L})\). Starting with an arbitrary 
+initialization of \(w_0\), putting \(z_1 = w_0\) and \(t_1 = 1\), then for
+\(k\geq 1\) until convergence do:
+\begin{eqnarray*}
+  x_k & = & \prox_{\varepsilon G}(y_k - \varepsilon\nabla F(y_k))\\
+  t_{k + 1} & = & \frac{1 + \sqrt{1 + 4 t_k^2}}{2}\\
+  y_{k + 1} & = & x_k + \left(\frac{t_k - 1}{t_{k + 1}}\right)(x_k - x_{k - 1})
+\end{eqnarray*}
+In our case \(G(v) = \lambda\Omega(v)\). Splitting \(\Omega(v) = \Omega_{\mathcal H}(v) + \Omega_{\mathcal G}(v)\) with 
+\(\Omega_{\mathcal H}(v) = \alpha\sum_{h\in\mathcal H}\eta_h\|v_h\|_2\) and
+\(\Omega_{\mathcal G}(v) = \beta\sum_{g\in\mathcal G}\eta_g\|v_g\|_2\), we observe
+that \[\prox_{\varepsilon\lambda\Omega_{\mathcal H}}(v) = \sum_{h\in\mathcal H}\iota_h\left([\|v_h\|_2 > \eta_h\varepsilon\lambda\alpha]\left(v_h - \eta_h\varepsilon\lambda\alpha\frac{v_h}{\|v_h\|_2}\right)\right),\]
+where \(\iota_h\) is the canonical injection of the group \(h\) into 
+\(\R^p\) (if \(\pi_g: v\mapsto v_g\), then \(\iota_g = \pi_g^\ast\) the 
+adjoint/transposed operator). This holds analogously for 
+\(\Omega_{\mathcal G}\).
+According to \cite{jenatton2011}, the proximal operator of 
+the hierarchical penalty \(\varepsilon\lambda\Omega\) is
+\[\prox_{\varepsilon\lambda\Omega}(v) = \prox_{\varepsilon\lambda\Omega_{\mathcal H}}\circ\prox_{\varepsilon\lambda\Omega_{\mathcal G}}(v).\]
 

### 2016-02-01 paper/paper.tex
more on algorithm

@@
 
-{\color{red}
-MISSING
-\begin{itemize}
-\item cross-validation scheme
-\item analysis of penalty tradeoff (CV scheme for that?)
-\item mentioning of control methods in methods. Trace norm, sparse group sparsity. Anything else? ENET?
-\end{itemize}
-}
+\paragraph{Hyperparameter optimization.}
+{\color{red} NEEDS EMBELLISHING}
+We perform nested cross-validation to obtain optimal hyperparameters. 
+In order to analyse their effect in detail, we split our analysis into two 
+parts.
+\begin{enumerate}
+\item In the first part, we optimize the trade-off between the different hierarchy levels as well as the global penalty level for maximal prediction.
+\item in the second part, we select the optimal global penalty level for 
+given trade-off ratios.
+\end{enumerate}
+
+\paragraph{Control methods}
+{\color{red} needs embellishing}
+We evaluate our tree structure against other commonly used structured sparse
+penalties.
 

### 2016-02-01 srne_plot.py
sanitize figs

@@ -16,19 +16,28 @@ try:
 except:
     pass
 
+plotting.plot_anat('colin.nii', cut_coords=(0, 0, 0), draw_cross=False,
+                  title='')
+plt.savefig('plots/colin.png')
+
 for i_prior, title_prior in example_net_reg_priors:
     out_fname = 'plots/prior_example_%s' % title_prior.replace(' ', '_')
-    plotting.plot_epi('resources/dbg_raal.nii.gz', title=title_prior,
+    plotting.plot_epi('resources/dbg_raal.nii.gz', title='',
                       cut_coords=(0, 0, 0), draw_cross=False)
     plt.savefig(out_fname + '_reg.png')
 
     net_regdmn_nii = index_img('resources/rsn_12.nii.gz', i_prior)
     plotting.plot_stat_map(net_regdmn_nii, cut_coords=(0, 0, 0),
-                           title=title_prior,
+                           title='',
                            colorbar=False, draw_cross=False, black_bg=True)
     plt.savefig(out_fname + '_net.png')
 
     net_regdmn_nii = index_img('resources/rsn_12_assigned_aal.nii.gz', i_prior)
     plotting.plot_epi(net_regdmn_nii, cut_coords=(0, 0, 0), draw_cross=False,
-                      title=title_prior)
-    plt.savefig(out_fname + '_regnet.png')
+                      title='')
+    # plotting.plot_stat_map(stat_map_img=net_regdmn_nii,
+    #                        bg_img=
+    #                        cut_coords=(0, 0, 0),
+    #                        title=title_prior,
+    #                        colorbar=False, draw_cross=False, black_bg=True)
+    plt.savefig(out_fname + '_regnet.png', transparent=True)

### 2016-02-02 paper/paper.tex
sanitize figs
next figure sanitized
pass on methods

@@
 As an extension to imaging neuroscience,
-priors on network hierarchies of brain regions have been incorporated into
-logistic-regression estimators for neural activity maps.
+the present work incorporates
+priors on network hierarchies of brain regions into
+logistic-regression estimators to distinguish neural activity.
 This remarries the perspectives of
@@
 from a reference dataset are
-shown to outperform na\"ive $\ell_1$-norm and
+shown to outperform naive $\ell_1$-norm and
 trace-norm penalization, as well as neurobiologically
 informed $\ell_1/\ell_2$-block-norm group sparsity.
-Varying the relative importance of
-region and network structure within the hierarchical tree prior
-recovered complementary aspects of the neural activity patterns
-with similar predictive accuracies.
-%
-In sum,
-we demonstrate that priors of local and global neurobiological knowledge can enhance
-out-of-sample performance and domain interpretability
+Weighing the relative importance of
+region and network structure within the hierarchical tree penalty
+recovered complementary aspects of the neural activity patterns.
+%
+It is thus demonstrated
+that priors of local and global neurobiological knowledge
+can enhance
+generalization performance, sample complexity, and domain interpretability
 by hierarchical tree sparsity.
@@
 recent passage from the classical regime (i.e., ``long data")  to
-the high-dimensional regime (i.e., ``wide data")
-\cite{jordan2015massive}.
+the high-dimensional regime (i.e., ``wide data").
+% the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
 Also in the brain imaging domain,
@@
 \textit{sparsity} assumptions
-\cite{buhlmann2011statistics, hastie2015statistical}.
+\cite{hastie2015statistical}.
 They act as a 
@@
 \cite{bach2012optimization}.
-Such restrictions to complexity are an attractive plan of attack
-for the $\textgreater$100,000 variables of brain maps.
+Such restrictions to statistical complexity
+are an attractive plan of attack
+for the $\textgreater$100,000 variables per brain map.
 Yet, what generally accepted neurobiological structure lends itself
@@
 \cite{kanwisher2010functional}.
-Functional integration, in turn, emphasizes that brain function
+Conversely, functional integration emphasizes that brain function
 is enabled by complex connections between these
@@
 %
-These notions were predominantly derived from
-invasive examination of anatomy (i.e., histological preparation),
-connectivity (i.e., axonal tracing),
-and functional properties
-(i.e., single-cell recordings) in animals.
-Regarding functional segregation into specialized regions,
-early histological investigations into the microscopic heterogeneity of
-the human cerebral cortex have resulted
-in several detailed anatomical maps
-\cite{brodmann1909vergleichende}.
-Regarding axonal connections,
-each such cortical area has been observed
-to possess a unique set of incoming and outgoing connections
-\cite{passingham2002, young93monkey, scannell95cat}.
-%
-Both
-local
-%cyto- and chemoarchitectonic
+Local
 infrastructure
-and its unique global connectivity profile
-together are thought to realize brain function.
-%
-In sum,
-cortical brain modules versus connections between them
-reflect 
-functional specialization versus functional integration
-\cite{friston2002beyond, mesulam_sensation}.
-Importantly,
+and its unique global connectivity profile are thought to go hand-in-hand
+to realize brain function.
+%
+However,
 probably no existing brain analysis method acknowledges that
 both functional organizations are inextricably involved
-in the realization of mental operations
-\cite{tononi1998complexity, saygin2012}.
-
-% SPECIAL
+in the realization of mental operations.
+
 Functional specialization has been
@@
 %
-Single-cell recordings and microscopic examination
-revealed, for instance, the
+For instance,
+single-cell recordings and microscopic examination
+revealed the
 specialization in the occipital visual cortex into V1, V2, V3, V3A/B, and V4
@@
 \cite{iaria2008contrib}.
-The whole-brain localization of
-sensory, motor, and emotional functions to cortical areas
-% in the living brain
-was later enabled by
-non-invasive brain imaging with
-functional magnetic resonance imaging (fMRI) and
-positron emission tomography (PET)
-\cite{fristen1997imaging}.
-Further,
-radioactive mapping of neurotransmitter receptors
-rendered accessible yet another
-local characteristic of neuronal populations
-\cite{zilles2009receptor}.
-% allude to our many-regions layer in our methods
-In the computational era,
-automatic clustering methods are increasingly employed to
-regionally differentiate the cerebral cortex,
-which can partly be more fine-grained than
-classical microscopical borders
-\cite{behrens03, cbp2015review}.
-High-thoughput approaches today enable
-ultrahigh-resolution 3D models of brain anatomy
-at near-cellular scale
-\cite{amunts2013bigbrain}.
 %
@@
 as the basic architecture of brain organization.
-
 % INTEGRAL
@@
 from circumscribed regions to network stratifications
-in systems neuroscience \cite{yuste2015, stephan_dys}.
-%
-Invasive axonal tracing studies in monkeys were complemented
-by diffusion MRI tractography in humans
-as a now frequently employed method to
-outline fiber bundles between brain regions
-\cite{jbabdi2013long}.
+in systems neuroscience \cite{yuste2015}.
+%
 Besides analyses of
 electrophysiological oscillations
-\cite{buzsaki2004neuronal}
+% \cite{buzsaki2004neuronal}
 and
-graph-theoretical properties \cite{bullmore2009complex},
+graph-theoretical properties,
+% graph-theoretical properties \cite{bullmore2009complex},
 studies of
-functional connectivity \cite{buckner2013opportunities} and
+functional connectivity correlation \cite{buckner2013opportunities} and
 independent component analysis (ICA) \cite{beckmann2005}
@@
 in neuroimaging.
-These revealed the important implication of
-canonical brain networks across psychological tasks,
-including the so-called
-``default-mode network'' \cite{raichle2001pnas},
-``salience network'' \cite{seeley2007dissociable},
-and ``dorsal attention network'' \cite{corbettashul2008}. 
-Characteristic changes in the configuration of
-these macroscopical networks
-were repeatedly observed to be induced
-by the onset of given psychological tasks \cite{fransson2006}.
-% Such task-induced mechanisms orchestrating supraordinate networks
-% might be subserved by the right anterior insula \cite{sridh2008}
-% and temporo-parietal junction \cite{bzdok2013tpj}.
 %
@@
 in stark constrast to methods examining regional specialization.
+
+% % specialization & integration
+% Concepts on human brain organization have long been torn
+% between the two extremes
+% \textit{functional specialization} and \textit{functional integration}.
+% Functional specialization emphasizes that microscopically distinguishable
+% brain regions are responsible for distinct classes of computational 
+% processes
+% \cite{kanwisher2010functional}.
+% Functional integration, in turn, emphasizes that brain function
+% is enabled by complex connections between these
+% distinct brain regions \cite{sporns14nn}.
+% %
+% These notions were predominantly derived from
+% invasive examination of anatomy (i.e., histological preparation),
+% connectivity (i.e., axonal tracing),
+% and functional properties
+% (i.e., single-cell recordings) in animals.
+% Regarding functional segregation into specialized regions,
+% early histological investigations into the microscopic heterogeneity of
+% the human cerebral cortex have resulted
+% in several detailed anatomical maps
+% \cite{brodmann1909vergleichende}.
+% Regarding axonal connections,
+% each such cortical area has been observed
+% to possess a unique set of incoming and outgoing connections
+% \cite{passingham2002, young93monkey, scannell95cat}.
+% %
+% Both
+% local
+% %cyto- and chemoarchitectonic
+% infrastructure
+% and its unique global connectivity profile
+% together are thought to realize brain function.
+% %
+% In sum,
+% cortical brain modules versus connections between them
+% reflect 
+% functional specialization versus functional integration
+% \cite{friston2002beyond, mesulam_sensation}.
+% Importantly,
+% probably no existing brain analysis method acknowledges that
+% both functional organizations are inextricably involved
+% in the realization of mental operations
+% \cite{tononi1998complexity, saygin2012}.
+% 
+% 
+% 
+% % SPECIAL
+% Functional specialization has been
+% explored and interpreted based on many different research methods.
+% %
+% Single-cell recordings and microscopic examination
+% revealed, for instance, the
+% specialization in the occipital visual cortex into V1, V2, V3, V3A/B, and V4
+% \cite{hubel1962receptive, zeki1978functional}.
+% Tissue lesion of the mid-fusiform gyrus of the visual system,
+% in turn,
+% was frequently reported to impair
+% recognition of others' identity from faces
+% \cite{iaria2008contrib}.
+% The whole-brain localization of
+% sensory, motor, and emotional functions to cortical areas
+% % in the living brain
+% was later enabled by
+% non-invasive brain imaging with
+% functional magnetic resonance imaging (fMRI) and
+% positron emission tomography (PET)
+% \cite{fristen1997imaging}.
+% Further,
+% radioactive mapping of neurotransmitter receptors
+% rendered accessible yet another
+% local characteristic of neuronal populations
+% \cite{zilles2009receptor}.
+% % allude to our many-regions layer in our methods
+% In the computational era,
+% automatic clustering methods are increasingly employed to
+% regionally differentiate the cerebral cortex,
+% which can partly be more fine-grained than
+% classical microscopical borders
+% \cite{behrens03, cbp2015review}.
+% High-thoughput approaches today enable
+% ultrahigh-resolution 3D models of brain anatomy
+% at near-cellular scale
+% \cite{amunts2013bigbrain}.
+% %
+% As a crucial common point,
+% all these methodological approaches
+% yield neuroscientific findings
+% that are naturally interpreted according to
+% non-overlapping, discrete region compartments
+% as the basic architecture of brain organization.
+% 
+% 
+% 
+% % INTEGRAL
+% It is more recent
+% that the main interpretational focus has shifted
+% from circumscribed regions to network stratifications
+% in systems neuroscience \cite{yuste2015, stephan_dys}.
+% %
+% Invasive axonal tracing studies in monkeys were complemented
+% by diffusion MRI tractography in humans
+% as a now frequently employed method to
+% outline fiber bundles between brain regions
+% \cite{jbabdi2013long}.
+% Besides analyses of
+% electrophysiological oscillations
+% \cite{buzsaki2004neuronal}
+% and
+% graph-theoretical properties \cite{bullmore2009complex},
+% studies of
+% functional connectivity \cite{buckner2013opportunities} and
+% independent component analysis (ICA) \cite{beckmann2005}
+% became the workhorses of network discovery
+% in neuroimaging.
+% These revealed the important implication of
+% canonical brain networks across psychological tasks,
+% including the so-called
+% ``default-mode network'' \cite{raichle2001pnas},
+% ``salience network'' \cite{seeley2007dissociable},
+% and ``dorsal attention network'' \cite{corbettashul2008}. 
+% Characteristic changes in the configuration of
+% these macroscopical networks
+% were repeatedly observed to be induced
+% by the onset of given psychological tasks \cite{fransson2006}.
+% % Such task-induced mechanisms orchestrating supraordinate networks
+% % might be subserved by the right anterior insula \cite{sridh2008}
+% % and temporo-parietal junction \cite{bzdok2013tpj}.
+% %
+% As a common point of all these methods,
+% interpretation of findings naturally embraces
+% cross-regional integration by
+% overlapping network compartments
+% as the basic architecture of brain organization,
+% in stark constrast to methods examining regional specialization.
 
@@
 natural images \cite{harzallah2009combining} and
-videos \cite{kang2015structured, kim2010sparse}
+videos \cite{kang2015structured}
+% videos \cite{kang2015structured, kim2010sparse}
 to
 astrophysics \cite{vinci2014estimating},
-genetics \cite{rapaport2008classification, kim2012tree},
+genetics \cite{kim2012tree},
+% genetics \cite{rapaport2008classification, kim2012tree},
 and
@@
 %
-This is extended by the present work that
-introduced neuroscience-specific estimators capitalizing on
-neurobiologically plausible region and network priors.
+The recently suggested hierarchical tree penalties for imaging neuroscience
+\cite{jenatton2011multi} will be extended
+by introducing neurobiologically plausible region and network priors
+to design neuroscience-specific estimators.
 %
@@
 and generalize better to new samples
-than domain-na\"ive estimators.
+than domain-naive estimators.
 
 \section{Methods}
-Our main contribution is the domain-specific adaptation of sparse structured
-penalties making it possible to jointly incorporate functional 
-specialization and functional integration priors into statistical 
+The main contribution is the domain adaptation of hierarchical structured
+tree penalties to jointly incorporate region 
+specialization and network integration priors into supervised 
 estimators.
-We capitalize on hierarchical group lasso as introduced by Jennaton and 
-others in \cite{jenatton2011structured} to create a set of convex penalty terms.
-These can probe the interplay between regional specialization and 
-inter-regional functional integration during defined psychological tasks.
+We capitalize on hierarchical group lasso as recently introduced
+\cite{jenatton2011structured} to create a set of convex penalty terms.
+These allow acknowledging the interplay between local specialization and 
+global connectivity during defined psychological tasks.
 %
 \paragraph{Rationale.}
-Three-dimensional voxel brain images as obtained by various neuroimaging
-techniques are very high-dimensional, but also very highly structured.
-While its explicit dimensionality, the number of brain voxels, which varies with
-the resolution of the image is generally of the order of 100,000, the number
-of samples available for analyses rarely exceeds hundreds or thousands.
-This \(n << p\) scenario immediately implies underdetermination of any
+3D brain maps obtained by neuroimaging
+techniques are high-dimensional but also highly structured.
+While its explicit dimensionality, the number of brain voxels,
+typically exceeds 100,000 variables, the number
+of samples rarely exceeds few hundreds.
+This \(n << p\) scenario directly implies underdetermination of any
 linear model based on dot products with the voxel values.
 
-Yet, there is abundant structure to be exploited, which can be
-injected into the estimation as a domain knowledge prior. Here we are 
-interested in incorporating knowledge about both the well-established 
-modules of functional specialization and the spatiotemporal interactions
+Yet, the abundant structure can be exploited by
+injecting domain-knowledge priors into the statistical estimation process.
+Here we are 
+interested in well-established neurobiological knowledge about
+brain regions of functional specialization and spatiotemporal interactions
 between these.
 %
-Developmentally, such large-scale networks emerge during late
-fetal growth (Doria et al., 2010), before mental capacities mature
-in childhood. 
-%
-In adults, nodes of a such a spatiotemporally cohesive network have more
+These large-scale brain networks emerge in human individuals around birth
+\cite{doria2010}, before mental capacities mature in childhood. 
+In adults,
+the sets of regions that compose the spatiotemporally cohesive network have more
 similar functional profiles than nodes from different networks
-(Anderson et al., 2013).
-%
-On the signal level, functional modules are localized structures implicating
-neighboring voxels in an image. A variety of known functional modules has
-been compiled into atlases of the brain. Different types of atlases rely on
-different ways of segregating modules from another. For instance, anatomical
-atlases rely on the variation of tissue properties across the brain, which
-can be at the cellular level or based on higher-order structure.
-%
-Global functional networks can be discovered by statistical analysis of
-functional brain imaging data, for example the BOLD contrast in fMRI. A
-well-established method of estimating these networks is independent 
-component analysis \cite{Hamalainen}. It robustly identifies the default
-mode, saliency and attention networks.
-%
-Global functional networks as estimated by ICA are continuous brain maps
-attributing weights to each voxel. Since the regions involved in these
-networks are nevertheless largely disjoint spatially and roughly in
-correspondence with module boundaries {\color{red} Danilo: Ok!}, 
-it is possible to uniquely associate each module from a region atlas to one
-of the extracted global functional networks.
-
-This correspondence makes it possible to inject established knowledge about the 
-networks and regions into a hierarchy: A brain contains a certain number of
-networks, which in turn consist of the atlas modules as subregions.
-We can use this hierarchy to create a structural prior of expected weight
-maps for classifiers.
-
-The hierarchical group lasso as introduced by \cite{jenatton2011} lends
-itself perfectly to represent this structure. It is based on the group lasso
-\cite{group_lasso} but permits groups to contain each other in a tree
-structure. The first level of the tree are the network groups containing all
-the voxels of the modules associated to them. Then each network contains as
-as subgroups the modules associated with it, grouping the voxels of each of
-these regions together.
-As with the group lasso, it is possible to associate an individual penalty
-to each group. In trading off the penalties on the network level against the
-penalties of the region level, we can create different regimes of 
-estimation: 
+\cite{anderson2013}.
+As a well-established method for network estimation
+\cite{beckmann2005},
+ICA yields continuous brain maps with
+weights for each voxel. The region nodes of ICA
+networks are spatially disjoint and in
+correspondence with boundaries of brain atlases.
+Consequently,
+each region from a brain atlas can be uniquely associate to one
+the extracted ICA networks.
+%
+The network regions are spatially compact structures of
+neighboring voxels in a neural activity map.
+The brain's grey matter can be segregated into functional regions to
+compile brain atlases
+using microscopical or algorithmic investigations
+\cite{cbp2015review}.
+%
+This brain-network correspondence
+allows constructing a hierarchy of global ICA networks with their
+assigned local regions.
+This network-region tree is used as a structural prior
+of expected weight distributions
+for supervised learning algorithms.
+
+The hierarchical group lasso introduced by \cite{jenatton2011multi} lends
+itself perfectly to represent this tree structure.
+It extends the group lasso
+\cite{yuan2006model} to permit variable groups to contain each other
+in a nested tree structure.
+The first hierarchical level of that tree are
+the network groups that contain all
+the voxels of the modules associated to them.
+Each network node, in turn, descends into a set of
+brain regions associated with spatially neighboring voxel groups.
+%
+As an important consequence,
+a child node enters the set of relevant voxel variables only
+if its parent node has been selected.
+Conversely,
+if a parent node is deselected,
+also the voxel variables of all child nodes are deselected.
+%
+Moreover,
+the coefficient of the region and network groups can
+be weighed individually.
+Trading off the voxel penalties of the network level against the
+voxel penalties of the region level,
+we can design different estimation regimes.
 %
@@
 forced without the bias of the network maps.
-%
 Conversely, setting low penalties on the region maps makes it possible for
@@
 %
-Taken together and varied smoothly, we can evaluate a tradeoff between the
-relevance of modular regions and functionally integrated networks in 
-statistical estimation of brain activity.
-
-%% we need to inject domain knowledge into
-%% statistical estimations to harness the curse of dimensionality.
-%% two neurobiological design principles 
-%% 
-%% imposing parsimony
-%% integrative processes
-%% 
-%%  This L1/L2 norm for group lasso has been extended to a more general setting to
-%% 
-%% designed groups
-%%  the child nodes enter the set of relevant inputs only if its parent node does. 
-%%  
-%% should be able to estimate voxel level
-%% while taking into account known supravoxel structure.
-%% is instrumental in
-%% Developmentally, such large-scale networks emerge during late
-%% fetal growth (Doria et al., 2010), before cognitive capacities mature
-%% in childhood. 
-%% 
-%% In adults, nodes of a same cohesive network have more
-%% similar functional profiles than nodes from different networks
-%% (Anderson et al., 2013).
-%% 
-%% data exhibit natural correlations between neighboring voxels forming clusters
-%% 
-%% representing some phenomenon with as few variables as possible
-%% 
-%% neurobiologically motivated restrictions to complexity circumvented
-%% the curse of dimensionality
-%% three-dimensional spatial arrangement that respects
-%% the functional anatomy of the brain
-%% not ignore the spatial configuration
-%% 
-%% incorporate rich prior knowledge
-%% 
-%% If meaningful structures exist,
-%% we show that one can take advantage of such structures
-%% 
-%% Statistically,
-%% l1 and l2 are local sparsity priors
-%% -> resulting sparsity does yield structure
-%% we want to priviledge representations with structure
-%% 
-%% 
-%% => 
+This region-network tradeoff allows inspecting the relative contributions
+of the region and network levels
+of the hierarchical prior.
+
 %%  a biologically and statistically desirable bias
@@
 \[\Omega(w) = \alpha\sum_{h\in\mathcal H}\eta_h\|w_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|w_g\|_2.\]
-According to \cite{Zhou_or_who_was_that} we set \(\eta_g = 1/\sqrt{|g|}\) to
+According to \cite{yuan2006model} we set \(\eta_g = 1/\sqrt{|g|}\) to
 account for varying group size. The hierarchy-level-specific factors 
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_prior.pdf}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_prior_colin.pdf}
 \end{centering}
@@
 (\textit{lower left})
-imposed region compartments, but na\"ive to network structure.
+imposed region compartments, but naive to network structure.
 Structured trace-norm penalization (\textit{lower right})
 imposed low-rank structure
-with sparsity of network patterns, but na\"ive to region structure.
+with sparsity of network patterns, but naive to region structure.
 Structured $\ell_1/\ell_2$-block-norm with a hierarchy of
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/dataratio.pdf}
+\includegraphics[width=1.00\textwidth]{figures/dataratio_trans.pdf}
 \end{centering}
 \vspace{-0.6cm}
-\caption{\textbf{Na\"ive versus informed sparse model selection
+\caption{\textbf{Naive versus informed sparse model selection
 across training set sizes.}
@@
 
-\paragraph{Sample complexity of na\"ive versus informed sparse model selection.}
+\paragraph{Sample complexity of naive versus informed sparse model selection.}
 Subsequently, the sample complexity of
@@
 support recovery than
-neurobiology-na\"ive $\ell_1$-constrained logistic regression
+neurobiology-naive $\ell_1$-constrained logistic regression
 in the data-scarce and data-rich scenarios.
@@
 profited more from the increased information quantities than
-neurobiologically na\"ive logistic regression.
+neurobiologically naive logistic regression.
 That is, the region-network priors actually further enhance the similarity
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio.pdf}
+\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio_colin.pdf}
 \end{centering}

### 2016-02-02 paper/icml2016/example_paper.tex
icml template

--- 2016-02-02 paper/paper.tex
@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e,times}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Use the following line _only_ if you're still using LaTeX 2.09.
+%\documentstyle[icml2016,epsf,natbib]{article}
+% If you rely on Latex2e packages, like most moden people use this:
+\documentclass{article}
+
+% use Times
+\usepackage{times}
+% For figures
+\usepackage{graphicx} % more modern
+%\usepackage{epsfig} % less modern
+\usepackage{subfigure}
+
+% For citations
+\usepackage{natbib}
+
+% For algorithms
+\usepackage{algorithm}
+\usepackage{algorithmic}
+
+% As of 2011, we use the hyperref package to produce hyperlinks in the
+% resulting PDF.  If this breaks your system, please commend out the
+% following usepackage line and replace \usepackage{icml2016} with
+% \usepackage[nohyperref]{icml2016} above.
 \usepackage{hyperref}
-\usepackage{url}
+
+% Packages hyperref and algorithmic misbehave sometimes.  We can fix
+% this with the following command.
+\newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+% Employ the following version of the ``usepackage'' statement for
+% submitting the draft version of the paper for review.  This will set
+% the note in the first column to ``Under review.  Do not distribute.''
+\usepackage{icml2016}
+
+% Employ this version of the ``usepackage'' statement after the paper has
+% been accepted, when creating the final version.  This will set the
+% note in the first column to ``Proceedings of the...''
+%\usepackage[accepted]{icml2016}
+
+\usepackage{multirow}
 \usepackage{amsmath,amsfonts,amsthm}
-\usepackage{bbm}
-\usepackage{algorithm,algorithmic}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{bbm}
-\usepackage[titletoc]{appendix}
-\usepackage{wrapfig}
-\usepackage{afterpage}
 \usepackage{amssymb}
-\usepackage{booktabs}
-\usepackage{ulem}
-\usepackage{multirow}
-\usepackage{comment}
-
-\def\B#1{\bm{#1}}
-%\def\B#1{\mathbf{#1}}
-\def\trans{\mathsf{T}}
+
 \DeclareMathOperator*{\argmin}{arg\,min}
-
-%\renewcommand{\labelitemi}{--}
-
-\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{remark}{Remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{Region-network hierarchical sparsity priors for\\
-high-dimensional inference in brain imaging}
-
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
-\DeclareMathOperator{\proj}{proj}
-\DeclareMathOperator{\softmax}{softmax}
 \DeclareMathOperator{\prox}{prox}
-\DeclareMathOperator{\Prox}{Prox}
-\DeclareMathOperator{\im}{im}
-
-% macros from michael's .tex
-\DeclareMathOperator{\dist}{dist} % The distance.
-%\DeclareMathOperator{\argmin}{argmin}
-\DeclareMathOperator{\argmax}{argmax}
 \DeclareMathOperator{\Id}{Id}
-\DeclareMathOperator{\abs}{abs}
+
 \newcommand{\R}{\mathbb{R}}
-\newcommand{\N}{\mathbb{N}}
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{prop}[thm]{Proposition}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{cor}[thm]{Corollary}
-
-\newcommand{\suggestadd}[1]{{\color{blue} #1}}
-\newcommand{\suggestremove}[1]{{\color{red} \sout{#1}}}
-
-% \nipsfinalcopy % Uncomment for camera-ready version
-\nipsfinaltrue
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% The \icmltitle you define below is probably too long as a header.
+% Therefore, a short form for the running title is supplied here:
+\icmltitlerunning{Submission and Formatting Instructions for ICML 2016}
 
@@
 
-\author{Danilo Bzdok, Michael Eickenberg,
-  Ga\"el Varoquaux, Bertrand Thirion\\
-  Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
-  INRIA, Parietal team, Saclay, France\\
-  CEA, Neurospin, Gif-sur-Yvette, France\\
-  firstname.lastname@inria.fr}
-
-\maketitle
+\twocolumn[
+\icmltitle{Submission and Formatting Instructions for \\ 
+           International Conference on Machine Learning (ICML 2016)}
+
+% It is OKAY to include author information, even for blind
+% submissions: the style file will automatically remove it for you
+% unless you've provided the [accepted] option to the icml2016
+% package.
+\icmlauthor{Your Name}{email@yourdomain.edu}
+\icmladdress{Your Fantastic Institute,
+            314159 Pi St., Palo Alto, CA 94306 USA}
+\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
+\icmladdress{Their Fantastic Institute,
+            27182 Exp St., Toronto, ON M6H 2T1 CANADA}
+
+% You may provide any keywords that you 
+% find helpful for describing your paper; these are used to populate 
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{boring formatting information, machine learning, ICML}
+
+\vskip 0.3in
+]
 
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_prior_colin.pdf}
+\includegraphics[width=1.00\textwidth]{../figures/reg_net_prior_colin.pdf}
 \end{centering}
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/sparsities.pdf}
+\includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
 \end{centering}
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/dataratio_trans.pdf}
+\includegraphics[width=1.00\textwidth]{../figures/dataratio_trans.pdf}
 \end{centering}
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{figures/reg_net_ratio_colin.pdf}
+\includegraphics[width=1.00\textwidth]{../figures/reg_net_ratio_colin.pdf}
 \end{centering}
@@
 \end{document}
+
+% This document was modified from the file originally made available by
+% Pat Langley and Andrea Danyluk for ICML-2K. This version was
+% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
+% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
+% slightly modified from the 2009 version by Kiri Wagstaff and 
+% Sam Roweis's 2008 version, which is slightly modified from 
+% Prasad Tadepalli's 2007 version which is a lightly 
+% changed version of the previous year's version by Andrew Moore, 
+% which was in turn edited from those of Kristian Kersting and 
+% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2016-02-03 paper/icml2016/example_paper.tex
figure* environments
ICMLize the paper

@@
 % the note in the first column to ``Under review.  Do not distribute.''
-\usepackage{icml2016}
+% \usepackage{icml2016}
 
@@
 % note in the first column to ``Proceedings of the...''
-%\usepackage[accepted]{icml2016}
+\usepackage[accepted]{icml2016}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Submission and Formatting Instructions for ICML 2016}
+\icmltitlerunning{Informing High-Dimensional Inference in Neuroimaging}
 
@@
 \twocolumn[
-\icmltitle{Submission and Formatting Instructions for \\ 
-           International Conference on Machine Learning (ICML 2016)}
+\icmltitle{Region-Network Hierarchical Sparsity Priors for\\
+High-Dimensional Inference in Brain Imaging}
 
@@
 % package.
-\icmlauthor{Your Name}{email@yourdomain.edu}
-\icmladdress{Your Fantastic Institute,
-            314159 Pi St., Palo Alto, CA 94306 USA}
-\icmlauthor{Your CoAuthor's Name}{email@coauthordomain.edu}
-\icmladdress{Their Fantastic Institute,
-            27182 Exp St., Toronto, ON M6H 2T1 CANADA}
+\icmlauthor{Danilo Bzdok}{danilo.bzdok@inria.fr}
+\icmladdress{Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
+  Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
+\icmlauthor{Michael Eickenberg}{Michael.Eickenberg@inria.fr}
+\icmladdress{Department d'Informatique, Ecole Normale Superieure, Paris}
+\icmlauthor{Ga\"el Varoquaux}{gael.varoquaux@inria.fr}
+\icmlauthor{Bertrand Thirion}{bertrand.thirion@inria.fr}
+\icmladdress{Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
 
@@
 % the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{boring formatting information, machine learning, ICML}
+\icmlkeywords{Sparsity-inducing norms, hierarchical tree sparsity,
+numerical optimization,
+systems neuroscience,
+functional specialization, functional integration}
 
@@
 by hierarchical tree sparsity.
-
-\textbf{\\keywords}:
-Sparsity-inducing norms, hierarchical tree sparsity,
-numerical optimization,
-systems neuroscience,
-functional specialization, functional integration
 
@@
 
-\begin{table}[h]
+\begin{table*}[h]
   \resizebox{0.98\textwidth}{!}{%
@@
 \label{table_tasks}
-\end{table}
+\end{table*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{centering}
@@
 \label{fig_priors}
-\end{figure}
-
-\begin{figure}
+\end{figure*}
+
+\begin{figure*}
 \begin{centering}
@@
 \label{fig_sparsities}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{../figures/dataratio_trans.pdf}
-\end{centering}
-\vspace{-0.6cm}
+\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
+%\vspace{-0.6cm}
 \caption{\textbf{Naive versus informed sparse model selection
@@
 \label{fig_dataratio}
-\end{figure}
+\end{centering}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{../figures/reg_net_ratio_colin.pdf}
-\end{centering}
-\vspace{-0.6cm}
+\includegraphics[width=0.80\textwidth]{../figures/reg_net_ratio_colin.pdf}
+%\vspace{-0.6cm}
 \caption{\textbf{Support recovery as a function of
@@
 \label{fig_regnetratio}
-\end{figure}
+\end{centering}
+\end{figure*}
 
@@
 % \bibliographystyle{plainnat}
-\bibliographystyle{splncs03}
+\bibliographystyle{icml2016}
 \bibliography{paper_refs}
+% \bibliography{paper_refs}
 

### 2016-02-03 paper/icml2016/build_icml.sh

@@ -1,0 +1,29 @@
+#!/usr/bin/env bash
+
+# rm -rf $(biber --cache)
+rm *.aux
+rm *.bcf
+rm *.bbl
+rm *.blg
+rm *.ist
+rm *.alg
+rm *.acr
+rm *.acn
+rm *.glsdefs
+rm *.out
+rm *.lot
+rm *.log
+rm *.lof
+rm *.toc
+rm *.run.xml
+rm *.synctex.gz
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 example_paper.tex
+
+bibtex example_paper
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 example_paper
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 example_paper
+# makeindex -s paper.idx -t paper.glsdef -o paper.acr paper.acn
+makeglossaries example_paper
+pdflatex -interaction=nonstopmodxe -file-line-error-style -synctex=1 example_paper
+
+open example_paper.pdf

### 2016-02-03 srne_plot_roc.py

@@ -1,0 +1,80 @@
+import struct_estimator_dataratio_zerobrainlevel_weighted
+
+import os.path as op
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn import svm, datasets
+from sklearn.metrics import roc_curve, auc
+from sklearn.cross_validation import train_test_split
+from sklearn.preprocessing import label_binarize
+from sklearn.multiclass import OneVsRestClassifier
+from scipy import interp
+import joblib
+
+n_classes = 18
+
+READ_DIR = 'srne_benchmark_dataratioFIXED100_zerobrainlevel_weighted'
+
+REGS = ['tree-l2', 'l1', 'trace-norm',
+        'sparse-group-lasso-l2', 'group-lasso-l2']
+
+auc_mat = np.zeros((len(REGS), n_classes))
+
+for i_r, r in enumerate(REGS):
+    print('-' * 80)
+    print(r)
+    dump_path = op.join(READ_DIR, '%s_dataratio100_maxit100' % r)
+    clf = joblib.load(dump_path)
+
+    print(len(clf.best_estimator_.estimators_))
+    print('Mean Accuracy: %.3f' % np.mean(clf.test_acc))
+    print('Mean Precision: %.3f' % np.mean(clf.test_prfs[0]))
+    print('Mean Recall: %.3f' % np.mean(clf.test_prfs[1]))
+
+    coef_ = np.array([est.W_.ravel() for
+                      est in clf.best_estimator_.estimators_]).T
+
+    y_score = np.dot(X_test, coef_)
+
+    # Compute ROC curve and ROC area for each class
+
+    Y_test_bin = label_binarize(Y_test, classes=np.arange(n_classes))
+
+    fpr = dict()
+    tpr = dict()
+    roc_auc = dict()
+    for i in range(n_classes):
+        fpr[i], tpr[i], _ = roc_curve(Y_test_bin[:, i], y_score[:, i])
+        cur_auc = auc(fpr[i], tpr[i])
+        roc_auc[i] = cur_auc
+        auc_mat[i_r, i] = cur_auc
+
+    # Compute micro-average ROC curve and ROC area
+    fpr["micro"], tpr["micro"], _ = roc_curve(
+        Y_test_bin.ravel(), y_score.ravel())
+    roc_auc["micro"] = auc(fpr["micro"], tpr["micro"])
+
+    plt.figure()
[…]

### 2016-02-03 paper/icml2016/example_paper.tex
ICMLize II

@@
 High-Dimensional Inference in Brain Imaging}
+% \icmltitle{Region-Network Hierarchical Sparsity Priors for\\
+% High-Dimensional Inference in Brain Imaging}
 
@@
 \paragraph{Implementation.}
-The analyses were performed in Python.
-We used \textit{nilearn} to handle
-the large quantities of neuroimaging data 
-\cite{abrah14}
+All analyses were performed in Python.
+We used \textit{nilearn} to process and resphape
+the extensive neuroimaging data 
+\cite{abrah14},
+\textit{scikit learn} to design machine-learning
+data processing pipelines
+\cite{pedr11},
 and
-\textit{Theano} for automatic, numerically stable
-differentiation of symbolic computation graphs
-\cite{bastien2012theano, bergstra2010theano}.
+\textit{SPAMs} for numerically optimized
+implementations of the sparse estimators
+(\url{http://spams-devel.gforge.inria.fr/}).
 All Python scripts that generated the results are
 accessible online for reproducibility and reuse
-% (\url{http://github.com/anonymous/anonymous}).
-(\url{http://github.com/banilo/nips2015}).
-
-all algorithm from a same software library -> SPAMs
+(\url{http://github.com/anonymous/anonymous}).
+% (\url{http://github.com/banilo/nips2015}).
 
@@
 were selected that are known to elicit reliable neural activity
-across participants (Table \ref{table_tasks}).
+across participants.
+% across participants (Table \ref{table_tasks}).
 In sum, the HCP task data incorporated 8650 first-level activity maps
@@
 
-\begin{table*}[h]
-  \resizebox{0.98\textwidth}{!}{%
-  \begin{tabular}{l|l|l}
-    \hline
-  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
-  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
-  2 Punish             &                                       &                                                                                   \\ \hline
-  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
-  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
-  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
-  6 Theory of mind     &                                       &                                                                                   \\ \hline
-  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
-  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
-  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
-  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
-  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
-  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
-  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
-  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
-  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
-  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
-  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
-  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
-  \end{tabular}
-}
-\vspace{-0.2cm}
-\caption{\textbf{Description of psychological tasks to predict.}}
-\label{table_tasks}
-\end{table*}
-
-These labeled data were complemented by unlabeled activity maps
-from HCP acquisitions of unconstrained resting-state activity
-\cite{smith2013resting}.
-These reflect brain activity in the absence of controlled thought.
-In sum, the HCP rest data concatenated
-8000 unlabeled, noise-cleaned rest maps with
-40 brain maps from each of 200 randomly selected participants.
-
-We were further interested in the utility of the
-optimized low-rank projection
-in one task dataset for dimensionality reduction in another task dataset.
-To this end, the HCP-derived network decompositions were used as preliminary
-step in the classification problem of another large sample.
-The ARCHI dataset \cite{pinel07} provides activity maps from
-diverse experimental tasks, including auditory and visual perception, motor action,
-reading, language comprehension and mental calculation.
-Analogous to HCP data, the second task dataset thus incorporated 1404
-labeled, grey-matter masked, and z-scored activity maps
-from 18 diverse tasks acquired in 78 participants.
-
-sparse statistical models have only few nonzero parameters
+% \begin{table*}[h]
+%   \resizebox{0.98\textwidth}{!}{%
+%   \begin{tabular}{l|l|l}
+%     \hline
+%   {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
+%   1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
+%   2 Punish             &                                       &                                                                                   \\ \hline
+%   3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
+%   4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
+%   5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
+%   6 Theory of mind     &                                       &                                                                                   \\ \hline
+%   7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
+%   8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
+%   9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
+%   10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
+%   11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
+%   12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
+%   13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
+%   14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
+%   15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
+%   16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
+%   17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
+%   18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
+%   \end{tabular}
+% }
+% \vspace{-0.2cm}
+% \caption{\textbf{Description of psychological tasks to predict.}}
+% \label{table_tasks}
+% \end{table*}
 
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{../figures/reg_net_prior_colin.pdf}
+\includegraphics[width=0.8\textwidth]{../figures/reg_net_prior_colin.pdf}
 \end{centering}
-\vspace{-0.6cm}
+\vspace{-0.2cm}
 \caption{\textbf{Building blocks of the region-network tree.}
@@
 \begin{centering}
-\includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
+% \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
+\includegraphics[width=0.55\textwidth]{../figures/ROC_ALL_perclass.png}
 \end{centering}
-\vspace{-0.6cm}
+\vspace{-0.4cm}
 \caption{\textbf{Model performance across sparsity priors.}
@@
 in classifying neural activity from 18 psychological tasks.
-The class-wise precision and recall metrics
-were obtained on the same test set.
-%
-Unstructured $\ell_1$-penalized logistic regression (\textit{upper left})
+The class-wise area under the curve (AUC)
+is obtained on the same test set.
+%
+\textit{Hierarchical Tree Sparsity}: Structured
+$\ell_1/\ell_2$-block-norm with a hierarchy of
+both region and network priors
+exhibited the best out-of-sample performance.
+\textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
 imposed a minimum of relevant brain voxels without
 assuming special structure.
-Structured $\ell_1/\ell_2$-block norm with additional $\ell_1$ term
-(\textit{lower left})
-imposed region compartments, but naive to network structure.
-Structured trace-norm penalization (\textit{lower right})
+\textit{Elastic-Net}: Unstructured logistic regression
+with interpolation between $\ell_1$- and $\ell_2$-norm 
+imposed an equilibrium between sparsity and model fit.
+\textit{Trace-norm}: Structured trace-norm penalization
 imposed low-rank structure
 with sparsity of network patterns, but naive to region structure.
-Structured $\ell_1/\ell_2$-block-norm with a hierarchy of
-both region and network priors (\textit{upper right})
-exhibited the best out-of-sample performance.
+\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
+norm with additional $\ell_1$ term
+imposed region compartments, but naive to network structure.
 %
@@
 \begin{centering}
-\includegraphics[width=0.80\textwidth]{../figures/reg_net_ratio_colin.pdf}
+\includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin.pdf}
 %\vspace{-0.6cm}
@@
 
-\paragraph{Support recovery as a function of region and network emphasis.}
+\paragraph{Support recovery as a function of region-network emphasis.}
 Finally, the relative importance of the
@@
 and multiplying
-$\frac{1}{3}$ to $\eta_g$ of all network group penalties.
-The data splitting cross-validation scheme was identical to the
-above modelling experiments.
+$\frac{1}{3}$ to $\eta_g$ of all network group penalties
+(Table \ref{table_reg_net_ratio}).
+
+\begin{table*}[]
+\centering
+\caption{18-class out-of-sample performance by region-network emphasis}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
+\textbf{Reg-Net Ratio} & 500 & 100  & 50   & 10   & 5    & 2    & 1    & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ & $\frac{1}{250}$ & $\frac{1}{500}$ & $\frac{1}{1000}$ \\ \hline
+\textbf{Accuracy {[}\%{]}}      & 3.8          & 41.7 & 63.7 & 89.9 & 89.9 & 88.5 & 87.9 & 87.9 & 87.9 & 87.8 & 88.6 & 87.8  & 85.6  & 67.2  & 39,3  
+\end{tabular}
+\label{table_reg_net_ratio}
+\end{table*}
 
@@
 
-\section{Discussion}
+\section{Conclusion}
 Relevant structure in neuroimaging data has long been investigated
@@
 \bibliographystyle{icml2016}
-\bibliography{paper_refs}
+\bibliography{../paper_refs}
 % \bibliography{paper_refs}

### 2016-02-03 srne_plot_roc.py

@@ -15,8 +15,12 @@ n_classes = 18
 
 READ_DIR = 'srne_benchmark_dataratioFIXED100_zerobrainlevel_weighted'
 
-REGS = ['tree-l2', 'l1', 'trace-norm',
+REGS = ['tree-l2', 'l1',
+        'elastic-net', 'trace-norm', 
         'sparse-group-lasso-l2', 'group-lasso-l2']
+REGS_STR = ['Hierarchical Tree Sparsity', 'Lasso',
+            'Elastic-Net', 'Trace-Norm', 
+            'Sparse Group Lasso', 'Group Lasso']
 
 auc_mat = np.zeros((len(REGS), n_classes))
 
@@ -67,7 +71,7 @@ for i_r, r in enumerate(REGS):
     plt.show()
     plt.savefig(dump_path + '_ROC.png')
 
-# summary plot across classifiers and classes
+# summary AUC plot: per classifier
 plt.figure()
 for i_c in range(n_classes):
     plt.plot(np.arange(len(REGS)), auc_mat[:, i_c] * 100, linewidth=2)
@@ -77,4 +81,21 @@ plt.ylabel('AUC [%]')
 plt.title('Comparing classifications of 18 tasks')
 plt.tight_layout()
 plt.show()
-plt.savefig(op.join(READ_DIR, 'ROC_ALL.png'))
+plt.savefig(op.join(READ_DIR, 'ROC_ALL_perclf.png'))
+
+# summary AUC plot: per task
+plt.figure()
+for i_r in range(len(REGS)):
+    plt.plot(np.arange(n_classes),
+             auc_mat[i_r, :] * 100,
+             label=REGS_STR[i_r],
+             linewidth=2)
+plt.ylim([35., 102.])
+plt.xticks(np.arange(n_classes), np.arange(n_classes) + 1)
+plt.ylabel('AUC [%]')
+plt.title('Comparing classifications of 18 classes')
+plt.xlabel('psychological task')
+plt.tight_layout()
+plt.legend(loc="middle right")
+plt.show()
+plt.savefig(op.join(READ_DIR, 'ROC_ALL_perclass.png'))

### 2016-02-03 paper/icml2016/example_paper.tex
interm

@@
 %
-Region-network hierarchical priors for supervised classification
-of 18 psychological tasks
+Region-network hierarchical priors for classifying
+18 psychological tasks
 from a reference dataset are
-shown to outperform naive $\ell_1$-norm and
+shown to outperform naive $\ell_1$-norm, elastic-net, and
 trace-norm penalization, as well as neurobiologically
@@
 total observations per data sample.
-This high-dimensional scenario challenges various statistical methods from
+This \(n << p\) scenario challenges various statistical methods from
 classical statistics.
@@
 Conversely, functional integration emphasizes that brain function
-is enabled by complex connections between these
+is enabled by a complex interplay between these
 distinct brain regions \cite{sporns14nn}.
@@
 infrastructure
-and its unique global connectivity profile are thought to go hand-in-hand
+and unique global connectivity profiles are thought to go hand-in-hand
 to realize brain function.
@@
 probably no existing brain analysis method acknowledges that
-both functional organizations are inextricably involved
+both functional design principles are inextricably involved
 in the realization of mental operations.
 
-Functional specialization has been
-explored and interpreted based on many different research methods.
+Functional specialization has long been
+explored and interpreted based on different research methods.
 %
@@
 revealed the
-specialization in the occipital visual cortex into V1, V2, V3, V3A/B, and V4
+segregation of the occipital visual cortex into V1, V2, V3, V3A/B, and V4
+regions
 \cite{hubel1962receptive, zeki1978functional}.
@@
 %
-As a common point of all these methods,
+As a common point of this second set of methods,
 interpretation of findings naturally embraces
@@
 % study
-Building on these two major interpretational traditions in systems neuroscience,
+Building on these two major interpretational traditions in neuroscience,
 the present study proposes to incorporate
@@
 %
-Learning techniques
+Learning algorithms
 exploiting structured sparsity 
-have recently made much progress in various application domains
+have recently made much progress in various domains
 from processing auditory signals \cite{daudet2004sparse},
@@
 %
-The recently suggested hierarchical tree penalties for imaging neuroscience
+The hierarchical tree penalties recently suggested for imaging neuroscience
 \cite{jenatton2011multi} will be extended
@@
 %
-Based on the largest neuroimaging repository,
+Based on the largest neuroimaging repository (Human Connectome Project [HCP]),
 we demonstrated that domain-informed supervised models
@@
 These allow acknowledging the interplay between local specialization and 
-global connectivity during defined psychological tasks.
+global connectivity when discriminating defined psychological tasks.
 %
@@
 linear model based on dot products with the voxel values.
-
-Yet, the abundant structure can be exploited by
-injecting domain-knowledge priors into the statistical estimation process.
-Here we are 
-interested in well-established neurobiological knowledge about
-brain regions of functional specialization and spatiotemporal interactions
-between these.
+However, the effective dimensionality of neuroimaging data is
+known to be low \cite{bzdok2015semi}.
+This will be exploited by
+injecting brain regions of functional specialization
+and spatiotemporal interactions into the statistical estimation process.
 %

### 2016-02-03 paper/icml2016/example_paper.tex
add Bertrands comments

@@
 We capitalize on hierarchical group lasso as recently introduced
-\cite{jenatton2011structured} to create a set of convex penalty terms.
+\cite{jenatton2011multi} to create a set of convex penalty terms.
 These allow acknowledging the interplay between local specialization and 
-global connectivity when discriminating defined psychological tasks.
+global connectivity when discriminating defined psychological tasks
+from brain activity.
+% Bertrand: univariate-multivariate is orthogonal to the
+% current study -> make clear why we opted for multivariate
+% rather than univariate which might even have been simpler
+Rather than inferring brain activity from psychological tasks
+in a univariate setting,
+this study infers psychological tasks from brain activity
+in a multivariate setting to allow for
+prediction in unseen neuroimaging data.
 %
@@
 3D brain maps obtained by neuroimaging
-techniques are high-dimensional but also highly structured.
-While its explicit dimensionality, the number of brain voxels,
-typically exceeds 100,000 variables, the number
+techniques are high-dimensional but, luckily,
+their signal is highly structured.
+Its explicit dimensionality, the number of brain voxels,
+typically exceeds 100,000 variables, while the number
 of samples rarely exceeds few hundreds.
@@
 linear model based on dot products with the voxel values.
-However, the effective dimensionality of neuroimaging data is
-known to be low \cite{bzdok2015semi}.
-This will be exploited by
-injecting brain regions of functional specialization
-and spatiotemporal interactions into the statistical estimation process.
-%
-These large-scale brain networks emerge in human individuals around birth
+However, the effective dimensionality of functional neuroimaging data has been
+shown to be much lower \cite{bzdok2015semi}.
+Two types of low-dimensional neighborhoods will be exploited by
+injecting established knowledge of regional specialization
+(i.e., region priors)
+and spatiotemporal interactions
+(i.e., network priors)
+into the statistical estimation process.
+
+Large-scale brain networks emerge in human individuals around birth
 \cite{doria2010}, before mental capacities mature in childhood. 
 In adults,
-the sets of regions that compose the spatiotemporally cohesive network have more
+the sets of regions that compose
+a given spatiotemporally cohesive network are known to have more
 similar functional profiles than nodes from different networks
@@
 weights for each voxel. The region nodes of ICA
-networks are spatially disjoint and in
-correspondence with boundaries of brain atlases.
+networks are spatially disjoint sets of voxel groups that
+agree with boundaries of brain atlases.
+Such brain atlases can be obtained by segregating
+the brain's grey matter into spatially compact voxel groups
+using clustering algorithmisms
+\cite{cbp2015review}.
 Consequently,
@@
 %
-The network regions are spatially compact structures of
-neighboring voxels in a neural activity map.
-The brain's grey matter can be segregated into functional regions to
-compile brain atlases
-using microscopical or algorithmic investigations
-\cite{cbp2015review}.
-%
-This brain-network correspondence
-allows constructing a hierarchy of global ICA networks with their
-assigned local regions.
-This network-region tree is used as a structural prior
+In the present work previously published network definitions
+obtained using ICA \cite{smith2009}
+and
+previously published region definitions obtained from
+spatially constrained ward clustering \cite{crad12}
+allow constructing a hierarchy of global ICA networks with their
+assigned local cluster regions.
+The ensuing network-region tree is used as a structural prior
 of expected weight distributions
-for supervised learning algorithms.
-
-The hierarchical group lasso introduced by \cite{jenatton2011multi} lends
-itself perfectly to represent this tree structure.
+during supervised model fitting.
+
+This tree structure can be seamlessly plugged into
+a recently introduced hierarchical sparsity estimator
+\cite{jenatton2011multi}.
 It extends the group lasso
-\cite{yuan2006model} to permit variable groups to contain each other
+\cite{yuan2006model}
+by permitting variable groups that contain each other
 in a nested tree structure.
@@
 the network groups that contain all
-the voxels of the modules associated to them.
-Each network node, in turn, descends into a set of
-brain regions associated with spatially neighboring voxel groups.
-%
-As an important consequence,
+the voxels of the brain regions associated to them.
+Each network node, in turn, descends into a second hierarchical level of
+brain regions of spatially neighboring voxel groups.
+%
+As a consequence of such a region-network sparsity tree,
 a child node enters the set of relevant voxel variables only
-if its parent node has been selected.
+if its parent node has been selected
+\cite{bach2012optimization}.
 Conversely,
@@
 Moreover,
-the coefficient of the region and network groups can
+the coefficient of all region groups and all network groups can
 be weighed individually.
@@
 higher penalties on region groups, selection of relevant region groups is
-forced without the bias of the network maps.
-Conversely, setting low penalties on the region maps makes it possible for
+forced without negligable bias of the network definitions.
+Conversely, setting low penalties on the region definitions
+makes it possible for
 all voxels to be active. Selecting higher penalties on the networks then
@@
 of the region and network levels
-of the hierarchical prior.
-
-%%  a biologically and statistically desirable bias
+of the hierarchical tree prior.
 
@@
 better support recovery with weight maps already much closer
-to the class averages.
+to the class averages
+\cite{varoquaux2012small}.
 In the case of scarce training data, which is typical for the brain imaging domain,
@@
 \cite{sporns14nn}.
+Both organizational principles are however inextricable because
+a specialized brain region communicates input and output with other regions
+and a brain network subserves complex function by
+orchestrating its region nodes.
+This suggests hierarchical statistical models
+as an underexploited opportunity for imaging imaging analysis.
 %
@@
 %
-Domain-informed hierarchical structured sparsity is shown to enhance
+This statistically and neurobiologically desirable bias
+is shown to enhance
 both model interpretability and generalization performance,

### 2016-02-04 paper/icml2016/example_paper.tex
email
sample complexity: add more results

@@
 \paragraph{Hyperparameter optimization.}
-{\color{red} NEEDS EMBELLISHING}
-We perform nested cross-validation to obtain optimal hyperparameters. 
-In order to analyse their effect in detail, we split our analysis into two 
-parts.
-\begin{enumerate}
-\item In the first part, we optimize the trade-off between the different hierarchy levels as well as the global penalty level for maximal prediction.
-\item in the second part, we select the optimal global penalty level for 
-given trade-off ratios.
-\end{enumerate}
-
-\paragraph{Control methods}
-{\color{red} needs embellishing}
-We evaluate our tree structure against other commonly used structured sparse
-penalties.
+The stratified and shuffled training data were submitted
+to a nested cross-validation scheme
+for model selection and model assessment.
+In the inner CV layer, the logistic regression estimators
+have been trained in a one-versus-rest design that
+distinguishes each class from
+the respective 17 other classes
+(number of maximal iterations=$100$, tolerance=$0.001$).
+In the outer CV layer, grid search
+selected among candidates for the respective $\lambda$ parameter
+by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
+Importantly, the thus selected sparse logistic regression classifier was
+evaluated on an identical test set in all settings.
 
@@
 %
-The stratified and shuffled training data were submitted
-to a nested cross-validation scheme
-for model selection and model assessment.
-In the inner CV layer, the logistic regression estimators
-have been trained in a one-versus-rest design that
-distinguishes each class from
-the respective 17 other classes
-(number of maximal iterations=$100$, tolerance=$0.001$).
-In the outer CV layer, grid search
-selected among candidates for the respective $\lambda$ parameter
-by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
-Importantly, the thus selected sparse logistic regression classifier was
-evaluated on an identical test set in all settings.
+% The stratified and shuffled training data were submitted
+% to a nested cross-validation scheme
+% for model selection and model assessment.
+% In the inner CV layer, the logistic regression estimators
+% have been trained in a one-versus-rest design that
+% distinguishes each class from
+% the respective 17 other classes
+% (number of maximal iterations=$100$, tolerance=$0.001$).
+% In the outer CV layer, grid search
+% selected among candidates for the respective $\lambda$ parameter
+% by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
+% Importantly, the thus selected sparse logistic regression classifier was
+% evaluated on an identical test set in all settings.
 
@@
 training set at different subsampling fractions:
-20\% (1516 maps),
+20\% (1516 neural activity maps),
 40\% (3033 maps),
@@
 100\% (7584 maps).
-%
-The stratified and shuffled training data were submitted
-to a nested cross-validation scheme
-for model selection and model assessment.
-In the inner CV layer, the logistic regression estimators
-have been trained in a one-versus-rest design that
-distinguishes each class from
-the respective 17 other classes
-(number of maximal iterations=$100$, tolerance=$0.001$).
-In the outer CV layer, grid search
-selected among candidates for the respective $\lambda$ parameter
-by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
-Importantly, the thus selected sparse logistic regression classifier was
-evaluated on an identical test set in all settings.
+
+% results: accuracy
+Regarding classification performances on the always same test set,
+$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
+achieved
+83.6\% versus 88.7\% (20\% of training data),
+85.0\% versus 89.2\% (40\%),
+86.8\% versus 89.8\% (60\%),
+88.9\% versus 90.3\% (80\%),
+88.6\% versus 89.7\% (100\%) accuracy.
+% results: sparsity
+Regarding the model sparsity,
+the model weights $w$ of both penalized estimators were
+was measured by $s = \frac{||w||_1}{||w||_F}$ for each of the 18 classes.
+The $\ell_1$-penalized logistic regression
+yielded the mean (+/- standard deviation) sparsity $s$ 
+50.0 (+/- 2.6), 45.4 (+/- 2.3), 40.0 (+/- 2.4), 30.9 (+/- 2.0), and 24.0 (+/- 2.3)
+after model fitting with 20\% to 100\% training data.
+The hierarchical-tree-penalized logistic regression
+yield the sparsity $s$ 
+163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and $88.4$ (+/- $8.4$)
+after fitting 20\% to 100\% of the training data.
+% results: support recovery
+Finally, the support recovery was quantified by
+Pearson correlation $\rho$ between vectors of
+the zscored model coefficients
+and
+the zscored sample maps for each class.
+$\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
+achieved a mean $\rho$ (+/- standard deviation) of
+0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
+0.11 (+/- 0.03) versus 0.13 (+/- 0.05),
+0.13 (+/- 0.04) versus 0.17 (+/- 0.05),
+0.16 (+/- 0.04) versus 0.22 (+/- 0.05), and
+0.19 (+/- 0.05) versus 0.29 (+/- 0.06)
+from 20\% to 100\% training data.
 
@@
 only with bigger input data quantities.
-
+%
 \begin{figure*}
@@
 \end{figure*}
-
+%
 \paragraph{Support recovery as a function of region-network emphasis.}
@@
 \centering
-\caption{18-class out-of-sample performance by region-network emphasis}
+\caption{Out-of-sample performance by region-network emphasis}
 \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
@@
 \paragraph{Acknowledgment.}
-{\small The research leading to these results has received funding from the
-European Union Seventh Framework Programme (FP7/2007-2013)
-under grant agreement no. 604102 (Human Brain Project).
-Data were provided by the Human Connectome Project.
-Further support was received from
-the German National Academic Foundation (D.B.),
-the German Research Foundation (BZ2/2-1 and BZ2/3-1 to D.B.),
-and the MetaMRI associated team (B.T., G.V.).
+{\small Data were provided by the Human Connectome Project.
 }
+
+% {\small The research leading to these results has received funding from the
+% European Union Seventh Framework Programme (FP7/2007-2013)
+% under grant agreement no. 604102 (Human Brain Project).
+% Data were provided by the Human Connectome Project.
+% Further support was received from
+% the German National Academic Foundation (D.B.),
+% the German Research Foundation (BZ2/2-1 and BZ2/3-1 to D.B.),
+% and the MetaMRI associated team (B.T., G.V.).
+% }
 

### 2016-02-04 srne_plot_sparsity.py

@@ -1,0 +1,84 @@
+# import struct_estimator_dataratio_zerobrainlevel_weighted
+
+import os.path as op
+import numpy as np
+from scipy import linalg
+import joblib
+import nibabel as nib
+from nilearn.input_data import NiftiMasker
+from scipy.stats import pearsonr
+
+n_classes = 18
+
+def calc_sparsity(coef):
+    # L1 norm divided by L2 norm of coef matrix (latter is Frobenius)
+    return np.sum(np.abs(coef)) / linalg.norm(coef, ord='fro')
+
+# load the class mean (=ground truth)
+contrasts_names = [
+    'REWARD-PUNISH', 'PUNISH-REWARD', 'SHAPES-FACES', 'FACES-SHAPES',
+    'RANDOM-TOM', 'TOM-RANDOM',
+
+    'MATH-STORY', 'STORY-MATH',
+    'T-AVG', 'F-H', 'H-F',
+    'MATCH-REL', 'REL-MATCH',
+
+    'BODY-AVG', 'FACE-AVG', 'PLACE-AVG', 'TOOL-AVG',
+    '2BK-0BK'
+]
+mask_img = 'grey10_icbm_3mm_bin.nii.gz'
+nifti_masker = NiftiMasker(mask_img=mask_img, smoothing_fwhm=False,
+                           standardize=False)
+nifti_masker.fit()
+mask_nvox = nifti_masker.mask_img_.get_data().sum()
+task_means_z = np.zeros((mask_nvox, n_classes))
+from scipy.stats import zscore
+for i_c, c in enumerate(contrasts_names):
+    cur_mean = '/git/cohort/archi/prelim2/compr2task_means/mean_%s.nii.gz' % c
+    print cur_mean
+    print op.exists(cur_mean)
+    cur_task_mean = np.squeeze(nifti_masker.transform(cur_mean))
+    cur_task_mean = np.nan_to_num(cur_task_mean)
+    task_means_z[:, i_c] = cur_task_mean
+    # task_means_z[:, i_c] = zscore(cur_task_mean)
+
+
+REGS = ['tree-l2', 'l1']
+dataratios = np.linspace(20, 100, 5)
+
+for ratio in dataratios:
+    READ_DIR = 'srne_benchmark_dataratioFIXED%i_zerobrainlevel_weighted'
+    for reg in REGS:
+        print('-' * 80)
+        print('%s: %i' % (reg, ratio))
+
[…]

### 2016-02-04 paper/icml2016/example_paper.tex
sample complexity: add more results2

@@
 yield the sparsity $s$ 
-163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and $88.4$ (+/- $8.4$)
+163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and 88.4 (+/- 8.4)
 after fitting 20\% to 100\% of the training data.

### 2016-02-04 paper/icml2016/example_paper.tex
pass over figures

@@
 % \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
-\includegraphics[width=0.55\textwidth]{../figures/ROC_ALL_perclass.png}
+\includegraphics[width=0.55\textwidth]{../figures/ROC_ALL.png}
 \end{centering}
 \vspace{-0.4cm}
-\caption{\textbf{Model performance across sparsity priors.}
-Compares the performance of logistic regression estimators
-with 4 different structured and unstructered sparsity terms
+\caption{\textbf{Prediction performance across sparsity priors.}
+Comparison of the performance of logistic regression estimators
+with 6 different structured and unstructered sparsity penalties
 in classifying neural activity from 18 psychological tasks.
-The class-wise area under the curve (AUC)
-is obtained on the same test set.
+The class-wise area under the curve (AUC, \textit{colors})
+is obtained on an identical test set.
 %
@@
 imposed an equilibrium between sparsity and model fit.
+\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
+norm (with additional $\ell_1$ term)
+imposed region compartments, but naive to network structure.
 \textit{Trace-norm}: Structured trace-norm penalization
@@
 with sparsity of network patterns, but naive to region structure.
-\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
-norm with additional $\ell_1$ term
-imposed region compartments, but naive to network structure.
 %
@@
 %
-Logistic regression with sparse group sparsity
-imposes a structured $\ell_1/\ell_2$ block norm with additional $\ell_1$ term
+Logistic regression with (sparse) group sparsity
+imposes a structured $\ell_1/\ell_2$ block norm (with additional $\ell_1$ term)
 with a known atlas of region voxel groups onto the statistical estimation process.
@@
 in distinguishing unseen neural activity maps from 18 psychological tasks
-(89.67\%, mean recall XX.YY, mean precision XX.YY).
+(89.7\% accuracy, mean precision 86.7, mean recall 91.5).
 It was closely followed by logistic regression
 structured by trace-norm regularization
-(89.43\%, mean recall XX.YY, mean precision XX.YY).
+(89.4\%, precision 86.4, recall 91.3).
 Lasso featured an average performance comparing to the other sparse estimators
-(88.60\%, mean recall XX.YY, mean precision XX.YY).
+(88.60\%, precision 85.7, recall 90.3).
+Elastic-Net, in turn, featured an
+average performance comparing to the other sparse estimators
+(88.1\%, precision 84.8, recall 84.1).
 Introducing a priori knowledge of brain region compartments
-by sparse group sparsity performed worst
-(87.89\%, mean recall XX.YY, mean precision XX.YY).
+by sparse group sparsity (87.9\%, precision 84.8, recall 89.5)
+and
+by group sparsity (87.9\%, precision 85.3, recall 90.3)
+performed worst.
 %
@@
 Removing region structure from the prior achieved
-88,84\% accuracy (mean recall XX.YY, mean precision XX.YY),
+88,84\% accuracy,
 while removing network structure from the prior achieved
-87,05\% accuracy (mean recall XX.YY, mean precision XX.YY).
+87,05\% accuracy.
 These results from partial priors are indeed outperformed
-the full region-network tree prior at 89,67\% accuracy
-(mean recall XX.YY, mean precision XX.YY).
+the full region-network tree prior at 89,67\% accuracy.
 %
@@
 (\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-The out-of-sample accuracies for predicting all 18 psychological tasks
-is given in percent.
+The support recovery of that exemplary task is given
+as Pearson correlation (cf. methods).
 %
@@
 better support recovery with the biggest difference
-in model performance.
+in model performance (83.7\% versus 89.0\%).
 %
@@
 % results: accuracy
-Regarding classification performances on the always same test set,
+Regarding classification performance on the always same test set,
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
@@
 % results: sparsity
-Regarding the model sparsity,
-the model weights $w$ of both penalized estimators were
-was measured by $s = \frac{||w||_1}{||w||_F}$ for each of the 18 classes.
+Regarding model sparsity,
+the measure $s = \frac{||w||_1}{||w||_F}$ was computed from
+the model weights $w$ of both penalized estimators
+for each of the 18 classes.
 The $\ell_1$-penalized logistic regression
-yielded the mean (+/- standard deviation) sparsity $s$ 
+yielded the mean (+/- standard deviation) sparsities
 50.0 (+/- 2.6), 45.4 (+/- 2.3), 40.0 (+/- 2.4), 30.9 (+/- 2.0), and 24.0 (+/- 2.3)
@@
 The hierarchical-tree-penalized logistic regression
-yield the sparsity $s$ 
+yield the sparsities
 163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and 88.4 (+/- 8.4)
@@
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
-achieved a mean $\rho$ (+/- standard deviation) of
+achieved a mean $\rho$ (+/- standard deviation) recovery of
 0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
@@
 0.19 (+/- 0.05) versus 0.29 (+/- 0.06)
-from 20\% to 100\% training data.
+based on 20\% to 100\% training data.
 

### 2016-02-04 srne_plot_roc.py

@@ -12,15 +12,16 @@ from scipy import interp
 import joblib
 
 n_classes = 18
+plt.close('all')
 
 READ_DIR = 'srne_benchmark_dataratioFIXED100_zerobrainlevel_weighted'
 
 REGS = ['tree-l2', 'l1',
-        'elastic-net', 'trace-norm', 
-        'sparse-group-lasso-l2', 'group-lasso-l2']
+        'elastic-net', 
+        'sparse-group-lasso-l2', 'group-lasso-l2', 'trace-norm']
 REGS_STR = ['Hierarchical Tree Sparsity', 'Lasso',
-            'Elastic-Net', 'Trace-Norm', 
-            'Sparse Group Lasso', 'Group Lasso']
+            'Elastic-Net', 
+            'Sparse Group Lasso', 'Group Lasso', 'Trace-Norm']
 
 auc_mat = np.zeros((len(REGS), n_classes))
 
@@ -75,10 +76,10 @@ for i_r, r in enumerate(REGS):
 plt.figure()
 for i_c in range(n_classes):
     plt.plot(np.arange(len(REGS)), auc_mat[:, i_c] * 100, linewidth=2)
-plt.ylim([35., 102.])
-plt.xticks(np.arange(len(REGS)), REGS, rotation=35)
-plt.ylabel('AUC [%]')
-plt.title('Comparing classifications of 18 tasks')
+plt.ylim([40., 102.])
+plt.xticks(np.arange(len(REGS)), REGS_STR, rotation=35)
+plt.ylabel('AUC')
+# plt.title('Comparing classifications of 18 tasks')
 plt.tight_layout()
 plt.show()
 plt.savefig(op.join(READ_DIR, 'ROC_ALL_perclf.png'))

### 2016-02-04 srne_plot_sparsity.py

@@ -43,8 +43,13 @@ for i_c, c in enumerate(contrasts_names):
     # task_means_z[:, i_c] = zscore(cur_task_mean)
 
 
-REGS = ['tree-l2', 'l1']
-dataratios = np.linspace(20, 100, 5)
+# REGS = ['tree-l2', 'l1']
+REGS = ['tree-l2',
+    'group-lasso-l2', 'sparse-group-lasso-l2',
+    'l1', 'elastic-net',
+    'trace-norm']
+# dataratios = np.linspace(20, 100, 5)
+dataratios = [100]
 
 for ratio in dataratios:
     READ_DIR = 'srne_benchmark_dataratioFIXED%i_zerobrainlevel_weighted'

### 2016-02-04 paper/icml2016/example_paper.tex
figs centered

@@
   Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
-\icmlauthor{Michael Eickenberg}{Michael.Eickenberg@inria.fr}
+\icmlauthor{Michael Eickenberg}{Michael.Eickenberg@normalesup.org}
 \icmladdress{Department d'Informatique, Ecole Normale Superieure, Paris}
@@
 if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.
-
-\paragraph{Optimization.}
 We optimize the data loss function using an iterative forward-backward
-scheme analogous to (F)ISTA for the lasso \cite{beck2009}. 
-{\color{red} Michael: Algorithm specification to be removed for ICML - supposed known, except possibly for hierarchical prox.}
-We divide the
-loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
-logistic regression loss) and a potentially non-smooth, convex 
-regularization term \(G(w)\). 
-Define \(\prox_{\gamma G}(v) = (\Id + \gamma\partial G)^{-1}(v)\), where \(\partial G\) is the subdifferential of \(G\) and 
-let \(\nabla F(v)\) be the gradient of \(F\) in \(v\). Further let \(L > 0\)
-be a Lipschitz constant of the gradient of \(F\) and choose a step size
-\(\varepsilon\in (0, \frac{2}{L})\). Starting with an arbitrary 
-initialization of \(w_0\), putting \(z_1 = w_0\) and \(t_1 = 1\), then for
-\(k\geq 1\) until convergence do:
-\begin{eqnarray*}
-  x_k & = & \prox_{\varepsilon G}(y_k - \varepsilon\nabla F(y_k))\\
-  t_{k + 1} & = & \frac{1 + \sqrt{1 + 4 t_k^2}}{2}\\
-  y_{k + 1} & = & x_k + \left(\frac{t_k - 1}{t_{k + 1}}\right)(x_k - x_{k - 1})
-\end{eqnarray*}
-In our case \(G(v) = \lambda\Omega(v)\). Splitting \(\Omega(v) = \Omega_{\mathcal H}(v) + \Omega_{\mathcal G}(v)\) with 
-\(\Omega_{\mathcal H}(v) = \alpha\sum_{h\in\mathcal H}\eta_h\|v_h\|_2\) and
-\(\Omega_{\mathcal G}(v) = \beta\sum_{g\in\mathcal G}\eta_g\|v_g\|_2\), we observe
-that \[\prox_{\varepsilon\lambda\Omega_{\mathcal H}}(v) = \sum_{h\in\mathcal H}\iota_h\left([\|v_h\|_2 > \eta_h\varepsilon\lambda\alpha]\left(v_h - \eta_h\varepsilon\lambda\alpha\frac{v_h}{\|v_h\|_2}\right)\right),\]
-where \(\iota_h\) is the canonical injection of the group \(h\) into 
-\(\R^p\) (if \(\pi_g: v\mapsto v_g\), then \(\iota_g = \pi_g^\ast\) the 
-adjoint/transposed operator). This holds analogously for 
-\(\Omega_{\mathcal G}\).
-According to \cite{jenatton2011}, the proximal operator of 
-the hierarchical penalty \(\varepsilon\lambda\Omega\) is
-\[\prox_{\varepsilon\lambda\Omega}(v) = \prox_{\varepsilon\lambda\Omega_{\mathcal H}}\circ\prox_{\varepsilon\lambda\Omega_{\mathcal G}}(v).\]
+scheme analogous to FISTA for the lasso \cite{beck2009}.
+
+% \paragraph{Optimization.}
+% We optimize the data loss function using an iterative forward-backward
+% scheme analogous to FISTA for the lasso \cite{beck2009}. 
+% We divide the
+% loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
+% logistic regression loss) and a potentially non-smooth, convex 
+% regularization term \(G(w)\). 
+% Define \(\prox_{\gamma G}(v) = (\Id + \gamma\partial G)^{-1}(v)\), where \(\partial G\) is the subdifferential of \(G\) and 
+% let \(\nabla F(v)\) be the gradient of \(F\) in \(v\). Further let \(L > 0\)
+% be a Lipschitz constant of the gradient of \(F\) and choose a step size
+% \(\varepsilon\in (0, \frac{2}{L})\). Starting with an arbitrary 
+% initialization of \(w_0\), putting \(z_1 = w_0\) and \(t_1 = 1\), then for
+% \(k\geq 1\) until convergence do:
+% \begin{eqnarray*}
+%   x_k & = & \prox_{\varepsilon G}(y_k - \varepsilon\nabla F(y_k))\\
+%   t_{k + 1} & = & \frac{1 + \sqrt{1 + 4 t_k^2}}{2}\\
+%   y_{k + 1} & = & x_k + \left(\frac{t_k - 1}{t_{k + 1}}\right)(x_k - x_{k - 1})
+% \end{eqnarray*}
+% In our case \(G(v) = \lambda\Omega(v)\). Splitting \(\Omega(v) = \Omega_{\mathcal H}(v) + \Omega_{\mathcal G}(v)\) with 
+% \(\Omega_{\mathcal H}(v) = \alpha\sum_{h\in\mathcal H}\eta_h\|v_h\|_2\) and
+% \(\Omega_{\mathcal G}(v) = \beta\sum_{g\in\mathcal G}\eta_g\|v_g\|_2\), we observe
+% that \[\prox_{\varepsilon\lambda\Omega_{\mathcal H}}(v) = \sum_{h\in\mathcal H}\iota_h\left([\|v_h\|_2 > \eta_h\varepsilon\lambda\alpha]\left(v_h - \eta_h\varepsilon\lambda\alpha\frac{v_h}{\|v_h\|_2}\right)\right),\]
+% where \(\iota_h\) is the canonical injection of the group \(h\) into 
+% \(\R^p\) (if \(\pi_g: v\mapsto v_g\), then \(\iota_g = \pi_g^\ast\) the 
+% adjoint/transposed operator). This holds analogously for 
+% \(\Omega_{\mathcal G}\).
+% According to \cite{jenatton2011}, the proximal operator of 
+% the hierarchical penalty \(\varepsilon\lambda\Omega\) is
+% \[\prox_{\varepsilon\lambda\Omega}(v) = \prox_{\varepsilon\lambda\Omega_{\mathcal H}}\circ\prox_{\varepsilon\lambda\Omega_{\mathcal G}}(v).\]
 
@@
 \begin{figure*}
-\begin{centering}
+\centering
 \includegraphics[width=0.8\textwidth]{../figures/reg_net_prior_colin.pdf}
-\end{centering}
 \vspace{-0.2cm}
@@
 \includegraphics[width=0.55\textwidth]{../figures/ROC_ALL.png}
-\end{centering}
 \vspace{-0.4cm}
@@
 }
+\end{centering}
 \label{fig_sparsities}

### 2016-02-04 paper/icml2016/example_paper.tex
abide b ICML guidlines

@@
 % the note in the first column to ``Under review.  Do not distribute.''
-% \usepackage{icml2016}
+\usepackage{icml2016}
 
@@
 % note in the first column to ``Proceedings of the...''
-\usepackage[accepted]{icml2016}
+% \usepackage[accepted]{icml2016}
 
@@
 %
-\paragraph{Rationale.}
+\subsection{Rationale}
+% \paragraph{Rationale.}
 3D brain maps obtained by neuroimaging
@@
 
-\paragraph{Problem formulation.}
+% \paragraph{Problem formulation.}
+\subsection{Problem formulation}
 We formulate our estimation problem in the framework of regularized risk
 estimation applied to linear models: 
-We would like to estimate a good predictor of cognitive task
+The goal is to estimate a good predictor of cognitive task
 given a brain image. Let the set \(\mathcal X\subset\R^p\) represent brain
@@
 if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.
-We optimize the data loss function using an iterative forward-backward
+The data loss function is approximated using an iterative forward-backward
 scheme analogous to FISTA for the lasso \cite{beck2009}.
@@
 
-\paragraph{Hyperparameter optimization.}
+% \paragraph{Hyperparameter optimization.}
+\subsection{Hyperparameter optimization}
 The stratified and shuffled training data were submitted
@@
 
-\paragraph{Implementation.}
+% \paragraph{Implementation.}
+\subsection{Implementation}
 All analyses were performed in Python.
@@
 %
-\paragraph{Data.}
+\subsection{Data}
+% \paragraph{Data.}
 As the currently biggest openly-accessible reference dataset,
@@
 
-\paragraph{Benchmarking hierarchical tree sparsity against
-common sparsity penalties.}
+% \paragraph{Benchmarking hierarchical tree sparsity against
+\subsection{Benchmarking hierarchical tree sparsity against
+common sparsity penalties}
 Hierarchical region-network priors have been systematically
@@
 
-\paragraph{Sample complexity of naive versus informed sparse model selection.}
+\subsection{Sample complexity of naive versus informed sparse model selection}
+% \paragraph{Sample complexity of naive versus informed sparse model selection.}
 Subsequently, the sample complexity of
@@
 %
-\paragraph{Support recovery as a function of region-network emphasis.}
+\subsection{Support recovery as a function of region-network emphasis}
+% \paragraph{Support recovery as a function of region-network emphasis.}
 Finally, the relative importance of the
@@
 
-\paragraph{Acknowledgment.}
-{\small Data were provided by the Human Connectome Project.
-}
-
+% \paragraph{Acknowledgment.}
 % {\small The research leading to these results has received funding from the

### 2016-02-04 paper/icml2016/example_paper.tex
integrate Bertrands comments

@@
 logistic-regression estimators to distinguish neural activity.
-This remarries the perspectives of
-functional segregation and functional integration
-that are routinely divorced in neuroscientific research.
+This enables recombination of
+the neurobiological architectures underlying
+functional segregation into brain regions and
+functional integration by brain networks
+that are routinely studied separately in neuroscientific research.
 %
@@
 total observations per data sample.
-This \(n << p\) scenario challenges various statistical methods from
+This $n \ll p$ scenario challenges various statistical methods from
 classical statistics.
@@
 Yet, what generally accepted neurobiological structure lends itself
-to fruitful exploitation using structured sparsity priors?
+to exploitation using structured sparsity priors?
 
@@
 %
-Based on the largest neuroimaging repository (Human Connectome Project [HCP]),
+Based on the largest public neuroimaging repository
+(Human Connectome Project [HCP], \url{http://www.humanconnectomeproject.org/}),
 we demonstrated that domain-informed supervised models
@@
 tree penalties to jointly incorporate region 
-specialization and network integration priors into supervised 
+specialization and network integration priors into multivariate 
 estimators.
@@
 of samples rarely exceeds few hundreds.
-This \(n << p\) scenario directly implies underdetermination of any
+This $n \ll p$ scenario directly implies underdetermination of any
 linear model based on dot products with the voxel values.
@@
 Consequently,
-each region from a brain atlas can be uniquely associate to one
+each region from a brain atlas can be uniquely associated with one
 the extracted ICA networks.
@@
 \(\hat y = X\hat w + \hat b\), while regularizing to incorporate a useful
-prior. Taken together, this can be framed as an optimization problem
+prior:
 \[\argmin_{w, b} \mathcal L(Xw + b, y) + \lambda\Omega(w),\]
@@
 \caption{\textbf{Building blocks of the region-network tree.}
-Depicts neurobiological priors introduced into the classification problem 
-by hierarchical structured sparsity.
+Neurobiological priors introduced into the classification problem 
+by hierarchical structured sparsity are displayed.
 \textit{Left:} Continuous, partially overlapping brain network priors
@@
 in distinguishing unseen neural activity maps from 18 psychological tasks
-(89.7\% accuracy, mean precision 86.7, mean recall 91.5).
+(89.7\% multi-class accuracy, mean precision 86.7, mean recall 91.5).
 It was closely followed by logistic regression
@@
 Equal region and network emphasis yields more dispersed,
-less interpretable predictive model choices.
+less interpretable model choices.
 }

### 2016-02-04 paper/icml2016/example_paper.tex
make a and b explicit

@@
 both region and network priors
-exhibited the best out-of-sample performance.
+exhibited the best out-of-sample performance
+($\alpha = 1, \beta = 1$).
 \textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
@@
 incorporated a hierarchy of previously known region and network neighborhoods
-for a neurobiological bias of the statistical estimation.
+for a neurobiological bias of the statistical estimation
+($\alpha = 1, \beta = 1$).
 %
@@
 to hierarchical-tree-penalized logistic regression
-(\textit{lower row})
+($\alpha = 1, \beta = 1$, \textit{lower row})
 with increasing fraction
@@
 $\ell_1$-penalized and hierarchical-tree-penalized logistic regression
+($\alpha = 1, \beta = 1$)
 were quantitatively compared (Figure \ref{fig_dataratio}).
@@
 on model selection
-is systematically varied against each other.
+is systematically varied against each other
+(i.e., $\alpha$ and $\beta$ are changed reciprocally).
 This region-network ratio (\textit{upper fractions}) weighted voxel groups
@@
 increased the relative importance of known region structure
-by multiplying $\frac{3}{1}$ to
+by multiplying $\beta = \frac{3}{1}$ to
 $\eta_g$ of all region group penalties
 and multiplying
-$\frac{1}{3}$ to $\eta_g$ of all network group penalties
+$\alpha = \frac{1}{3}$ to $\eta_g$ of all network group penalties
 (Table \ref{table_reg_net_ratio}).

### 2016-02-04 paper/icml2016/example_paper.tex
add big picture

@@
 with one or several target variables.
-The principled regularization scheme could even inform
-unsupervised structure-discovery methods,
-such as principal component analysis
-\cite{jenatton2009structured}
-and
-k-means clustering \cite{witten2010framework}.
-%
+The principled regularization scheme could inform
+unsupervised structure-discovery by
+matrix factorization and clustering algorithms
+\cite{jenatton2009structured, witten2010framework}.
 Additionally,
@@
 \cite{gramfort2011tracking}.
+%
+The deterministic choice of a region and network atlas
+could further be avoided by
+sparse selection of overcomplete region-network dictionaries.
+Non-hierarchical penalty terms will probably allow for
+more complex structured sparsity that
+extend the recently enabled tree dependencies.
 %

### 2016-02-04 paper/icml2016/example_paper.tex
add cit + AUC in 1 tier

@@
 Logistic regression with trace-norm penalization
-imposed low-rank structure.
+imposed low-rank structure \cite{harchaoui2012large}.
 This supervised classification algorithm
@@
 in distinguishing unseen neural activity maps from 18 psychological tasks
-(89.7\% multi-class accuracy, mean precision 86.7, mean recall 91.5).
+(89.7\% multi-class accuracy, mean AUC 94.8 [+/- 9.1 standard deviation]
+mean precision 86.7, mean recall 91.5).
 It was closely followed by logistic regression
 structured by trace-norm regularization
-(89.4\%, precision 86.4, recall 91.3).
+(89.4\%, mean AUC 90.8 [+/- 14.8],
+precision 86.4, recall 91.3).
 Lasso featured an average performance comparing to the other sparse estimators
-(88.60\%, precision 85.7, recall 90.3).
+(88.60\%, mean AUC 94.3 [+/- 9.3],
+precision 85.7, recall 90.3).
 Elastic-Net, in turn, featured an
 average performance comparing to the other sparse estimators
-(88.1\%, precision 84.8, recall 84.1).
+(88.1\%, mean AUC 94.1 [+/- 10.2],
+precision 84.8, recall 84.1).
 Introducing a priori knowledge of brain region compartments
-by sparse group sparsity (87.9\%, precision 84.8, recall 89.5)
+by sparse group sparsity
+(87.9\%, mean AUC 93.9 [+/- 10.1], precision 84.8, recall 89.5)
 and
-by group sparsity (87.9\%, precision 85.3, recall 90.3)
+by group sparsity
+(87.9\%, mean AUC 84.7 [+/- 17.3], precision 85.3, recall 90.3)
 performed worst.
@@
 more complex structured sparsity that
-extend the recently enabled tree dependencies.
+extend the recently enabled parent-children dependencies.
 %

### 2016-02-04 srne_plot_roc.py

@@ -72,6 +72,11 @@ for i_r, r in enumerate(REGS):
     plt.show()
     plt.savefig(dump_path + '_ROC.png')
 
+for i_r, r in enumerate(REGS):
+    print('%s: mean %.2f std: %.2f' % (
+        r, np.mean(auc_mat[i_r, :]), np.std(auc_mat[i_r, :])
+    ))
+
 # summary AUC plot: per classifier
 plt.figure()
 for i_c in range(n_classes):
@@ -93,7 +98,7 @@ for i_r in range(len(REGS)):
              linewidth=2)
 plt.ylim([35., 102.])
 plt.xticks(np.arange(n_classes), np.arange(n_classes) + 1)
-plt.ylabel('AUC [%]')
+plt.ylabel('AUC')
 plt.title('Comparing classifications of 18 classes')
 plt.xlabel('psychological task')
 plt.tight_layout()

### 2016-02-05 paper/icml2016/example_paper.tex
shorten title
reformulate methods

@@
 images of \(p > 0\) voxels.
-
-Then we would like to minimize the risk \(\mathcal L(\hat y, y)\), where
-\(\hat y = X\hat w + \hat b\), while regularizing to incorporate a useful
-prior:
-\[\argmin_{w, b} \mathcal L(Xw + b, y) + \lambda\Omega(w),\]
+%
+We minimize the risk \(\mathcal L(\hat y, y)\) with
+\(\hat y = f(X\hat w + \hat b)\), where \(f\) is a link function 
+(e.g. sigmoid for logistic regression, identity for linear regression),
+and \(\mathcal L\) usually represents an appropriate negative loglikelihood.
+We incorporate a useful prior through regularization:
+\[\argmin_{w, b} \mathcal L(f(Xw + b), y) + \lambda\Omega(w),\]
 where \(\lambda > 0\) and \(\Omega\) is the regularizer.
 
-Brain regions are defined as disjoint groups of voxels. Let \(\mathcal G\)
+Brain \textit{regions} are defined as disjoint groups of voxels. Let \(\mathcal G\)
 be a partition of \(\{1, \dots, p\}\), i.e.
@@
 
-Brain networks consist of regions and are thus super-regions or groups of 
-regions. The set of brain networks \(\mathcal{H}\) is also a partition of 
+Brain \textit{networks} consist of a group of one or several brain regions.
+The set of brain networks \(\mathcal{H}\) also forms a partition of 
 \(\{1, \dots, p\}\) and in addition it is consistent with \(\mathcal G\) in

### 2016-02-05 paper/icml2016/example_paper.tex
ref

@@
 \textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
-This allows a clear association of each region \(g\in\mathcal G\) to a 
+This allows the association of each region \(g\in\mathcal G\) to a 
 network \(h\in\mathcal H\) and thus establishes a tree structure (up to 
@@
 penalization of brain networks and thus to tendentially fully active groups
-and dense brain maps. If at the same time \(\beta\) is increased to a point
-of inducing group sparsity, then only the structure of brain regions encoded
-by \(\mathcal G\) is present. Conversely, if \(\beta\) is decreased to 
-become non-selective, and \(\alpha\) is increased to group selectivity,
-then the structure imposed will come from \(\mathcal H\), leading to the
+and dense brain maps. If at the same time \(\beta\) is increased to 
+induce group sparsity, then only the structure of brain regions encoded
+by \(\mathcal G\) is present. Conversely, if \(\beta\) is chosen 
+sufficiently small, and \(\alpha\) increased,
+then the structure will come from \(\mathcal H\), leading to the
 selection of brain networks rather than regions.
@@
 then necessarily the network containing it must be active.
-This relation is asymmetric, since when swapping the roles of \(\mathcal G\)
- and \(\mathcal H\), these statements do not hold true anymore. A brain 
+This relation is asymmetric, the roles of \(\mathcal G\) and \(\mathcal H\) 
+cannot be swapped: A brain 
 region can set all its coefficients to zero without forcing the 
 corresponding network to zero. A brain network can be active without its
-subregions necessarily being active.
+subregions being active.
 When evaluating the trade-off in \((\alpha, \beta)\), this needs to be taken
@@
 if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.
-The data loss function is approximated using an iterative forward-backward
+We optimize parameters \(w\) using an iterative forward-backward
 scheme analogous to FISTA for the lasso \cite{beck2009}.
@@
 (number of maximal iterations=$100$, tolerance=$0.001$).
-In the outer CV layer, grid search
+{\color{red} In the outer CV layer, grid search
 selected among candidates for the respective $\lambda$ parameter
-by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
+by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.}
 Importantly, the thus selected sparse logistic regression classifier was

### 2016-02-05 paper/icml2016/example_paper.tex
scikit-learn
typo

@@
 \cite{abrah14},
-\textit{scikit learn} to design machine-learning
+\textit{scikit-learn} to design machine-learning
 data processing pipelines
@@
 % \paragraph{Data.}
-As the currently biggest openly-accessible reference dataset,
+As the currently biggest openly accessible reference dataset,
 we chose resources from the Human Connectome Project (HCP)

### 2016-02-05 paper/icml2016/example_paper.tex
interm

--- 2016-02-05 paper/icml2016/example_paper.tex
@@
 \twocolumn[
-\icmltitle{Region-Network Hierarchical Sparsity Priors for\\
+\icmltitle{Hierarchical Region-Network Sparsity for\\
 High-Dimensional Inference in Brain Imaging}
@@
 statistical models applied to high-dimensional data in various domains.
+%
 As an extension to imaging neuroscience,
@@
 priors on network hierarchies of brain regions into
-logistic-regression estimators to distinguish neural activity.
-This enables recombination of
-the neurobiological architectures underlying
+logistic-regression to distinguish neural activity.
+This recombines neurobiological architectures underlying
 functional segregation into brain regions and
 functional integration by brain networks
-that are routinely studied separately in neuroscientific research.
-%
-Region-network hierarchical priors for classifying
-18 psychological tasks
-from a reference dataset are
-shown to outperform naive $\ell_1$-norm, elastic-net, and
-trace-norm penalization, as well as neurobiologically
-informed $\ell_1/\ell_2$-block-norm group sparsity.
+that are studied separately in neuroscientific research.
+%
+Hierarchical region-network priors are shown to better classify
+18 psychological tasks from a reference dataset
+than other sparse estimators.
 Weighing the relative importance of
@@
 %
-It is thus demonstrated
-that priors of local and global neurobiological knowledge
-can enhance
-generalization performance, sample complexity, and domain interpretability
-by hierarchical tree sparsity.
+Local and global priors of neurobiological knowledge
+are thus demonstrated to enhance
+generalization performance, sample complexity, and domain interpretability.
 
@@
 images of \(p > 0\) voxels.
-%
-We minimize the risk \(\mathcal L(\hat y, y)\) with
-\(\hat y = f(X\hat w + \hat b)\), where \(f\) is a link function 
-(e.g. sigmoid for logistic regression, identity for linear regression),
-and \(\mathcal L\) usually represents an appropriate negative loglikelihood.
-We incorporate a useful prior through regularization:
-\[\argmin_{w, b} \mathcal L(f(Xw + b), y) + \lambda\Omega(w),\]
+
+Then we would like to minimize the risk \(\mathcal L(\hat y, y)\), where
+\(\hat y = X\hat w + \hat b\), while regularizing to incorporate a useful
+prior:
+\[\argmin_{w, b} \mathcal L(Xw + b, y) + \lambda\Omega(w),\]
 where \(\lambda > 0\) and \(\Omega\) is the regularizer.
 
-Brain \textit{regions} are defined as disjoint groups of voxels. Let \(\mathcal G\)
+Brain regions are defined as disjoint groups of voxels. Let \(\mathcal G\)
 be a partition of \(\{1, \dots, p\}\), i.e.
@@
 
-Brain \textit{networks} consist of a group of one or several brain regions.
-The set of brain networks \(\mathcal{H}\) also forms a partition of 
+Brain networks consist of regions and are thus super-regions or groups of 
+regions. The set of brain networks \(\mathcal{H}\) is also a partition of 
 \(\{1, \dots, p\}\) and in addition it is consistent with \(\mathcal G\) in

### 2016-02-05 srne_plot_roc.py

@@ -73,7 +73,7 @@ for i_r, r in enumerate(REGS):
     plt.savefig(dump_path + '_ROC.png')
 
 for i_r, r in enumerate(REGS):
-    print('%s: mean %.2f std: %.2f' % (
+    print('%s: mean %.3f std: %.3f' % (
         r, np.mean(auc_mat[i_r, :]), np.std(auc_mat[i_r, :])
     ))
 
@@ -82,8 +82,9 @@ plt.figure()
 for i_c in range(n_classes):
     plt.plot(np.arange(len(REGS)), auc_mat[:, i_c] * 100, linewidth=2)
 plt.ylim([40., 102.])
-plt.xticks(np.arange(len(REGS)), REGS_STR, rotation=35)
-plt.ylabel('AUC')
+REGS_STR_auc = ['' + r + '\nmean AUC=%.1f' % np.mean(auc_mat[i_r, :] * 100) for i_r, r in enumerate(REGS_STR)]
+plt.xticks(np.arange(len(REGS)), REGS_STR_auc, rotation=35)
+plt.ylabel('class AUC')
 # plt.title('Comparing classifications of 18 tasks')
 plt.tight_layout()
 plt.show()

### 2016-02-05 paper/icml2016/example_paper.tex
style up 1 §

@@
 Many quantitative scientific domains underwent a
-recent passage from the classical regime (i.e., ``long data")  to
-the high-dimensional regime (i.e., ``wide data").
+recent passage from the classical ``long data" regime to
+the high-dimensional ``wide data" regime.
 % the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
@@
 \cite{hastie2015statistical}.
-They act as a 
-regularizer and can be used for model selection.
+They act as regularizer by encouraging zero coefficients
+in model selection.
 Sparse supervised and unsupervised
@@
 %
-Generally, \textit{structured sparsity} can impose
+Moreover, \textit{structured sparsity} can impose
 domain knowledge on the 
@@
 \cite{kanwisher2010functional}.
-Conversely, functional integration emphasizes that brain function
+Conversely, functional integration emphasizes that brain computation
 is enabled by a complex interplay between these
@@
 infrastructure
-and unique global connectivity profiles are thought to go hand-in-hand
-to realize brain function.
+and global connectivity profiles are thought to go hand-in-hand
+to realize neural processes.
 %
@@
 For instance,
-single-cell recordings and microscopic examination
+single-cell recordings and microscopic tissue examination
 revealed the

### 2016-02-05 paper/icml2016/example_paper.tex
style up 2

@@
 as the basic architecture of brain organization,
-in stark constrast to methods examining regional specialization.
+in contrast to methods examining regional specialization.
 
@@
 by introducing neurobiologically plausible region and network priors
-to design neuroscience-specific estimators.
+to design neuroscience-specific classifiers.
 %
@@
 and generalize better to new samples
-than domain-naive estimators.
+than domain-naive blackbox estimators.
 
 \section{Methods}
-The main contribution is the domain adaptation of hierarchical structured
+This paper contributes a domain adaptation of hierarchical structured
 tree penalties to jointly incorporate region 
 specialization and network integration priors into multivariate 
-estimators.
+classification.
 We capitalize on hierarchical group lasso as recently introduced
@@
 global connectivity when discriminating defined psychological tasks
-from brain activity.
+from neural activity maps.
 % Bertrand: univariate-multivariate is orthogonal to the
@@
 % \paragraph{Rationale.}
-3D brain maps obtained by neuroimaging
-techniques are high-dimensional but, luckily,
-their signal is highly structured.
+3D brain maps acquired by neuroimaging
+scanners are high-dimensional but, luckily,
+their signal is also highly structured.
 Its explicit dimensionality, the number of brain voxels,
@@
 
-Large-scale brain networks emerge in human individuals around birth
+Major brain networks emerge in human individuals around birth
 \cite{doria2010}, before mental capacities mature in childhood. 
 In adults,
-the sets of regions that compose
-a given spatiotemporally cohesive network are known to have more
+the regions that compose
+a given cohesive network are known to have more
 similar functional profiles than nodes from different networks
 \cite{anderson2013}.
-As a well-established method for network estimation
-\cite{beckmann2005},
-ICA yields continuous brain maps with
+As a well-established method for network estimation,
+ICA \cite{beckmann2005} yields continuous brain maps with
 weights for each voxel. The region nodes of ICA
@@
 Such brain atlases can be obtained by segregating
-the brain's grey matter into spatially compact voxel groups
-using clustering algorithmisms
+the brain's grey matter into local voxel groups
+using clustering algorithisms
 \cite{cbp2015review}.
 Consequently,
-each region from a brain atlas can be uniquely associated with one
+each region from a brain atlas can be uniquely associated with one of
 the extracted ICA networks.
@@
 
-This tree structure can be seamlessly plugged into
-a recently introduced hierarchical sparsity estimator
+This tree structure can be plugged into
+hierarchical sparsity penalty terms
 \cite{jenatton2011multi}.
@@
 the voxels of the brain regions associated to them.
-Each network node, in turn, descends into a second hierarchical level of
+Each network node in turn descends into a second hierarchical level of
 brain regions of spatially neighboring voxel groups.
@@
 voxel penalties of the region level,
-we can design different estimation regimes.
-%
-Setting a low penalty on the network groups makes it probable
-that all of them are active in the estimated weight map. If we then select
+we can design distinct estimation regimes.
+%
+Setting a low penalty on the network groups makes it is probable
+that all of them are active in the estimated weight maps. If we then select
 higher penalties on region groups, selection of relevant region groups is

### 2016-02-05 paper/icml2016/example_paper.tex
style up 3

@@
 higher penalties on region groups, selection of relevant region groups is
-forced without negligable bias of the network definitions.
+forced without obeying network definitions.
 Conversely, setting low penalties on the region definitions
@@
 %
-This region-network tradeoff allows inspecting the relative contributions
+This region-network equilibrium allows inspecting the relative contributions
 of the region and network levels
@@
 \subsection{Problem formulation}
-We formulate our estimation problem in the framework of regularized risk
-estimation applied to linear models: 
-The goal is to estimate a good predictor of cognitive task
-given a brain image. Let the set \(\mathcal X\subset\R^p\) represent brain
+We formulate our estimation problem in the framework of regularized
+empirical risk
+minimization applied to linear models.
+The goal is to estimate a good predictor of psychological task
+given single brain images. Let the set \(\mathcal X\in\R^{nxp}\) represent brain
 images of \(p > 0\) voxels.
 %
-We minimize the risk \(\mathcal L(\hat y, y)\) with
+We then minimize the risk \(\mathcal L(\hat y, y)\) with
 \(\hat y = f(X\hat w + \hat b)\), where \(f\) is a link function 
-(e.g. sigmoid for logistic regression, identity for linear regression),
+(e.g., sigmoid for logistic regression, identity for linear regression),
 and \(\mathcal L\) usually represents an appropriate negative loglikelihood.
-We incorporate a useful prior through regularization:
+We incorporate an informative prior through regularization:
 \[\argmin_{w, b} \mathcal L(f(Xw + b), y) + \lambda\Omega(w),\]
@@
 
-Brain \textit{networks} consist of a group of one or several brain regions.
+Brain \textit{networks} consist of one or several brain regions.
 The set of brain networks \(\mathcal{H}\) also forms a partition of 
-\(\{1, \dots, p\}\) and in addition it is consistent with \(\mathcal G\) in
+\(\{1, \dots, p\}\) that is consistent with \(\mathcal G\) in
 the sense that
-\[\textrm{for all }g\in\mathcal G, h\in\mathcal H,\quad
+\[\forall g\in\mathcal G, h\in\mathcal H,\quad
 \textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
-This allows the association of each region \(g\in\mathcal G\) to a 
-network \(h\in\mathcal H\) and thus establishes a tree structure (up to 
-adding a root node containing all voxels).
+This allows an unambiguous assignment of each region \(g\in\mathcal G\) to one
+network \(h\in\mathcal H\) and thus establishes a tree structure.
+A root node is added to contain all voxels.
 
@@
 \(w_g\in\R^{|g|}\) is defined as the restriction of \(w\) to the coordinates
- in \(g\). The structured penalty incorporating network
+ in \(g\). The penalty structured by network
 and region information can then be written as
 \[\Omega(w) = \alpha\sum_{h\in\mathcal H}\eta_h\|w_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|w_g\|_2.\]
-According to \cite{yuan2006model} we set \(\eta_g = 1/\sqrt{|g|}\) to
-account for varying group size. The hierarchy-level-specific factors 
-\(\alpha > 0\) and \(\beta > 0\) are used to trade-off region-weighted and
+As originally recommended \cite{yuan2006model},
+we set \(\eta_g = 1/\sqrt{|g|}\) to
+account for discrepancy in group sizes. The hierarchy-level-specific factors 
+\(\alpha > 0\) and \(\beta > 0\) can trade-off region-weighted and
 network-weighted models against each other.
 
-One can read off the formula that decreasing \(\alpha\) leads to less 
-penalization of brain networks and thus to tendentially fully active groups
+Following the formula, decreasing \(\alpha\) leads to less 
+penalization of brain networks and thus the tendency for fully active groups
 and dense brain maps. If at the same time \(\beta\) is increased to 
 induce group sparsity, then only the structure of brain regions encoded
-by \(\mathcal G\) is present. Conversely, if \(\beta\) is chosen 
-sufficiently small, and \(\alpha\) increased,
-then the structure will come from \(\mathcal H\), leading to the
+by \(\mathcal G\) is acknowledged. Conversely, if \(\beta\) is chosen 
+sufficiently small and \(\alpha\) increased,
+the structure will come from \(\mathcal H\), leading to the
 selection of brain networks rather than regions.
@@
 \cite{barch2013}.
-Neuroimaging task data with labels of ongoing cognitive processes
+Neuroimaging task data with labels of ongoing psychological processes
 were drawn from 500

### 2016-02-05 paper/icml2016/example_paper.tex
remove padding

--- 2016-02-05 paper/icml2016/example_paper.tex
@@
 Many quantitative scientific domains underwent a
-recent passage from the classical ``long data" regime to
-the high-dimensional ``wide data" regime.
+recent passage from the classical regime (i.e., ``long data")  to
+the high-dimensional regime (i.e., ``wide data").
 % the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
@@
 \cite{hastie2015statistical}.
-They act as regularizer by encouraging zero coefficients
-in model selection.
+They act as a 
+regularizer and can be used for model selection.
 Sparse supervised and unsupervised
@@
 %
-Moreover, \textit{structured sparsity} can impose
+Generally, \textit{structured sparsity} can impose
 domain knowledge on the 
@@
 \cite{kanwisher2010functional}.
-Conversely, functional integration emphasizes that brain computation
+Conversely, functional integration emphasizes that brain function
 is enabled by a complex interplay between these
@@
 infrastructure
-and global connectivity profiles are thought to go hand-in-hand
-to realize neural processes.
+and unique global connectivity profiles are thought to go hand-in-hand
+to realize brain function.
 %
@@
 For instance,
-single-cell recordings and microscopic tissue examination
+single-cell recordings and microscopic examination
 revealed the
@@
 
-One can read off the formula that decreasing \(\alpha\) leads to less 
+Decreasing \(\alpha\) leads to less 
 penalization of brain networks and thus to tendentially fully active groups

### 2016-02-05 paper/icml2016/example_paper.tex
style up 4

--- 2016-02-05 paper/icml2016/example_paper.tex
@@
 allow constructing a hierarchy of global ICA networks with their
-assigned local cluster regions.
+assigned local cluster regions
+(Figure \ref{fig_priors}).
 The ensuing network-region tree is used as a structural prior
@@
 It is important to note that the above trade-off shows that predominance
-can be either attributed to regions or networks, but that nevertheless the
-penalty structure is hierarchical: If the network penalty layer sets a
+can be either attributed to regions or networks, but that the
+penalty structure is nevertheless hierarchical.
+If the network penalty layer sets a
 network group to zero, then all the contained region groups are forced to
@@
 The prediction problem at hand is a multiclass classification. We choose to
-attack this using one-vs-rest scheme on a binary logistic regression, whose
-loss can be written as
+attack this using one-versus-rest scheme on a binary logistic regression.
+Its loss can be written as
 \[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
@@
 We optimize parameters \(w\) using an iterative forward-backward
-scheme analogous to FISTA for the lasso \cite{beck2009}.
+scheme analogous to the FISTA solver for the lasso \cite{beck2009}.
 
@@
 The stratified and shuffled training data were submitted
-to a nested cross-validation scheme
+to a nested cross-validation (CV) scheme
 for model selection and model assessment.
@@
 \subsection{Implementation}
-All analyses were performed in Python.
+All experiments were performed in Python.
 We used \textit{nilearn} to process and resphape
@@
 \textit{SPAMs} for numerically optimized
-implementations of the sparse estimators
+implementations of the sparse learners
 (\url{http://spams-devel.gforge.inria.fr/}).
@@
 % \paragraph{Data.}
-As the currently biggest openly accessible reference dataset,
-we chose resources from the Human Connectome Project (HCP)
+As the currently biggest open-access dataset,
+we chose brain data from the Human Connectome Project (HCP)
 \cite{barch2013}.
-Neuroimaging task data with labels of ongoing psychological processes
+Neuroimaging data with labels of ongoing psychological processes
 were drawn from 500
-healthy HCP participants (cf. Appendix for details on datasets).
+healthy HCP participants.
 18 HCP tasks 
@@
 % across participants (Table \ref{table_tasks}).
-In sum, the HCP task data incorporated 8650 first-level activity maps
+The HCP data incorporated $n$ = 8650 first-level activity maps
 from 18 diverse paradigms administered to 498 participants (2 removed
 due to incomplete data).
-All maps were resampled to a common $60\times72\times60$ space of
+All maps were warped into a common $60\times72\times60$ space of
 3mm isotropic voxels and gray-matter masked (at least 10\% tissue
 probability).
-The supervised analyses were thus based on labeled HCP task maps with
-79,941 voxels of interest representing z-values in gray matter.
+Hence,
+the present experiments were based on task-labeled HCP maps of neural
+activity with
+$p$ = 79,941 voxels of interest that represent zscored-values in gray matter.
 
@@
 \end{centering}
-\label{fig_sparsities}
+\label{Tab:fig_sparsities}
 \end{figure*}
@@
 in an 18-class scenario
-(Figure \ref{fig_sparsities}).
-%
-Logistic regression with $\ell_1/\ell_2$ block norm penalization
+(Figure 2).
+% (Figure \ref{Tab:fig_sparsities}).
+%
+Logistic regression with $\ell_1/\ell_2$-block-norm penalization
 incorporated a hierarchy of previously known region and network neighborhoods
@@
 %
-Vanilla logistic regression with $\ell_1$-penalization
-does not assume any previously known special structure.
-This classification estimator embraces a vision of neural activity structure
+Vanilla logistic regression with $\ell_1$-penalization and
+$\ell_1$-$\ell_2$-elastic-net penalization
+do not assume any previously known special structure.
+These classification estimators embrace a vision of neural activity structure
 that expects a minimum of
@@
 Logistic regression with (sparse) group sparsity
-imposes a structured $\ell_1/\ell_2$ block norm (with additional $\ell_1$ term)
-with a known atlas of region voxel groups onto the statistical estimation process.
-This supervised estimator shrinks and selects the coefficients
-of topographically compact voxel groups expected to be relevant together.
+imposes a structured $\ell_1/\ell_2$-block norm (with additional $\ell_1$ term)
+with a known region atlas of voxel groups
+onto the statistical estimation process.
+These supervised estimators shrink and select the coefficients
+of topographically compact voxel groups expected to
+be relevant in unison.
 %
@@
 This supervised classification algorithm
-expected a minimum of unknown network patterns
+expected a minimum of unknown ``network'' patterns
 to be relevant.
@@
 (89.7\% multi-class accuracy, mean AUC 94.8 [+/- 9.1 standard deviation]
-mean precision 86.7, mean recall 91.5).
+mean precision 0.87, mean recall 0.92).
 It was closely followed by logistic regression
@@
 (89.4\%, mean AUC 90.8 [+/- 14.8],
-precision 86.4, recall 91.3).
+precision 0.86, recall 0.91).
 Lasso featured an average performance comparing to the other sparse estimators
-(88.60\%, mean AUC 94.3 [+/- 9.3],
-precision 85.7, recall 90.3).
+(88.6\%, mean AUC 94.3 [+/- 9.3],
+precision 0.86, recall 0.90).
 Elastic-Net, in turn, featured an
@@
 (88.1\%, mean AUC 94.1 [+/- 10.2],
-precision 84.8, recall 84.1).
+precision 0.85, recall 0.84).
 Introducing a priori knowledge of brain region compartments
 by sparse group sparsity
-(87.9\%, mean AUC 93.9 [+/- 10.1], precision 84.8, recall 89.5)
+(87.9\%, mean AUC 93.9 [+/- 10.1], precision 0.85, recall 0.90)
 and
 by group sparsity
-(87.9\%, mean AUC 84.7 [+/- 17.3], precision 85.3, recall 90.3)
+(87.9\%, mean AUC 84.7 [+/- 17.3], precision 0.85, recall 0.90)
 performed worst.
-%
+
 In an important subanalysis,
 the gain of the combined region-network prior was also confirmed by
-selectively zeroing the $\eta_g$ coefficients of all region groups
-or all network groups in the hierarchical prior.
+selectively zeroing
+the $\eta_g$ coefficients of all region groups
+or
+the $\eta_h$ coefficients of all network groups in the hierarchical prior.
 Removing region structure from the prior achieved
@@
 87,05\% accuracy.
-These results from partial priors are indeed outperformed
+These results from partial priors were indeed outperformed by
 the full region-network tree prior at 89,67\% accuracy.
@@
 In sum,
-biasing sparse model selection by domain knowledge of region-network hierarchies
+driving sparse model selection by domain knowledge of region-network hierarchies
 outcompeted other types of frequently used sparse penalization techniques.
@@
 }
-\label{fig_dataratio}
+\label{Tab:fig_dataratio}
 \end{centering}
@@
 ($\alpha = 1, \beta = 1$)
-were quantitatively compared (Figure \ref{fig_dataratio}).
-Region-network priors should bias model selection towards more
+was quantitatively compared (Figure \ref{Tab:fig_dataratio}).
+Region-network priors should contrain model selection towards more
 neurobiologically plausible classification estimators.
@@
 %
-The HCP task data with examples from 18
+The HCP data with examples from 18
 psychological tasks were first divided into
 90\% of training set (i.e., 7584 neural activity maps) and
-10\% of test set (i.e., 842 neural activity maps).
+10\% of test set (i.e., 842 maps).
 Both learning algorithms were fitted based on the
@@
 % results: accuracy
-Regarding classification performance on the always same test set,
+Regarding classification performance on the identical test set,
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression

### 2016-02-05 paper/icml2016/example_paper.tex
style up 5

@@
 
-Following the formula, decreasing \(\alpha\) leads to less 
+Decreasing \(\alpha\) leads to less 
 penalization of brain networks and thus the tendency for fully active groups
@@
 \textit{Middle:} These two types of predefined voxel groups are incorporated
-into hierarchical priors of parent networks with their
-descending region nodes.
+into a joint hierarchical prior of parent networks with their
+descending region child nodes.
 \textit{Top to bottom:} Four examplary region-network priors
 are shown, including
-the early cortex that processes
+the early cortices that process
 visual and sound information from the environment,
@@
 Comparison of the performance of logistic regression estimators
-with 6 different structured and unstructered sparsity penalties
+with 6 different structured and unstructered
+sparse regularization terms
 in classifying neural activity from 18 psychological tasks.
-The class-wise area under the curve (AUC, \textit{colors})
-is obtained on an identical test set.
+The area under the curve (AUC, \textit{colors})
+is obtained on an identical test set
+as mean and class-wise measure.
 %
 \textit{Hierarchical Tree Sparsity}: Structured
-$\ell_1/\ell_2$-block-norm with a hierarchy of
-both region and network priors
+$\ell_1/\ell_2$-block norm with a hierarchy of
+region and network priors
 exhibited the best out-of-sample performance
@@
 imposed low-rank structure
-with sparsity of network patterns, but naive to region structure.
+with sparsity of unknown ``network'' patterns,
+but naive to region structure.
 %
@@
 with increasing fraction
-of the available training data (\textit{left to right columns}).
+of the available training data
+to be fitted (\textit{left to right columns}).
 For one example (i.e., ``View tools'') from 18 psychological tasks,
@@
 (\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-The support recovery of that exemplary task is given
-as Pearson correlation (cf. methods).
+The support recovery of that exemplary class is given
+as Pearson correlation $\rho$ (cf. results).
 %
 In the data-scarce scenario,
-typical for brain imaging,
+ubiquitous in brain imaging studies,
 hierarchical tree sparsity achieves much
@@
 and
-the zscored sample maps for each class.
+the zscored average sample maps for each class.
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
-achieved a mean $\rho$ (+/- standard deviation) recovery of
+achieved a mean correlation $\rho$ (+/- standard deviation) of
 0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
@@
 0.16 (+/- 0.04) versus 0.22 (+/- 0.05), and
-0.19 (+/- 0.05) versus 0.29 (+/- 0.06)
+0.19 (+/- 0.05) versus 0.29 (+/- 0.06) across classes
 based on 20\% to 100\% training data.
@@
 Three observations have been made.
-In the data-scarce scenario (i.e., 1/5 of available training data),
+First,
+in the data-scarce scenario (i.e., 1/5 of available training data),
 hierarchical tree sparsity achieved the biggest advantage
-in out-of-sample performance by 5,11\% as well as
+in out-of-sample performance by 5,1\% as well as
 better support recovery with weight maps already much closer
-to the class averages
+to the respective class averages
 \cite{varoquaux2012small}.
@@
 %
-Across training data fractions,
+Second,
+across training data fractions,
 the weight maps from ordinary logistic regression exhibited
@@
 this observation is likely to reflect instable selection of
-representatives among class-responsive predictor groups
+representative voxels among class-responsive predictor groups
 due to the $\ell_1$-norm penalization.
 %
-In the data-rich scenario (i.e., entire training data used for model fitting),
+Third,
+in the data-rich scenario (i.e., entire training data used for model fitting),
 neurobiologically informed logistic regression
-profited more from the increased information quantities than
+profited much more from the increased information quantities than
 neurobiologically naive logistic regression.
-That is, the region-network priors actually further enhance the similarity
-to the weight maps even in abundant input data.
+That is, the region-network priors actually further enhanced the support
+recovery even in abundant input data.
 This was the case although
@@
 In contrast, 
-the unstructured estimator reached this generalization performance
+the unstructured estimator approached this generalization performance
 only with bigger input data quantities.
@@
 (\textit{right columns}).
-Among the 18 classes, the model weights are shown for the psychological
+Among the 18 classes, the model weights are shown for 5 exemplary
+psychological
 tasks (\textit{from top to bottom}): tongue movement, listening stories,
@@
 %
-Different emphasis on regions versus networks
+First,
+different emphasis on regions versus networks
 in hierarchical structured sparsity can
@@
 %
-Favoring region versus network structure during model selection
+Second,
+favoring region versus network structure during model selection
 recovers complementary aspects of the neural activity pattern.
 %
-Equal region and network emphasis yields more dispersed,
+Third,
+equal region and network emphasis yields more dispersed,
 less interpretable model choices.
@@
 Finally, the relative importance of the
-region and network priors within the hierarchical tree prior
+region and network group penalties within the hierarchical tree prior
 was quantified (Figure \ref{fig_regnetratio}).
@@
 region-network ratio, while the
-group weight $\eta_g$ of network priors was divided by that
+group weight $\eta_h$ of network priors was divided by that
 region-network ratio. For instance, a region-network ratio of 3
@@
 and multiplying
-$\alpha = \frac{1}{3}$ to $\eta_g$ of all network group penalties
+$\alpha = \frac{1}{3}$ to $\eta_h$ of all network group penalties
 (Table \ref{table_reg_net_ratio}).
@@
 a range between region-dominant and network-dominant structured penalties
-yielded quantitatively almost identical generalization to new data
+yielded quantitatively similar generalization to new data
 but qualitatively different decision functions manifested in the weight maps
@@
 that set less voxel coefficients to zero and spread the
-probability mass with lower absolute coefficients across the whole brain
+probability mass across the whole brain
+with lower absolute coefficients
 (Figure \ref{fig_regnetratio}, third column in the middle).
@@
 overly strong emphasis on either level of the hierarchical prior
-can yield the neurobiologically informative results with maps
+provides the neurobiologically informative results with maps
 of the most necessary region or network structure for
-statistically significant out-of-sample performance
+statistically significant generalization
 (Figure \ref{fig_regnetratio}, leftmost and rightmost columns).
@@
 stratifying the hierarchical tree penalty between region and network emphasis
-suggests that \textit{class-specific region-network weights}
+suggests that \textit{class-specific region-network tradeoffs}
 might offer more performant and more interpretable classification models
@@
 orchestrating its region nodes.
-This suggests hierarchical statistical models
-as an underexploited opportunity for imaging imaging analysis.
+It suggests hierarchical statistical models
+as an underexploited opportunity for neuroimaging analysis.
 %
 This proof-of-concept study demonstrates the simultaneous exploitation of
-both these neurobiological compartments
+both neurobiological compartments
 for sparse variable selection and high-dimensional prediction
@@
 %
-This statistically and neurobiologically desirable bias
+This statistically and neurobiologically desirable simplification
 is shown to enhance
-both model interpretability and generalization performance,
-although these statistical-learning goals are typically in conflict.
+model interpretability and generalization performance,
+although these two goals are typically in conflict
+\cite{hastie2015statistical}.
 
@@
 the neuroimaging data to harness the curse of dimensionality.
-They often use preliminary pooling functions within regions
+They often resort to preliminary pooling functions within regions
 or regression against network templates
 for subsequent supervised learning on the aggregated feature space.
-Such lossy approaches divided into feature engineering and inference steps
+Such lossy approaches of
+feature engineering and subsequent inference
 \textit{i)} can only satisfy the specialization or

### 2016-02-05 paper/icml2016/example_paper.tex
style up 6

@@
 and
-\textit{iii)} cannot issue individual coefficients for every brain voxels.
+\textit{iii)} cannot issue individual coefficients for every brain voxel.
 %
@@
 by estimating individual voxel contributions
-while benefitting from their functional segregation and integration
+while benefitting from their biological multi-level stratification
 to restrict statistical complexity.
@@
 Viewed from the bias-variance tradeoff,
-our modification to logistic regression estimators
+our modification to logistic regression
 entailed a large decrease in model variance but only a modest
@@
 this entailed a healthy decrease in the complexity capacity of the prediction model
-with a higher chance of generalizing to unobserved data.
+with a higher chance of extrapolating to unobserved data samples.
 
@@
 This includes supervised methods for whole-brain classification and regression
-with one or several target variables.
+in single- and multi-task learning settings.
 The principled regularization scheme could inform
@@
 Additionally,
-model regularization by hierarchical structured sparsity could be extended
-from the spatial domain of neural activity to
+hierarchical regularization could be extended
+from the spatial activity domain to
 priors of coherent spatiotemporal activity structure
@@
 sparse selection of overcomplete region-network dictionaries.
-Non-hierarchical penalty terms will probably allow for
+Advanced but non-hierarchical penalty terms will probably allow for
 more complex structured sparsity that
-extend the recently enabled parent-children dependencies.
+go beyond the recently enabled parent-children dependencies.
 %
@@
 successful high-dimensional inference is
-an important prerequisite
+a prerequisite
 for predicting diagnosis,

### 2016-02-05 paper/icml2016/example_paper.tex
add model variance results

@@
 % results: support recovery
-Finally, the support recovery was quantified by
+Regarding the support recovery, we computed
 Pearson correlation $\rho$ between vectors of
@@
 based on 20\% to 100\% training data.
+% results: model variance
+Finally, regarding model variance,
+we quantified the agreement between
+$\ell_1$-penalized versus hierarchical-tree-penalized
+model weights after fitting
+on 5 different 20\%-subsamples of the training data.
+For each classifier,
+the absolute model weights were concatenated for all 18 classes,
+thresholded at 0.0001 to binarize variable selection,
+and mutual information was computed on all pairs
+of the 5 trained models.
+This agreement metric of model selection across fold pairs
+yielded the means 0.001 ($\ell_1$) versus 0.506 (Hierarchical Tree).
 

### 2016-02-05 srne_model_variance.py

@@ -1,0 +1,125 @@
+import struct_estimator_dataratio_zerobrainlevel_weighted
+
+import os.path as op
+import numpy as np
+import matplotlib.pyplot as plt
+from sklearn.preprocessing import StandardScaler
+import joblib
+
+n_classes = 18
+plt.close('all')
+REGS = ['tree-l2', 'l1']
+
+READ_DIR = '/git/srne/srne_benchmark_dataratioFIXED100_zerobrainlevel_weighted/'
+coeffs_ref = {}
+for reg in REGS:
+    coeffs_ref[reg] = []
+    cur_dmp = op.join(READ_DIR, '%s_dataratio100_maxit100' % reg)
+    print(cur_dmp)
+    clf = joblib.load(cur_dmp)
+    coef_ = np.array([est.W_.ravel() for est in clf.best_estimator_.estimators_]).T
+    coeffs_ref[reg].append(coef_.ravel())
+    coeffs_ref[reg] = np.array(coeffs_ref[reg]).squeeze()
+
+READ_DIR = '/git/srne/srne_benchmark_dataratioFIXED20_zerobrainlevel_weighted/'
+coeffs = {}
+for reg in REGS:
+    coeffs[reg] = []
+    for i_fold in range(5):  # per fold
+        cur_dmp = op.join(READ_DIR, '%s_dataratio20_maxit100' % reg)
+        if i_fold > 0:
+            cur_dmp += '_fold%i' % (i_fold + 1)
+        print(cur_dmp)
+        clf = joblib.load(cur_dmp)
+        coef_ = np.array([est.W_.ravel() for est in clf.best_estimator_.estimators_]).T
+        coeffs[reg].append(coef_.ravel())
+    coeffs[reg] = np.array(coeffs[reg])
+
+# coeffs_ss = coeffs.copy()
+# for reg in REGS:
+#     coeffs_ss[reg] = ss.fit_transform(coeffs_ss[reg].T).T
+
+for reg in REGS:
+    print('Variance of %s: %.2f' % (reg,
+        np.abs(coeffs[reg]).var(axis=0).sum()))
+
+def dice_coefficient(a,b):
+    if not len(a) or not len(b): return 0.0
+    """ quick case for true duplicates """
+    # if a == b: return 1.0
+    """ if a != b, and a or b are single chars, then they can't possibly match """
+    if len(a) == 1 or len(b) == 1: return 0.0
+    
[…]

### 2016-02-05 paper/icml2016/example_paper.tex
interm

@@
 The hierarchical tree penalties recently suggested for imaging neuroscience
-\cite{jenatton2011multi} will be extended
-by introducing neurobiologically plausible region and network priors
+\cite{jenatton2011multi} will be revisited to
+introduce neurobiologically plausible region and network priors
 to design neuroscience-specific classifiers.
@@
 the network groups that contain all
-the voxels of the brain regions associated to them.
+the voxels of the brain regions associated with them.
 Each network node in turn descends into a second hierarchical level of
@@
 (number of maximal iterations=$100$, tolerance=$0.001$).
-{\color{red} In the outer CV layer, grid search
+In the outer CV layer, grid search
 selected among candidates for the respective $\lambda$ parameter
-by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.}
+by searching between $10^{-2}$ and $10^{1}$ in 9 steps on a logarithmic scale.
 Importantly, the thus selected sparse logistic regression classifier was
@@
 %% The intercept $b$ is left unregularized
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.8\textwidth]{../figures/reg_net_prior_colin.pdf}
+\vspace{-0.2cm}
+\caption{\textbf{Building blocks of the region-network tree.}
+Neurobiological priors introduced into the classification problem 
+by hierarchical structured sparsity are displayed.
+\textit{Left:} Continuous, partially overlapping brain network priors
+(\textit{hot-colored}, taken from \cite{smith2009})
+accommodate the functional integration
+perspective of brain organization.
+\textit{Right:} Discrete, non-overlapping brain region priors
+(\textit{single-colored}, taken from \cite{crad12})
+accommodate the functional segregation perspective.
+\textit{Middle:} These two types of predefined voxel groups are incorporated
+into a joint hierarchical prior of parent networks with their
+descending region child nodes.
+\textit{Top to bottom:} Four examplary region-network priors
+are shown, including
+the early cortices that process
+visual and sound information from the environment,
+a well-known attentional circuit in the left brain hemisphere,
+and
+the cerebellum that is involved in motor behavior.
+}
+\label{fig_priors}
+\end{figure*}
+
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
+%\vspace{-0.6cm}
+\caption{\textbf{Naive versus informed sparse model selection
+across training set sizes.}
+Ordinary $\ell_1$-penalized logistic regression
+(\textit{upper row})
+is compared
+to hierarchical-tree-penalized logistic regression
+($\alpha = 1, \beta = 1$, \textit{lower row})
+with increasing fraction
+of the available training data
+to be fitted (\textit{left to right columns}).
+For one example (i.e., ``View tools'') from 18 psychological tasks,
+unthresholded axial maps of model weights
+are shown for comparison against
+the sample average of that class
+(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
+The support recovery of that exemplary class is given
+as Pearson correlation $\rho$ (cf. results).
+%
+In the data-scarce scenario,
+ubiquitous in brain imaging studies,
+hierarchical tree sparsity achieves much
+better support recovery.
+% with the biggest difference
+% in model performance (83.7\% versus 89.0\%).
+%
+In the data-rich scenario,
+neurobiologically informed logistic regression
+profits more from the available information quantities than
+neurobiologically naive logistic regression.
+}
+\label{Tab:fig_dataratio}
+\end{centering}
+\end{figure*}
 
@@
 \begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{../figures/reg_net_prior_colin.pdf}
-\vspace{-0.2cm}
-\caption{\textbf{Building blocks of the region-network tree.}
-Neurobiological priors introduced into the classification problem 
-by hierarchical structured sparsity are displayed.
-\textit{Left:} Continuous, partially overlapping brain network priors
-(\textit{hot-colored}, taken from \cite{smith2009})
-accommodate the functional integration
-perspective of brain organization.
-\textit{Right:} Discrete, non-overlapping brain region priors
-(\textit{single-colored}, taken from \cite{crad12})
-accommodate the functional segregation perspective.
-\textit{Middle:} These two types of predefined voxel groups are incorporated
-into a joint hierarchical prior of parent networks with their
-descending region child nodes.
-\textit{Top to bottom:} Four examplary region-network priors
-are shown, including
-the early cortices that process
-visual and sound information from the environment,
-a well-known attentional circuit in the left brain hemisphere,
-and
-the cerebellum that is involved in motor behavior.
-}
-\label{fig_priors}
-\end{figure*}
-
-\begin{figure*}
 \begin{centering}
@@
 that expects a minimum of
-topographically and functionally independent brain voxel to be relevant.
+topographically and functionally independent brain voxels to be relevant.
 %
@@
 Removing region structure from the prior achieved
-88,84\% accuracy,
+88,8\% accuracy,
 while removing network structure from the prior achieved
-87,05\% accuracy.
+87,1\% accuracy.
 These results from partial priors were indeed outperformed by
-the full region-network tree prior at 89,67\% accuracy.
+the full region-network tree prior at 89,7\% accuracy.
 %
@@
 outcompeted other types of frequently used sparse penalization techniques.
-
-\begin{figure*}
-\begin{centering}
-\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
-%\vspace{-0.6cm}
-\caption{\textbf{Naive versus informed sparse model selection
-across training set sizes.}
-Ordinary $\ell_1$-penalized logistic regression
-(\textit{upper row})
-is compared
-to hierarchical-tree-penalized logistic regression
-($\alpha = 1, \beta = 1$, \textit{lower row})
-with increasing fraction
-of the available training data
-to be fitted (\textit{left to right columns}).
-For one example (i.e., ``View tools'') from 18 psychological tasks,
-unthresholded axial maps of model weights
-are shown for comparison against
-the sample average of that class
-(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-The support recovery of that exemplary class is given
-as Pearson correlation $\rho$ (cf. results).
-%
-In the data-scarce scenario,
-ubiquitous in brain imaging studies,
-hierarchical tree sparsity achieves much
-better support recovery with the biggest difference
-in model performance (83.7\% versus 89.0\%).
-%
-In the data-rich scenario,
-neurobiologically informed logistic regression
-profits more from the available information quantities than
-neurobiologically naive logistic regression.
-}
-\label{Tab:fig_dataratio}
-\end{centering}
-\end{figure*}
 
@@
 %
+\begin{table*}[]
+\centering
+\caption{Out-of-sample performance by region-network emphasis}
+\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
+\textbf{Reg-Net Ratio} & 500 & 100  & 50   & 10   & 5    & 2    & 1    & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ & $\frac{1}{250}$ & $\frac{1}{500}$ & $\frac{1}{1000}$ \\ \hline
+\textbf{Accuracy {[}\%{]}}      & 3.8          & 41.7 & 63.7 & 89.9 & 89.9 & 88.5 & 87.9 & 87.9 & 87.9 & 87.8 & 88.6 & 87.8  & 85.6  & 67.2  & 39,3  
+\end{tabular}
+\label{table_reg_net_ratio}
+\end{table*}
+%
 \subsection{Support recovery as a function of region-network emphasis}
@@
 (Table \ref{table_reg_net_ratio}).
-
-\begin{table*}[]
-\centering
-\caption{Out-of-sample performance by region-network emphasis}
-\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
-\textbf{Reg-Net Ratio} & 500 & 100  & 50   & 10   & 5    & 2    & 1    & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ & $\frac{1}{250}$ & $\frac{1}{500}$ & $\frac{1}{1000}$ \\ \hline
-\textbf{Accuracy {[}\%{]}}      & 3.8          & 41.7 & 63.7 & 89.9 & 89.9 & 88.5 & 87.9 & 87.9 & 87.9 & 87.8 & 88.6 & 87.8  & 85.6  & 67.2  & 39,3  
-\end{tabular}
-\label{table_reg_net_ratio}
-\end{table*}
 

### 2016-02-05 paper/icml2016/example_paper.tex
gaels comments

@@
 logistic-regression to distinguish neural activity.
-This recombines neurobiological architectures underlying
+These priors bridge two levels of neurobiological architecture 
+that are studied separately in neuroscientific research:
 functional segregation into brain regions and
 functional integration by brain networks
-that are studied separately in neuroscientific research.
 %
@@
 than other sparse estimators.
-Weighing the relative importance of
+Varying the relative importance of
 region and network structure within the hierarchical tree penalty
@@
 Many quantitative scientific domains underwent a
-recent passage from the classical ``long data" regime to
+recent shift from the classical ``long data" regime to
 the high-dimensional ``wide data" regime.
 % the high-dimensional regime (i.e., ``wide data") \cite{jordan2015massive}.
-Also in the brain imaging domain,
+In the brain imaging domain,
 many contemporary methods for acquiring brain signals yield
@@
 \cite{bach2012optimization}.
-Such restrictions to statistical complexity
+Such restrictions to model complexity
 are an attractive plan of attack
@@
 % INTEGRAL
-It is more recent
-that the main interpretational focus has shifted
+More recently,
+the main interpretational focus has shifted
 from circumscribed regions to network stratifications
@@
 previously published region definitions obtained from
-spatially constrained ward clustering \cite{crad12}
+spatially constrained spectral clustering \cite{crad12}
 allow constructing a hierarchy of global ICA networks with their
@@
 The goal is to estimate a good predictor of psychological task
-given single brain images. Let the set \(\mathcal X\in\R^{nxp}\) represent brain
+given single brain images. Let the set \(\mathcal X\in\R^{n \times p}\) represent brain
 images of \(p > 0\) voxels.
@@
 ($\alpha = 1, \beta = 1$)
-was quantitatively compared (Figure \ref{Tab:fig_dataratio}).
+was empirically estimated and quantitatively compared
+(Figure \ref{Tab:fig_dataratio}).
 Region-network priors should contrain model selection towards more

### 2016-02-05 paper/icml2016/example_paper.tex
z-scored

@@
 activity with
-$p$ = 79,941 voxels of interest that represent zscored-values in gray matter.
+$p$ = 79,941 voxels of interest that represent z-scored-values in gray matter.
 
@@
 Pearson correlation $\rho$ between vectors of
-the zscored model coefficients
+the z-scored model coefficients
 and
-the zscored average sample maps for each class.
+the z-scored average sample maps for each class.
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression

### 2016-02-05 paper/icml2016/example_paper.tex
some corrcetions on parts 1, 2

@@
 in contrast to methods examining regional specialization.
+% XXX are the compartments overlapping or not ?
 
@@
 the brain's grey matter into local voxel groups
-using clustering algorithisms
+using clustering algorithms
 \cite{cbp2015review}.
@@
 all voxels to be active. Selecting higher penalties on the networks then
-leads to a selection of networks with all regions associated to it.
+leads to a selection of networks with all regions associated with it.
 %
@@
 The support recovery of that exemplary class is given
-as Pearson correlation $\rho$ (cf. results).
+as Pearson correlation $r$ (cf. results).
 %
@@
 Regarding the support recovery, we computed
-Pearson correlation $\rho$ between vectors of
+Pearson correlation $r$ between vectors of
 the z-scored model coefficients
@@
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
-achieved a mean correlation $\rho$ (+/- standard deviation) of
+achieved a mean correlation $r$ (+/- standard deviation) of
 0.10 (+/- 0.03) versus 0.13 (+/- 0.04),

### 2016-03-25 paper/icml2016/example_paper.tex
A small fix
rebuttal

--- 2016-02-05 paper/icml2016/example_paper.tex
@@
 functional segregation into brain regions and
-functional integration by brain networks
+functional integration by brain networks.
 %
@@
 % study
-Building on these two major interpretational traditions in neuroscience,
+Building on these two
+separate major interpretational traditions in neuroscience,
 the present study proposes to incorporate
@@
 The hierarchical tree penalties recently suggested for imaging neuroscience
-\cite{jenatton2011multi} will be revisited to
+\cite{jenatton2012multi} will be revisited to
 introduce neurobiologically plausible region and network priors
@@
 We capitalize on hierarchical group lasso as recently introduced
-\cite{jenatton2011multi} to create a set of convex penalty terms.
+\cite{jenatton2012multi} to create a set of convex penalty terms.
 These allow acknowledging the interplay between local specialization and 
@@
 hierarchical sparsity penalty terms
-\cite{jenatton2011multi}.
+\cite{jenatton2012multi}.
 It extends the group lasso
@@
 %% 
-%% \cite{jenatton2011multi}
+%% \cite{jenatton2012multi}
 %% 

### 2016-03-25 paper/icml2016/example_paper.tex

--- 2016-02-05 paper/icml2016/example_paper.tex
@@
 this observation is likely to reflect instable selection of
-representative voxels among class-responsive predictor groups
+representative voxels among class-responsive groups
 due to the $\ell_1$-norm penalization.

### 2016-05-09 paper/nips2016/paper.tex
created NIPS version

--- 2016-03-25 paper/icml2016/example_paper.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%% ICML 2016 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Use the following line _only_ if you're still using LaTeX 2.09.
-%\documentstyle[icml2016,epsf,natbib]{article}
-% If you rely on Latex2e packages, like most moden people use this:
-\documentclass{article}
-
-% use Times
-\usepackage{times}
-% For figures
-\usepackage{graphicx} % more modern
-%\usepackage{epsfig} % less modern
-\usepackage{subfigure}
-
-% For citations
-\usepackage{natbib}
-
-% For algorithms
-\usepackage{algorithm}
-\usepackage{algorithmic}
-
-% As of 2011, we use the hyperref package to produce hyperlinks in the
-% resulting PDF.  If this breaks your system, please commend out the
-% following usepackage line and replace \usepackage{icml2016} with
-% \usepackage[nohyperref]{icml2016} above.
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e,times}
 \usepackage{hyperref}
-
-% Packages hyperref and algorithmic misbehave sometimes.  We can fix
-% this with the following command.
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-% Employ the following version of the ``usepackage'' statement for
-% submitting the draft version of the paper for review.  This will set
-% the note in the first column to ``Under review.  Do not distribute.''
-\usepackage{icml2016}
-
-% Employ this version of the ``usepackage'' statement after the paper has
-% been accepted, when creating the final version.  This will set the
-% note in the first column to ``Proceedings of the...''
-% \usepackage[accepted]{icml2016}
-
+\usepackage{url}
+\usepackage{amsmath,amsfonts,amsthm}
+\usepackage{bbm}
+\usepackage{algorithm,algorithmic}
+\usepackage{graphicx}
+\usepackage{bm}
+\usepackage{bbm}
+\usepackage[titletoc]{appendix}
+\usepackage{wrapfig}
+\usepackage{afterpage}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage{ulem}
 \usepackage{multirow}
-\usepackage{amsmath,amsfonts,amsthm}
-\usepackage{amssymb}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
+
+\def\B#1{\bm{#1}}
+%\def\B#1{\mathbf{#1}}
+\def\trans{\mathsf{T}}
+
+%\renewcommand{\labelitemi}{--}
+
+\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{remark}{Remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{Hierarchical Region-Network Sparsity for\\
+High-Dimensional Inference in Brain Imaging}
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+\DeclareMathOperator{\proj}{proj}
+\DeclareMathOperator{\softmax}{softmax}
 \DeclareMathOperator{\prox}{prox}
+\DeclareMathOperator{\Prox}{Prox}
+\DeclareMathOperator{\im}{im}
+
+% macros from michael's .tex
+\DeclareMathOperator{\dist}{dist} % The distance.
+\DeclareMathOperator{\argmin}{argmin}
+\DeclareMathOperator{\argmax}{argmax}
 \DeclareMathOperator{\Id}{Id}
-
+\DeclareMathOperator{\abs}{abs}
 \newcommand{\R}{\mathbb{R}}
-
-% The \icmltitle you define below is probably too long as a header.
-% Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Informing High-Dimensional Inference in Neuroimaging}
+\newcommand{\N}{\mathbb{N}}
+\newtheorem{thm}{Theorem}[section]
+\newtheorem{prop}[thm]{Proposition}
+\newtheorem{lem}[thm]{Lemma}
+\newtheorem{cor}[thm]{Corollary}
+
+\newcommand{\suggestadd}[1]{{\color{blue} #1}}
+\newcommand{\suggestremove}[1]{{\color{red} \sout{#1}}}
+
+% \nipsfinalcopy % Uncomment for camera-ready version
+% \nipsfinaltrue
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\twocolumn[
-\icmltitle{Hierarchical Region-Network Sparsity for\\
-High-Dimensional Inference in Brain Imaging}
-% \icmltitle{Region-Network Hierarchical Sparsity Priors for\\
-% High-Dimensional Inference in Brain Imaging}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the icml2016
-% package.
-\icmlauthor{Danilo Bzdok}{danilo.bzdok@inria.fr}
-\icmladdress{Department of Psychiatry, Psychotherapy and Psychosomatics, RWTH Aachen, Germany\\
-  Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
-\icmlauthor{Michael Eickenberg}{Michael.Eickenberg@normalesup.org}
-\icmladdress{Department d'Informatique, Ecole Normale Superieure, Paris}
-\icmlauthor{Ga\"el Varoquaux}{gael.varoquaux@inria.fr}
-\icmlauthor{Bertrand Thirion}{bertrand.thirion@inria.fr}
-\icmladdress{Parietal, INRIA, NeuroSpin, bat 145, CEA, 91191 Gif-sur-Yvette France}
-
-% You may provide any keywords that you 
-% find helpful for describing your paper; these are used to populate 
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Sparsity-inducing norms, hierarchical tree sparsity,
-numerical optimization,
-systems neuroscience,
-functional specialization, functional integration}
-
-\vskip 0.3in
-]
+\maketitle
+
+\author{Danilo Bzdok, Michael Eickenberg,
+Ga\"el Varoquaux, Bertrand Thirion\\
+INRIA, Parietal team, Saclay, France\\
+CEA, Neurospin, Gif-sur-Yvette, France\\
+firstname.lastname@inria.fr}
 
@@
   generalization performance, sample complexity, and domain interpretability.
+%
+
+% OUR keywords
+%\textbf{\\keywords}: curse of dimensionality; semi-supervised learning;
+%fMRI; systems neuroscience
+
+% official NIPS keywords
+\textbf{\\keywords}: Sparsity-inducing norms, hierarchical tree sparsity,
+numerical optimization, systems neuroscience,
+functional specialization, functional integration
 
@@
 statistical relationships that can be readily
-estimated, reproduced, and interpreted
-\cite{giraud2014introduction}.
+estimated, reproduced, and interpreted.
 %
@@
 from circumscribed regions to network stratifications
-in systems neuroscience \cite{yuste2015}.
+in systems neuroscience.
 %
@@
 by hierarchical structured sparsity.
-% The "true" relative importance of 
-% local region compartments and global network compartments
-% is typically unknown
-% but
-% probably varying in degree
-% across diverse neuroscientific questions.
+That is, every variable carrying brain signals
+will be a-priori assigned to both region and network compartments to
+improve model fitting based on existing domain knowledge.
 %
@@
 using clustering algorithms
-\cite{cbp2015review}.
+\cite{crad12}.
 Consequently,
@@
 attack this using one-versus-rest scheme on a binary logistic regression.
+The one-versus-rest classification strategy is
+chosen to obtain one weight map per class for display and model diagnostics.
 Its loss can be written as
@@
 }
+\vspace{-0.4cm}
 \label{fig_priors}
@@
 \includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
-%\vspace{-0.6cm}
+\vspace{-0.2cm}
 \caption{\textbf{Naive versus informed sparse model selection
@@
 }
+\vspace{-0.4cm}
 \label{Tab:fig_dataratio}
@@
 were selected that are known to elicit reliable neural activity
-across participants.
+across participants
+(see appendix for detailed descriptions of dataset and tasks).
 % across participants (Table \ref{table_tasks}).
@@
 % \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
-\includegraphics[width=0.55\textwidth]{../figures/ROC_ALL.png}
-\vspace{-0.4cm}
+\includegraphics[width=0.60\textwidth]{../figures/ROC_ALL.png}
+\vspace{-0.6cm}
 \caption{\textbf{Prediction performance across sparsity priors.}
@@
 \end{centering}
+\vspace{-0.4cm}
 \label{Tab:fig_sparsities}
@@
 to be relevant.
+
 %
@@
 
-Across analyses,
+Across experiments with stratified and shuffled
+cross-validation (90\%/10\% train/test set) across pooled subject data,
 hierarchial tree sparsity was most successful
@@
 and
-the z-scored average sample maps for each class.
+the z-scored across-participant average maps for each class.
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
@@
 \begin{centering}
-\includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin.pdf}
-%\vspace{-0.6cm}
+\includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin2.pdf}
+%
 \caption{\textbf{Support recovery as a function of
@@
 (i.e., $\alpha$ and $\beta$ are changed reciprocally).
-This region-network ratio (\textit{upper fractions}) weighted voxel groups
+Horizontal brain slices are shown with the voxel-wise weights for each class
+from the fitted predictive model.
+The region-network ratio (\textit{columns}) weighted voxel groups
 to priviledge sparse models in function space
@@
 psychological
-tasks (\textit{from top to bottom}): tongue movement, listening stories,
+tasks followed by participants lying in a brain imaging scanner
+(\textit{from top to bottom}): tongue movement, listening to stories,
 taking somebody else's perspective (ToM, "theory of mind"),
@@
 in hierarchical structured sparsity can
-yield comparable model performance.
+yield very similar out-of-sample generalization.
 %
@@
 favoring region versus network structure during model selection
-recovers complementary aspects of the neural activity pattern.
+recovers complementary, non-identical aspects of
+the neural activity pattern underlying the psychological tasks.
 %
 Third,
-equal region and network emphasis yields more dispersed,
+equal emphasis on region versus network neighborhoods in the
+high-dimensional neuroimaging data yields more dispersed,
 less interpretable model choices.
@@
 \end{figure*}
-%
-\begin{table*}[]
-\centering
-\caption{Out-of-sample performance by region-network emphasis}
-\begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
-\textbf{Reg-Net Ratio} & 500 & 100  & 50   & 10   & 5    & 2    & 1    & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ & $\frac{1}{250}$ & $\frac{1}{500}$ & $\frac{1}{1000}$ \\ \hline
-\textbf{Accuracy {[}\%{]}}      & 3.8          & 41.7 & 63.7 & 89.9 & 89.9 & 88.5 & 87.9 & 87.9 & 87.9 & 87.8 & 88.6 & 87.8  & 85.6  & 67.2  & 39,3  
-\end{tabular}
-\label{table_reg_net_ratio}
-\end{table*}
 %
@@
 can similarly extrapolate to unseen neural activity maps.
+%
+\begin{table*}[]
+  \centering
+  \caption{Out-of-sample performance by region-network emphasis}
+  \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
+    \textbf{Region-Network Ratio}          & 100   & 50    & 10   & 5     & 2    & 1     & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ \\ \hline
+    \textbf{Accuracy {[}\%{]}}             & 89.7  & 89.9  & 90.1 & 90.5  & 88.0 & 89.7  & 87.8           & 88.0           & 87.7           & 88.4           & 88.1  
+  \end{tabular}
+  \vspace{-0.6cm}
+  \label{table_reg_net_ratio}
+\end{table*}
+%
 Second,
@@
 % \bibliographystyle{plainnat}
-\bibliographystyle{icml2016}
 \bibliography{../paper_refs}
-% \bibliography{paper_refs}
+\bibliographystyle{splncs03}
+
+\newpage
+\section{Appendix}
+%
+\paragraph{Data.}
+As the currently biggest openly-accessible reference dataset,
+we chose the Human Connectome Project (HCP) resources
+(Barch et al., 2013).
+Neuroimaging task data with labels of ongoing cognitive processes
+were drawn from 500
+healthy HCP participants.
+18 HCP tasks 
+were selected that are known to elicit reliable neural activity
+across participants.
+The task paradigms include
+1) working memory/cognitive control processing, 2)
+incentive processing, 3) visual and somatosensory-motor processing,
+4) language processing (semantic and phonological processing),
+5) social cognition, 6) relational processing, and 7) emotional
+processing. All data were acquired on the same Siemens Skyra 3T scanner.
+Whole-brain EPI acquisitions were acquired with a
+32 channel head coil (TR=720ms, TE=33.1ms, flip angle=52°, BW=2290Hz/Px,
+in-plane FOV=$280\textrm{mm}\times180\textrm{mm}$, 72 slices, 2.0mm 
+isotropic voxels).
+The ``minimally preprocessed'' pipeline includes
+gradient unwarping, motion correction, fieldmap-based EPI distortion
+correction, brain-boundary-based registration of EPI to structural
+T1-weighted scans, nonlinear (FNIRT) registration into MNI space,
+and grand-mean intensity normalization. Activity maps were spatially
+smoothed with a Gaussian kernel of 4mm (FWHM). A GLM was
+implemented by FILM from the FSL suite with model regressors from convolution
+with a “canonical” hemodynamic response function and from temporal derivatives.
+HCP tasks were conceived to modulate activity
+in a maximum of different brain regions and neural systems. Indeed, at
+least 70\% of the participants showed consistent brain activity in
+contrasts from the task battery, which certifies excellent
+activity patterns covering extended parts of the brain (Barch et al., 2013).
+%
+In sum, the HCP task data incorporated 8650 first-level activity maps
+from 18 diverse paradigms administered to 498 participants (2 removed
+due to incomplete data).
+All maps were resampled to a common 60x72x60 space of
+3mm isotropic voxels and gray-matter masked (at least 10\% tissue
+probability).
+The supservised analyses were based on labeled HCP task maps with
+79,941 voxels of interest representing z-values in gray matter.
+
+\begin{table}[h]
+  \resizebox{0.98\textwidth}{!}{%
+  \begin{tabular}{l|l|l}
+    \hline
+  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
+  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
+  2 Punish             &                                       &                                                                                   \\ \hline
+  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
+  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
+  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
+  6 Theory of mind     &                                       &                                                                                   \\ \hline
+  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
+  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
+  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
+  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
+  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
+  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
+  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
+  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
+  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
+  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
+  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
+  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
+  \end{tabular}
+}
+\vspace{-0.2cm}
+\caption{\textbf{Description of psychological tasks to predict.}}
+\label{table_tasks}
+\end{table}
 
 \end{document}
-
-% This document was modified from the file originally made available by
-% Pat Langley and Andrea Danyluk for ICML-2K. This version was
-% created by Lise Getoor and Tobias Scheffer, it was slightly modified  
-% from the 2010 version by Thorsten Joachims & Johannes Fuernkranz, 
-% slightly modified from the 2009 version by Kiri Wagstaff and 
-% Sam Roweis's 2008 version, which is slightly modified from 
-% Prasad Tadepalli's 2007 version which is a lightly 
-% changed version of the previous year's version by Andrew Moore, 
-% which was in turn edited from those of Kristian Kersting and 
-% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2016-05-09 paper/nips2016/build_paper.sh

@@ -1,0 +1,27 @@
+#!/usr/bin/env bash
+
+# rm -rf $(biber --cache)
+rm *.aux
+rm *.bcf
+rm *.bbl
+rm *.blg
+rm *.ist
+rm *.alg
+rm *.acr
+rm *.acn
+rm *.glsdefs
+rm *.out
+rm *.lot
+rm *.log
+rm *.lof
+rm *.toc
+rm *.run.xml
+rm *.synctex.gz
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 paper.tex
+
+bibtex paper
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 paper
+pdflatex -interaction=nonstopmode -file-line-error-style -synctex=1 paper
+# makeindex -s paper.idx -t paper.glsdef -o paper.acr paper.acn
+makeglossaries paper
+pdflatex -interaction=nonstopmodxe -file-line-error-style -synctex=1 paper

### 2016-05-14 paper/nips2016/paper.tex
integrated comments for NIPS

@@
 % \nipsfinalcopy % Uncomment for camera-ready version
-% \nipsfinaltrue
+\nipsfinalfalse
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-Based on the largest public neuroimaging repository
-(Human Connectome Project [HCP], \url{http://www.humanconnectomeproject.org/}),
+Based on the currently largest public neuroimaging repository
+(Human Connectome Project)
+and established region \cite{crad12} and network \cite{smith2009} atlases,
 we demonstrated that domain-informed supervised models
@@
 \subsection{Hyperparameter optimization}
-The stratified and shuffled training data were submitted
+Stratified and shuffled training sets were repeatedly and randomly drawn
+from the whole dataset with preserved class balance
+and submitted
 to a nested cross-validation (CV) scheme
@@
 
+%
 \begin{figure*}
@@
 \textit{Left:} Continuous, partially overlapping brain network priors
-(\textit{hot-colored}, taken from \cite{smith2009})
+(\textit{hot-colored}, network atlas taken from \cite{smith2009})
 accommodate the functional integration
@@
 \textit{Right:} Discrete, non-overlapping brain region priors
-(\textit{single-colored}, taken from \cite{crad12})
+(\textit{single-colored}, region atlas taken from \cite{crad12})
 accommodate the functional segregation perspective.
@@
 \end{figure*}
-
+%
 \begin{figure*}
 \begin{centering}
-\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
-\vspace{-0.2cm}
-\caption{\textbf{Naive versus informed sparse model selection
-across training set sizes.}
-Ordinary $\ell_1$-penalized logistic regression
-(\textit{upper row})
-is compared
-to hierarchical-tree-penalized logistic regression
-($\alpha = 1, \beta = 1$, \textit{lower row})
-with increasing fraction
-of the available training data
-to be fitted (\textit{left to right columns}).
-For one example (i.e., ``View tools'') from 18 psychological tasks,
-unthresholded axial maps of model weights
-are shown for comparison against
-the sample average of that class
-(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-The support recovery of that exemplary class is given
-as Pearson correlation $r$ (cf. results).
-%
-In the data-scarce scenario,
-ubiquitous in brain imaging studies,
-hierarchical tree sparsity achieves much
-better support recovery.
-% with the biggest difference
-% in model performance (83.7\% versus 89.0\%).
-%
-In the data-rich scenario,
-neurobiologically informed logistic regression
-profits more from the available information quantities than
-neurobiologically naive logistic regression.
+% \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
+\includegraphics[width=0.60\textwidth]{../figures/ROC_ALL_perclass.png}
+\vspace{-0.6cm}
+\caption{\textbf{Prediction performance across sparsity priors.}
+Comparison of the performance of logistic regression estimators
+with 6 different structured and unstructered
+sparse regularization terms
+in classifying neural activity from 18 psychological tasks.
+The area under the curve (AUC, \textit{colors})
+is obtained on an identical test set
+as mean and class-wise measure.
+%
+\textit{Hierarchical Tree Sparsity}: Structured
+$\ell_1/\ell_2$-block norm with a hierarchy of
+region and network priors
+exhibited the best out-of-sample performance
+($\alpha = 1, \beta = 1$).
+\textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
+imposed a minimum of relevant brain voxels without
+assuming special structure.
+\textit{Elastic-Net}: Unstructured logistic regression
+with interpolation between $\ell_1$- and $\ell_2$-norm 
+imposed an equilibrium between sparsity and model fit.
+\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
+norm (with additional $\ell_1$ term)
+imposed region compartments, but naive to network structure.
+\textit{Trace-norm}: Structured trace-norm penalization
+imposed low-rank structure
+with sparsity of unknown ``network'' patterns,
+but naive to region structure.
+%
+A priori knowledge of both region and network neighborhoods
+was hence most beneficial for predicting psychological tasks from
+brain maps.
 }
+\end{centering}
 \vspace{-0.4cm}
-\label{Tab:fig_dataratio}
-\end{centering}
+\label{fig_sparsities}
 \end{figure*}
-
+%
 % \paragraph{Implementation.}
@@
 As the currently biggest open-access dataset,
-we chose brain data from the Human Connectome Project (HCP)
+we chose brain data from the HCP
 \cite{barch2013}.
@@
 \begin{centering}
-% \includegraphics[width=1.00\textwidth]{../figures/sparsities.pdf}
-\includegraphics[width=0.60\textwidth]{../figures/ROC_ALL.png}
-\vspace{-0.6cm}
-\caption{\textbf{Prediction performance across sparsity priors.}
-Comparison of the performance of logistic regression estimators
-with 6 different structured and unstructered
-sparse regularization terms
-in classifying neural activity from 18 psychological tasks.
-The area under the curve (AUC, \textit{colors})
-is obtained on an identical test set
-as mean and class-wise measure.
-%
-\textit{Hierarchical Tree Sparsity}: Structured
-$\ell_1/\ell_2$-block norm with a hierarchy of
-region and network priors
-exhibited the best out-of-sample performance
-($\alpha = 1, \beta = 1$).
-\textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
-imposed a minimum of relevant brain voxels without
-assuming special structure.
-\textit{Elastic-Net}: Unstructured logistic regression
-with interpolation between $\ell_1$- and $\ell_2$-norm 
-imposed an equilibrium between sparsity and model fit.
-\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
-norm (with additional $\ell_1$ term)
-imposed region compartments, but naive to network structure.
-\textit{Trace-norm}: Structured trace-norm penalization
-imposed low-rank structure
-with sparsity of unknown ``network'' patterns,
-but naive to region structure.
-%
-A priori knowledge of both region and network neighborhoods
-was hence most beneficial for predicting psychological tasks from
-brain maps.
+\includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
+\vspace{-0.2cm}
+\caption{\textbf{Naive versus informed sparse model selection
+across training set sizes.}
+Ordinary $\ell_1$-penalized logistic regression
+(\textit{upper row})
+is compared
+to hierarchical-tree-penalized logistic regression
+($\alpha = 1, \beta = 1$, \textit{lower row})
+with increasing fraction
+of the available training data
+to be fitted (\textit{left to right columns}).
+For one example (i.e., ``View tools'') from 18 psychological tasks,
+unthresholded axial maps of recovered model weights
+are are quanitatively compared against
+the sample average of that class
+(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
+This notion of support recovery was computed by
+Pearson correlation $corr$ (cf. results).
+%
+In the data-scarce scenario,
+ubiquitous in brain imaging studies,
+hierarchical tree sparsity achieves much
+better support recovery.
+% with the biggest difference
+% in model performance (83.7\% versus 89.0\%).
+%
+In the data-rich scenario,
+neurobiologically informed logistic regression
+profits more from the available information quantities than
+neurobiologically naive logistic regression.
 }
+\vspace{-0.4cm}
+\label{fig_dataratio}
 \end{centering}
-\vspace{-0.4cm}
-\label{Tab:fig_sparsities}
 \end{figure*}
@@
 \subsection{Benchmarking hierarchical tree sparsity against
-common sparsity penalties}
+common sparse estimators}
 Hierarchical region-network priors have been systematically
@@
 in an 18-class scenario
-(Figure 2).
+(Figure \ref{fig_sparsities}).
 % (Figure \ref{Tab:fig_sparsities}).
@@
 In an important subanalysis,
-the gain of the combined region-network prior was also confirmed by
+the advantage of the \textit{combined} region-network prior was confirmed by
 selectively zeroing
-the $\eta_g$ coefficients of all region groups
-or
-the $\eta_h$ coefficients of all network groups in the hierarchical prior.
-Removing region structure from the prior achieved
-88,8\% accuracy,
-while removing network structure from the prior achieved
-87,1\% accuracy.
-These results from partial priors were indeed outperformed by
-the full region-network tree prior at 89,7\% accuracy.
-%
+either the $\eta_g$ coefficients of all \textit{region} groups
+or the $\eta_h$ coefficients of all \textit{network} groups in the hierarchical prior.
+Removing region structure from the sparsity penalty achieved
+88.8\% accuracy,
+while removing network structure from the sparsity penalty achieved
+87.1\% accuracy.
+These results from priors with impoverished a-priori structure
+were indeed outperformed by
+the full region-network tree prior at 89.7\% out-of-sample accuracy.
+
 In sum,
 driving sparse model selection by domain knowledge of region-network hierarchies
-outcompeted other types of frequently used sparse penalization techniques.
-
+outcompeted other frequently used sparse penalization techniques
+for high-dimensional data.
+%
+%
 \subsection{Sample complexity of naive versus informed sparse model selection}
@@
 was empirically estimated and quantitatively compared
-(Figure \ref{Tab:fig_dataratio}).
+(Figure \ref{fig_dataratio}).
 Region-network priors should contrain model selection towards more
@@
 hierarchical tree sparsity achieved the biggest advantage
-in out-of-sample performance by 5,1\% as well as
+in out-of-sample performance by 5.1\% as well as
 better support recovery with weight maps already much closer
@@
 suggests that \textit{class-specific region-network tradeoffs}
-might offer more performant and more interpretable classification models
-in the future.
+enables more performant and more interpretable classification models
+for future neuroimaging analyses.
 

### 2016-05-14 srne_plot_roc.py

@@ -25,6 +25,23 @@ REGS_STR = ['Hierarchical Tree Sparsity', 'Lasso',
 
 auc_mat = np.zeros((len(REGS), n_classes))
 
+# load HCP task data
+print('Loading data...')
+from sklearn.cross_validation import StratifiedShuffleSplit
+if on_server:
+    X_task, Y = joblib.load('/storage/workspace/danilo/prni2015/preload_HT_3mm')
+else:
+    X_task, Y = joblib.load('/git/prni2015/preload_HT_3mm')
+Y = np.array(Y)
+folder = StratifiedShuffleSplit(Y, n_iter=10, test_size=0.1,
+                                random_state=42)
+inds_train, inds_test = iter(folder).next()
+X_train = X_task[inds_train]
+# all estimators will have the same training set due to random_state
+Y_train = Y[inds_train]
+X_test = X_task[inds_test]
+Y_test = Y[inds_test]
+
 for i_r, r in enumerate(REGS):
     print('-' * 80)
     print(r)
@@ -91,12 +108,18 @@ plt.show()
 plt.savefig(op.join(READ_DIR, 'ROC_ALL_perclf.png'))
 
 # summary AUC plot: per task
+my_width = 3
+colors = ['k', 'y', 'b', 'g', 'r', 'm']
 plt.figure()
-for i_r in range(len(REGS)):
+for i_r, c in zip([0, 1, 2, 3, 4, 5], colors):
     plt.plot(np.arange(n_classes),
              auc_mat[i_r, :] * 100,
-             label=REGS_STR[i_r],
-             linewidth=2)
+             label=REGS_STR[i_r], color=c,
+             linewidth=my_width)
+i_r = 0
+plt.plot(np.arange(n_classes),
+    auc_mat[i_r, :] * 100, color='k',
+    linewidth=my_width)
 plt.ylim([35., 102.])
 plt.xticks(np.arange(n_classes), np.arange(n_classes) + 1)
 plt.ylabel('AUC')

### 2016-11-23 paper/ipmi2017/paper.tex
cutting back for IPMI

--- 2016-05-14 paper/nips2016/paper.tex
@@
-\documentclass{article} % For LaTeX2e
-\usepackage{nips14submit_e,times}
+%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is the LaTeX source for the instructions to authors using
+% the LaTeX document class 'llncs.cls' for contributions to
+% the Lecture Notes in Computer Sciences series.
+% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
+%
+% It may be used as a template for your own input - copy it
+% to a new file with a new name and use it as the basis
+% for your article.
+%
+% NB: the document class 'llncs' has its own and detailed documentation, see
+% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\documentclass[runningheads,a4paper]{llncs}
+
 \usepackage{hyperref}
 \usepackage{url}
-\usepackage{amsmath,amsfonts,amsthm}
+\usepackage{amsopn}
+% \usepackage{amsfonts,amsthm}
 \usepackage{bbm}
@@
 \usepackage{multirow}
-
-\def\B#1{\bm{#1}}
-%\def\B#1{\mathbf{#1}}
-\def\trans{\mathsf{T}}
-
-%\renewcommand{\labelitemi}{--}
-
-\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{remark}{Remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\title{Hierarchical Region-Network Sparsity for\\
-High-Dimensional Inference in Brain Imaging}
+\usepackage{amssymb}
+\setcounter{tocdepth}{3}
+\usepackage{graphicx}
+
+\usepackage{url}
+\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
+\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
+\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
+\newcommand{\keywords}[1]{\par\addvspace\baselineskip
+\noindent\keywordname\enspace\ignorespaces#1}
 
@@
 
-% \nipsfinalcopy % Uncomment for camera-ready version
-\nipsfinalfalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{document}
 
+\mainmatter  % start of an individual contribution
+
+% first the title is needed
+\title{Hierarchical Region-Network Sparsity for\\
+High-Dimensional Inference in Brain Imaging}
+
+% a short form should be given in case it is too long for the running head
+\titlerunning{Hierarchical Region-Network Sparsity for
+Brain Imaging}
+
+% the name(s) of the author(s) follow(s) next
+%
+% NB: Chinese authors should write their first names(s) in front of
+% their surnames. This ensures that the names appear correctly in
+% the running heads and the author index.
+%
+
+% \author{Danilo Bzdok, Michael Eickenberg,
+% Ga\"el Varoquaux, Bertrand Thirion\\
+% INRIA, Parietal team, Saclay, France\\
+% CEA, Neurospin, Gif-sur-Yvette, France\\
+% firstname.lastname@inria.fr}
+
+\author{Author1, Author2, Author3}
+
+% \author{Alfred Hofmann%
+% \thanks{Please note that the LNCS Editorial assumes that all authors have used
+% the western naming convention, with given names preceding surnames. This determines
+% the structure of the names in the running heads and the author index.}%
+% \and Ursula Barth\and Ingrid Haas\and Frank Holzwarth\and\\
+% Anna Kramer\and Leonie Kunz\and Christine Rei\ss\and\\
+% Nicole Sator\and Erika Siebert-Cole\and Peter Stra\ss er}
+
+%
+\authorrunning{Author names}
+% (feature abused for this document to repeat the title also on left hand pages)
+
+% the affiliations are given next; don't give your e-mail address
+% unless you accept that it will be published
+% \institute{Springer-Verlag, Computer Science Editorial,\\
+% Tiergartenstr. 17, 69121 Heidelberg, Germany\\
+% \mailsa\\
+% \mailsb\\
+% \mailsc\\
+% \url{http://www.springer.com/lncs}}
+
+%
+% NB: a more complex sample for affiliations and the mapping to the
+% corresponding authors can be found in the file "llncs.dem"
+% (search for the string "\mainmatter" where a contribution starts).
+% "llncs.dem" accompanies the document class "llncs.cls".
+%
+
+\toctitle{Lecture Notes in Computer Science}
+\tocauthor{Authors' Instructions}
 \maketitle
-
-\author{Danilo Bzdok, Michael Eickenberg,
-Ga\"el Varoquaux, Bertrand Thirion\\
-INRIA, Parietal team, Saclay, France\\
-CEA, Neurospin, Gif-sur-Yvette, France\\
-firstname.lastname@inria.fr}
 
@@
     priors on network hierarchies of brain regions into
-  logistic-regression to distinguish neural activity.
-  These priors bridge two levels of neurobiological architecture 
-  that are studied separately in neuroscientific research:
-  functional segregation into brain regions and
-  functional integration by brain networks.
+    logistic-regression to distinguish neural activity effects.
+    These priors bridge two separately studied levels
+    of brain architecture:
+    functional segregation into regions and
+    functional integration by networks.
     %
     Hierarchical region-network priors are shown to better classify
-  18 psychological tasks from a reference dataset
-  than other sparse estimators.
+    and recover 
+    18 psychological tasks than other sparse estimators.
     Varying the relative importance of
     region and network structure within the hierarchical tree penalty
-  recovered complementary aspects of the neural activity patterns.
+    captured complementary aspects of the neural activity patterns.
     %
@@
     generalization performance, sample complexity, and domain interpretability.
-%
-
-% OUR keywords
-%\textbf{\\keywords}: curse of dimensionality; semi-supervised learning;
-%fMRI; systems neuroscience
-
-% official NIPS keywords
-\textbf{\\keywords}: Sparsity-inducing norms, hierarchical tree sparsity,
-numerical optimization, systems neuroscience,
-functional specialization, functional integration
-
 \end{abstract}
@@
 In the brain imaging domain,
-many contemporary methods for acquiring brain signals yield
+many contemporary technologies for acquiring brain signals yield many
 more variables per observation than
@@
 \cite{bach2012optimization}.
-Such restrictions to model complexity
+These restrictions to model complexity
 are an attractive plan of attack
 for the $\textgreater$100,000 variables per brain map.
-Yet, what generally accepted neurobiological structure lends itself
+Yet, what neurobiological structure best lends itself
 to exploitation using structured sparsity priors?
@@
 % specialization & integration
-Concepts on human brain organization have long been torn
+Neuroscientific concepts on brain organization were long torn
 between the two extremes
@@
 Functional specialization emphasizes that microscopically distinguishable
-brain regions are responsible for distinct classes of computational 
-processes
+brain regions are solving distinct computational problems
 \cite{kanwisher2010functional}.
-Conversely, functional integration emphasizes that brain computation
+Conversely, functional integration emphasizes that neural computation
 is enabled by a complex interplay between these
@@
 %
-Local
-infrastructure
+However,
+local
+neuronal populations
 and global connectivity profiles are thought to go hand-in-hand
@@
 %
-However,
+Yet,
 probably no existing brain analysis method acknowledges that
 both functional design principles are inextricably involved
-in the realization of mental operations.
-
+in realizing mental operations.
+
+%
 Functional specialization has long been
-explored and interpreted based on different research methods.
-%
-For instance,
-single-cell recordings and microscopic tissue examination
+explored and interpreted.
+%
+Single-cell recordings and microscopic tissue examination
 revealed the
@@
 regions
-\cite{hubel1962receptive, zeki1978functional}.
-Tissue lesion of the mid-fusiform gyrus of the visual system,
-in turn,
+\cite{zeki1978functional}.
+Tissue lesion of the mid-fusiform gyrus of the visual system
 was frequently reported to impair
@@
 As a crucial common point,
-all these methodological approaches
+these and other methods
 yield neuroscientific findings
-that are naturally interpreted according to
+naturally interpreted according to
 non-overlapping, discrete region compartments
@@
 More recently,
-the main interpretational focus has shifted
+the interpretational focus has shifted
 from circumscribed regions to network stratifications
-in systems neuroscience.
+in neuroscience.
 %
@@
 studies of
-functional connectivity correlation \cite{buckner2013opportunities} and
-independent component analysis (ICA) \cite{beckmann2005}
+functional connectivity correlation and
+independent component analysis (ICA)
 became the workhorses of network discovery
-in neuroimaging.
-%
-As a common point of this second set of methods,
-interpretation of findings naturally embraces
+in neuroimaging \cite{beckmann2005}.
+%
+As a common point of these other methods,
+neuroscientific findings are naturally interpreted as
 cross-regional integration by
@@
 in contrast to methods examining regional specialization.
-% XXX are the compartments overlapping or not ?
 
@@
 % in stark constrast to methods examining regional specialization.
-
+%
 % study
 Building on these two
-separate major interpretational traditions in neuroscience,
-the present study proposes to incorporate
-established neurobiological structure underlying
+interpretational traditions in neuroscience,
+the present study incorporates
+neurobiological structure underlying
 functional segregation and integration
@@
 by hierarchical structured sparsity.
-That is, every variable carrying brain signals
+Every variable carrying brain signals
 will be a-priori assigned to both region and network compartments to
-improve model fitting based on existing domain knowledge.
+improve high-dimensional model fitting based on
+existing neurobiological knowledge.
 %
@@
 have recently made much progress in various domains
-from processing auditory signals \cite{daudet2004sparse},
-natural images \cite{harzallah2009combining} and
-videos \cite{kang2015structured}
+from processing auditory signals,
+% \cite{daudet2004sparse},
+natural images %\cite{harzallah2009combining}
+and
+videos
+%\cite{kang2015structured}
 % videos \cite{kang2015structured, kim2010sparse}
 to
-astrophysics \cite{vinci2014estimating},
-genetics \cite{kim2012tree},
+astrophysics, %\cite{vinci2014estimating},
+genetics, %\cite{kim2012tree},
 % genetics \cite{rapaport2008classification, kim2012tree},
 and
-conformational dynamics of protein complexes \cite{jenatton2009structured}.
+conformational dynamics of protein complexes. %\cite{jenatton2009structured}.
 %
 The hierarchical tree penalties recently suggested for imaging neuroscience
-\cite{jenatton2012multi} will be revisited to
+\cite{jenatton2012multi} will be extended to
 introduce neurobiologically plausible region and network priors
@@
 Based on the currently largest public neuroimaging repository
-(Human Connectome Project)
-and established region \cite{crad12} and network \cite{smith2009} atlases,
-we demonstrated that domain-informed supervised models
+(Human Connectome Project [HCP])
+and widely used region \cite{crad12} and network \cite{smith2009} atlases,
+we demonstrate that domain-informed supervised models
 gracefully tackle the curse of dimensionality,
@@
 and generalize better to new samples
-than domain-naive blackbox estimators.
-
-\section{Methods}
+than domain-naive black-box estimators.
+\nopagebreak
+\section*{Methods}
 This paper contributes a domain adaptation of hierarchical structured
 tree penalties to jointly incorporate region 
-specialization and network integration priors into multivariate 
-classification.
-We capitalize on hierarchical group lasso as recently introduced
-\cite{jenatton2012multi} to create a set of convex penalty terms.
-These allow acknowledging the interplay between local specialization and 
+specialization and network integration priors into high-dimensional 
+prediction.
+We capitalize on hierarchical group lasso
+\cite{jenatton2012multi} to create a set of convex sparse penalty terms.
+These conjointly acknowledge local specialization and 
 global connectivity when discriminating defined psychological tasks
@@
 Rather than inferring brain activity from psychological tasks
-in a univariate setting,
-this study infers psychological tasks from brain activity
-in a multivariate setting to allow for
+by independent comparisons of task pairs,
+this study simultaneously infers
+a set of psychological tasks from brain activity maps
+in a multivariate setting and allows for
 prediction in unseen neuroimaging data.
@@
 scanners are high-dimensional but, luckily,
-their signal is also highly structured.
-Its explicit dimensionality, the number of brain voxels,
+the measured signal is also highly structured.
+Its \textit{explicit dimensionality}, the number of brain voxels,
 typically exceeds 100,000 variables, while the number
@@
 linear model based on dot products with the voxel values.
-However, the effective dimensionality of functional neuroimaging data has been
+However, the \textit{effective dimensionality} of functional brain scans has been
 shown to be much lower \cite{bzdok2015semi}.
 Two types of low-dimensional neighborhoods will be exploited by
-injecting established knowledge of regional specialization
+injecting accepted knowledge of regional specialization
 (i.e., region priors)
@@
 (i.e., network priors)
-into the statistical estimation process.
-
-Major brain networks emerge in human individuals around birth
-\cite{doria2010}, before mental capacities mature in childhood. 
+into statistical estimation.
+\begin{figure*}
+  \vspace{-0.6cm}
+  \centering
+  \includegraphics[width=0.9\textwidth]{../figures/reg_net_prior_colin2.pdf}
+  \vspace{-0.3cm}
+  \caption{\textbf{Building blocks of the hierarchical region-network tree.}
+  Displays the a-priori neurobiological knowledge
+  introduced into the classification problem 
+  by hierarchical structured sparsity.
+  \textit{Left:} Continuous, partially overlapping brain network priors
+  (\textit{hot-colored}, network atlas taken from \cite{smith2009})
+  accommodate the functional integration
+  perspective of brain organization.
+  \textit{Right:} Discrete, non-overlapping brain region priors
+  (\textit{single-colored}, region atlas taken from \cite{crad12})
+  accommodate the functional segregation perspective.
+  \textit{Middle:} These two types of predefined voxel groups are incorporated
+  into a joint hierarchical prior of parent networks with their
+  descending region child nodes.
+  \textit{Top to bottom:} Two exemplary region-network priors
+  are shown, including
+  the early cortices that process
+  visual and sound information from the environment.
+  }
+  \vspace{-0.6cm}
+  \label{fig_priors}
+\end{figure*}
+
+Major brain networks already emerge in human individuals around birth
+\cite{doria2010}.
 In adults,
 the regions that compose
-a given cohesive network are known to have more
+a given cohesive network have more
 similar functional profiles than nodes from different networks
@@
 agree with boundaries of brain atlases.
-Such brain atlases can be obtained by segregating
-the brain's grey matter into local voxel groups
-using clustering algorithms
-\cite{crad12}.
-Consequently,
+Hence,
 each region from a brain atlas can be uniquely associated with one of
@@
 %
-In the present work previously published network definitions
+Here, previously published network definitions
 obtained using ICA \cite{smith2009}
 and
-previously published region definitions obtained from
-spatially constrained spectral clustering \cite{crad12}
+region definitions obtained from
+spatially constrained clustering \cite{crad12}
 allow constructing a hierarchy of global ICA networks with their
@@
 of expected weight distributions
-during supervised model fitting.
+that guide supervised model fitting.
 
@@
 in a nested tree structure.
-The first hierarchical level of that tree are
-the network groups that contain all
+The first hierarchical level are
+the network groups with all
 the voxels of the brain regions associated with them.
-Each network node in turn descends into a second hierarchical level of
-brain regions of spatially neighboring voxel groups.
-%
-As a consequence of such a region-network sparsity tree,
+Each network node in turn descends into a second hierarchical level with
+brain regions of neighboring voxels.
+%
+As a consequence of this region-network sparsity tree,
 a child node enters the set of relevant voxel variables only
@@
 Moreover,
-the coefficient of all region groups and all network groups can
+the coefficient of all region or all network groups can
 be weighed individually.
@@
 %
-Setting a low penalty on the network groups makes it is probable
-that all of them are active in the estimated weight maps. If we then select
-higher penalties on region groups, selection of relevant region groups is
-forced without obeying network definitions.
-Conversely, setting low penalties on the region definitions
-makes it possible for
-all voxels to be active. Selecting higher penalties on the networks then
-leads to a selection of networks with all regions associated with it.
+% Setting a low penalty on the network groups makes it is probable
+% that all of them are active in the estimated weight maps. If we then select
+% higher penalties on region groups, selection of relevant region groups is
+% forced without obeying network definitions.
+% Conversely, setting low penalties on the region definitions
+% makes it possible for
+% all voxels to be active. Selecting higher penalties on the networks then
+% leads to a selection of networks with all regions associated with it.
 %
@@
 minimization applied to linear models.
-The goal is to estimate a good predictor of psychological task
-given single brain images. Let the set \(\mathcal X\in\R^{n \times p}\) represent brain
+The goal is to estimate a good predictor of psychological tasks
+given a single brain image. Let the set \(\mathcal X\in\R^{n \times p}\) represent brain
 images of \(p > 0\) voxels.
@@
 \textrm{ either } g\subset h\textrm{ or }g\cap h = \emptyset.\]
-This allows an unambiguous assignment of each region \(g\in\mathcal G\) to one
-network \(h\in\mathcal H\) and thus establishes a tree structure.
+This allows for an unambiguous assignment of each region \(g\in\mathcal G\) to one
+network \(h\in\mathcal H\) and thus generates a tree structure.
 A root node is added to contain all voxels.
@@
 account for discrepancy in group sizes. The hierarchy-level-specific factors 
-\(\alpha > 0\) and \(\beta > 0\) can trade-off region-weighted and
+\(\alpha > 0\) and \(\beta > 0\) can tradeoff region-weighted and
 network-weighted models against each other.
@@
 sufficiently small and \(\alpha\) increased,
-the structure will come from \(\mathcal H\), leading to the
+the detected structure will derive from \(\mathcal H\), leading to the
 selection of brain networks rather than regions.
 
-It is important to note that the above trade-off shows that predominance
-can be either attributed to regions or networks, but that the
-penalty structure is nevertheless hierarchical.
+Please note that the above tradeoff enables predominance
+attributed to either brain regions or networks, although the
+penalty structure remains hierarchical.
 If the network penalty layer sets a
@@
 subregions being active.
-When evaluating the trade-off in \((\alpha, \beta)\), this needs to be taken
+When evaluating the tradeoff in \((\alpha, \beta)\), this needs to be taken
 into account.
@@
 Importantly, the thus selected sparse logistic regression classifier was
-evaluated on an identical test set in all settings.
+evaluated on an identical test set in all analysis settings.
 
@@
 \begin{figure*}
-\centering
-\includegraphics[width=0.8\textwidth]{../figures/reg_net_prior_colin.pdf}
-\vspace{-0.2cm}
-\caption{\textbf{Building blocks of the region-network tree.}
-Neurobiological priors introduced into the classification problem 
-by hierarchical structured sparsity are displayed.
-\textit{Left:} Continuous, partially overlapping brain network priors
-(\textit{hot-colored}, network atlas taken from \cite{smith2009})
-accommodate the functional integration
-perspective of brain organization.
-\textit{Right:} Discrete, non-overlapping brain region priors
-(\textit{single-colored}, region atlas taken from \cite{crad12})
-accommodate the functional segregation perspective.
-\textit{Middle:} These two types of predefined voxel groups are incorporated
-into a joint hierarchical prior of parent networks with their
-descending region child nodes.
-\textit{Top to bottom:} Four examplary region-network priors
-are shown, including
-the early cortices that process
-visual and sound information from the environment,
-a well-known attentional circuit in the left brain hemisphere,
-and
-the cerebellum that is involved in motor behavior.
-}
-\vspace{-0.4cm}
-\label{fig_priors}
-\end{figure*}
-%
-\begin{figure*}
+\vspace{-0.6cm}
 \begin{centering}
@@
 \caption{\textbf{Prediction performance across sparsity priors.}
-Comparison of the performance of logistic regression estimators
+Comparing the performance of logistic regression estimators
 with 6 different structured and unstructered
-sparse regularization terms
+sparse regularization penalties (\textit{colors})
 in classifying neural activity from 18 psychological tasks.
-The area under the curve (AUC, \textit{colors})
-is obtained on an identical test set
-as mean and class-wise measure.
-%
-\textit{Hierarchical Tree Sparsity}: Structured
-$\ell_1/\ell_2$-block norm with a hierarchy of
-region and network priors
-exhibited the best out-of-sample performance
-($\alpha = 1, \beta = 1$).
-\textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
-imposed a minimum of relevant brain voxels without
-assuming special structure.
-\textit{Elastic-Net}: Unstructured logistic regression
-with interpolation between $\ell_1$- and $\ell_2$-norm 
-imposed an equilibrium between sparsity and model fit.
-\textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
-norm (with additional $\ell_1$ term)
-imposed region compartments, but naive to network structure.
-\textit{Trace-norm}: Structured trace-norm penalization
-imposed low-rank structure
-with sparsity of unknown ``network'' patterns,
-but naive to region structure.
-%
-A priori knowledge of both region and network neighborhoods
-was hence most beneficial for predicting psychological tasks from
-brain maps.
+The area under the curve (AUC)
+is provided on an identical test set
+as class-wise measure (\textit{y-axis}) and across-class mean (\textit{legend}).
+%
+% \textit{Hierarchical Tree Sparsity}: Structured
+% $\ell_1/\ell_2$-block norm with a hierarchy of
+% region and network priors
+% exhibited the best out-of-sample performance
+% ($\alpha = 1, \beta = 1$).
+% \textit{Lasso}: Unstructured $\ell_1$-penalized logistic regression
+% imposed a minimum of relevant brain voxels without
+% assuming special structure.
+% \textit{Elastic-Net}: Unstructured logistic regression
+% with interpolation between $\ell_1$- and $\ell_2$-norm 
+% imposed an equilibrium between sparsity and model fit.
+% \textit{(Sparse) Group Sparsity}: Structured $\ell_1/\ell_2$-block
+% norm (with additional $\ell_1$ term)
+% imposed region compartments, but naive to network structure.
+% \textit{Trace-norm}: Structured trace-norm penalization
+% imposed low-rank structure
+% with sparsity of unknown ``network'' patterns,
+% but naive to region structure.
+%
+A-priori knowledge of both region and network neighborhoods
+was hence most beneficial for predicting
+various psychological tasks from brain maps.
 }
 \end{centering}
-\vspace{-0.4cm}
 \label{fig_sparsities}
+\vspace{-0.6cm}
 \end{figure*}
@@
 % (\url{http://github.com/banilo/nips2015}).
-
-%
+\nopagebreak
 \subsection{Data}
 % \paragraph{Data.}
-As the currently biggest open-access dataset,
+As the currently biggest open-access dataset in brain imagingf5,
 we chose brain data from the HCP
@@
 
+% \paragraph{Benchmarking hierarchical tree sparsity against
+\subsection{Benchmarking hierarchical tree sparsity against
+common sparse estimators}
+Hierarchical region-network priors have been systematically
+evaluated against other popular choices of sparse classification algorithms
+in an 18-class scenario
+(Figure \ref{fig_sparsities}).
+% (Figure \ref{Tab:fig_sparsities}).
+%
+Logistic regression with $\ell_1/\ell_2$-block-norm penalization
+incorporated a hierarchy of previously known region and network neighborhoods
+for a neurobiological bias of the statistical estimation
+($\alpha = 1, \beta = 1$).
+%
+Vanilla logistic regression with $\ell_1$-penalization and
+$\ell_1$-$\ell_2$-elastic-net penalization
+do not assume any previously known special structure.
+These classification estimators embrace a vision of neural activity structure
+that expects a minimum of
+topographically and functionally independent brain voxels to be relevant.
+%
 \begin{figure*}
+  \vspace{-0.6cm}
   \begin{centering}
     \includegraphics[width=0.80\textwidth]{../figures/dataratio_trans.pdf}
-\vspace{-0.2cm}
-\caption{\textbf{Naive versus informed sparse model selection
-across training set sizes.}
+    \vspace{-0.3cm}
+    \caption{\textbf{Sample complexity in naive versus informed sparse model selection.}
     Ordinary $\ell_1$-penalized logistic regression
@@
     (\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-This notion of support recovery was computed by
-Pearson correlation $corr$ (cf. results).
+    This notion of weight recovery was computed by
+    Pearson correlation ($corr$).
     %
     In the data-scarce scenario,
-ubiquitous in brain imaging studies,
+    ubiquitous in brain imaging field,
     hierarchical tree sparsity achieves much
@@
     }
-\vspace{-0.4cm}
     \label{fig_dataratio}
+    \vspace{-0.6cm}
   \end{centering}
 \end{figure*}
-
-% \paragraph{Benchmarking hierarchical tree sparsity against
-\subsection{Benchmarking hierarchical tree sparsity against
-common sparse estimators}
-Hierarchical region-network priors have been systematically
-evaluated against other popular choices of sparse classification algorithms
-in an 18-class scenario
-(Figure \ref{fig_sparsities}).
-% (Figure \ref{Tab:fig_sparsities}).
-%
-Logistic regression with $\ell_1/\ell_2$-block-norm penalization
-incorporated a hierarchy of previously known region and network neighborhoods
-for a neurobiological bias of the statistical estimation
-($\alpha = 1, \beta = 1$).
-%
-Vanilla logistic regression with $\ell_1$-penalization and
-$\ell_1$-$\ell_2$-elastic-net penalization
-do not assume any previously known special structure.
-These classification estimators embrace a vision of neural activity structure
-that expects a minimum of
-topographically and functionally independent brain voxels to be relevant.
-%
 Logistic regression with (sparse) group sparsity
@@
 Across experiments with stratified and shuffled
-cross-validation (90\%/10\% train/test set) across pooled subject data,
+cross-validation (90\%/10\% train/test set) across pooled participant data,
 hierarchial tree sparsity was most successful
@@
 precision 0.85, recall 0.84).
-Introducing a priori knowledge of brain region compartments
+Introducing a-priori knowledge of brain region compartments
 by sparse group sparsity
@@
 driving sparse model selection by domain knowledge of region-network hierarchies
-outcompeted other frequently used sparse penalization techniques
+outcompeted all other frequently used sparse penalization techniques
 for high-dimensional data.
@@
 (Figure \ref{fig_dataratio}).
-Region-network priors should contrain model selection towards more
+Region-network priors should constrain model selection towards more
 neurobiologically plausible classification estimators.
@@
 
+%
 % results: accuracy
@@
 88.6\% versus 89.7\% (100\%) accuracy.
+%
 % results: sparsity
@@
 This agreement metric of model selection across fold pairs
-yielded the means 0.001 ($\ell_1$) versus 0.506 (Hierarchical Tree).
-
-Three observations have been made.
-First,
-in the data-scarce scenario (i.e., 1/5 of available training data),
-hierarchical tree sparsity achieved the biggest advantage
-in out-of-sample performance by 5.1\% as well as
-better support recovery with weight maps already much closer
-to the respective class averages
-\cite{varoquaux2012small}.
-In the case of scarce training data, which is typical for the brain imaging domain,
-regularization by region-network priors thus allowed for
-more effective extraction of classification-relevant structure
-from the neural activity maps.
-%
-Second,
-across training data fractions,
-the weight maps from ordinary logistic regression exhibited
-higher variance and more zero coefficients
-than hierarchical tree logistic regression.
-Given the usually high multicollinearity in neuroimaging data,
-this observation is likely to reflect instable selection of
-representative voxels among class-responsive groups
-due to the $\ell_1$-norm penalization.
-%
-Third,
-in the data-rich scenario (i.e., entire training data used for model fitting),
-neurobiologically informed logistic regression
-profited much more from the increased information quantities than
-neurobiologically naive logistic regression.
-That is, the region-network priors actually further enhanced the support
-recovery even in abundant input data.
-This was the case although
-the maximal classification performance of $\approx$90\% has already
-been reached with small training data fractions by the structured estimator.
-In contrast, 
-the unstructured estimator approached this generalization performance
-only with bigger input data quantities.
-%
+yielded the means 0.001 ($\ell_1$) versus 0.506 (hierarchical tree).
 \begin{figure*}
+  \vspace{-0.6cm}
   \begin{centering}
-\includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin2.pdf}
-%
+    % \includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin2.pdf}
+    \includegraphics[width=0.90\textwidth]{../figures/reg_net_ratio_colin3.png}
+    \vspace{-0.3cm}
     \caption{\textbf{Support recovery as a function of
@@
     (\textit{right columns}).
-Among the 18 classes, the model weights are shown for 5 exemplary
+    Among the 18 classes, the model weights are shown for 3 exemplary
     psychological
     tasks followed by participants lying in a brain imaging scanner
-(\textit{from top to bottom}): tongue movement, listening to stories,
-taking somebody else's perspective (ToM, "theory of mind"),
-as well as
+    (\textit{from top to bottom}): tongue movement,
     viewing locations and tools.
-The 18-class out-of-sample accuracy is indicated
-on the \textit{bottom} and
-the class-wise mean neural activty
-(\textit{rightmost column}, thresholded at the $75^{th}$ percentile).
-%
-First,
-different emphasis on regions versus networks
+    The 18-class out-of-sample accuracy \textit{bottom} and
+    the class-wise mean neural activity
+    (\textit{rightmost column}, thresholded at the $75^{th}$ percentile)
+    are indicated.
+    %
+    % First,
+    Different emphasis on regions versus networks
     in hierarchical structured sparsity can
@@
     %
-Second,
-favoring region versus network structure during model selection
+    % Second,
+    Favoring region versus network structure during model selection
     recovers complementary, non-identical aspects of
@@
     %
-Third,
-equal emphasis on region versus network neighborhoods in the
-high-dimensional neuroimaging data yields more dispersed,
-less interpretable model choices.
+    % Third,
+    % equal emphasis on region versus network neighborhoods in the
+    % high-dimensional neuroimaging data yields more dispersed,
+    % less interpretable model choices.
     }
@@
   \end{centering}
+  \vspace{-0.6cm}
 \end{figure*}
+\begin{table*}[]
+  \centering
+  \caption{Out-of-sample performance by region-network emphasis}
+  \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
+    \textbf{Reg-Net Ratio}          & 100   & 50    & 10   & 5     & 2    & 1     & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ \\ \hline
+    \textbf{Accuracy {[}\%{]}}             & 89.7  & 89.9  & 90.1 & 90.5  & 88.0 & 89.7  & 87.8           & 88.0           & 87.7           & 88.4           & 88.1  
+  \end{tabular}
+  \vspace{-0.6cm}
+  \label{table_reg_net_ratio}
+\end{table*}
+
+%
+Three observations have been made.
+First,
+in the data-scarce scenario (i.e., 1/5 of available training data),
+hierarchical tree sparsity achieved the biggest advantage
+in out-of-sample performance by 5.1\% as well as
+better support recovery with weight maps already much closer
+to the respective class averages
+\cite{varoquaux2012small}.
+In the case of scarce training data, which is typical for the brain imaging domain,
+regularization by region-network priors thus allowed for
+more effective extraction of classification-relevant structure
+from the neural activity maps.
+%
+Second,
+across training data fractions,
+the weight maps from ordinary logistic regression exhibited
+higher variance and more zero coefficients
+than hierarchical tree logistic regression.
+Given the usually high multicollinearity in neuroimaging data,
+this observation is likely to reflect instable selection of
+representative voxels among class-responsive groups
+due to the $\ell_1$-norm penalization.
+%
+Third,
+in the data-rich scenario (i.e., entire training data used for model fitting),
+neurobiologically informed logistic regression
+profited much more from the increased information quantities than
+neurobiologically naive logistic regression.
+That is, the region-network priors actually further enhanced the support
+recovery in abundant input data.
+This was the case although
+the maximal classification performance of $\approx$90\% has already
+been reached with small training data fractions by the structured estimator.
+In contrast, 
+the unstructured estimator approached this generalization performance
+only with bigger input data quantities.
 %
@@
 can similarly extrapolate to unseen neural activity maps.
-%
-\begin{table*}[]
-  \centering
-  \caption{Out-of-sample performance by region-network emphasis}
-  \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
-    \textbf{Region-Network Ratio}          & 100   & 50    & 10   & 5     & 2    & 1     & $\frac{1}{2}$  & $\frac{1}{5}$  & $\frac{1}{10}$ & $\frac{1}{50}$ & $\frac{1}{100}$ \\ \hline
-    \textbf{Accuracy {[}\%{]}}             & 89.7  & 89.9  & 90.1 & 90.5  & 88.0 & 89.7  & 87.8           & 88.0           & 87.7           & 88.4           & 88.1  
-  \end{tabular}
-  \vspace{-0.6cm}
-  \label{table_reg_net_ratio}
-\end{table*}
-%
 Second,
@@
 \section{Conclusion}
+
 Relevant structure in neuroimaging data has long been investigated
@@
 orchestrating its region nodes.
-It suggests hierarchical statistical models
+Hierarchical statistical models hence suggest themselves
 as an underexploited opportunity for neuroimaging analysis.
 %
-This proof-of-concept study demonstrates the simultaneous exploitation of
+The present proof-of-concept study demonstrates the simultaneous exploitation of
 both neurobiological compartments
 for sparse variable selection and high-dimensional prediction
-in a reference dataset.
+in an extensive reference dataset.
 %
@@
 
-The present approach has important advantages over previous
+Our approach has important advantages over previous
 analysis strategies that rely on dimensionality reduction of
@@
 integration account of brain organization,
-\textit{ii)} depend on the ground truth being a region or network effect,
+\textit{ii)} depend on the ground truth being either a region or network effect,
 and
@@
 in single- and multi-task learning settings.
-The principled regularization scheme could inform
+The principled regularization scheme could also inform
 unsupervised structure-discovery by
 matrix factorization and clustering algorithms
-\cite{jenatton2009structured, witten2010framework}.
+\cite{jenatton2009structured}.
+% \cite{jenatton2009structured, witten2010framework}.
 Additionally,
@@
 Ultimately,
-successful high-dimensional inference is
+successful high-dimensional inference on brain scans is
 a prerequisite
@@
 in personalized psychiatry and neurology.
-
-% \paragraph{Acknowledgment.}
-% {\small The research leading to these results has received funding from the
-% European Union Seventh Framework Programme (FP7/2007-2013)
-% under grant agreement no. 604102 (Human Brain Project).
-% Data were provided by the Human Connectome Project.
-% Further support was received from
-% the German National Academic Foundation (D.B.),
-% the German Research Foundation (BZ2/2-1 and BZ2/3-1 to D.B.),
-% and the MetaMRI associated team (B.T., G.V.).
-% }
-
+\nopagebreak
 \small
+\bibliography{../paper_refs}
 % \bibliographystyle{plainnat}
-\bibliography{../paper_refs}
 \bibliographystyle{splncs03}
 
-\newpage
-\section{Appendix}
-%
-\paragraph{Data.}
-As the currently biggest openly-accessible reference dataset,
-we chose the Human Connectome Project (HCP) resources
-(Barch et al., 2013).
-Neuroimaging task data with labels of ongoing cognitive processes
-were drawn from 500
-healthy HCP participants.
-18 HCP tasks 
-were selected that are known to elicit reliable neural activity
-across participants.
-The task paradigms include
-1) working memory/cognitive control processing, 2)
-incentive processing, 3) visual and somatosensory-motor processing,
-4) language processing (semantic and phonological processing),
-5) social cognition, 6) relational processing, and 7) emotional
-processing. All data were acquired on the same Siemens Skyra 3T scanner.
-Whole-brain EPI acquisitions were acquired with a
-32 channel head coil (TR=720ms, TE=33.1ms, flip angle=52°, BW=2290Hz/Px,
-in-plane FOV=$280\textrm{mm}\times180\textrm{mm}$, 72 slices, 2.0mm 
-isotropic voxels).
-The ``minimally preprocessed'' pipeline includes
-gradient unwarping, motion correction, fieldmap-based EPI distortion
-correction, brain-boundary-based registration of EPI to structural
-T1-weighted scans, nonlinear (FNIRT) registration into MNI space,
-and grand-mean intensity normalization. Activity maps were spatially
-smoothed with a Gaussian kernel of 4mm (FWHM). A GLM was
-implemented by FILM from the FSL suite with model regressors from convolution
-with a “canonical” hemodynamic response function and from temporal derivatives.
-HCP tasks were conceived to modulate activity
-in a maximum of different brain regions and neural systems. Indeed, at
-least 70\% of the participants showed consistent brain activity in
-contrasts from the task battery, which certifies excellent
-activity patterns covering extended parts of the brain (Barch et al., 2013).
-%
-In sum, the HCP task data incorporated 8650 first-level activity maps
-from 18 diverse paradigms administered to 498 participants (2 removed
-due to incomplete data).
-All maps were resampled to a common 60x72x60 space of
-3mm isotropic voxels and gray-matter masked (at least 10\% tissue
-probability).
-The supservised analyses were based on labeled HCP task maps with
-79,941 voxels of interest representing z-values in gray matter.
-
-\begin{table}[h]
-  \resizebox{0.98\textwidth}{!}{%
-  \begin{tabular}{l|l|l}
-    \hline
-  {\bf Cognitive Task} & {\bf Stimuli}                         & {\bf Instruction for participants}                                                \\ \hline
-  1 Reward             & \multirow{2}{*}{Card game}            & \multirow{2}{*}{Guess the number of a mystery card for gain/loss of money}        \\ \cline{1-1}
-  2 Punish             &                                       &                                                                                   \\ \hline
-  3 Shapes             & Shape pictures                        & Decide which of two shapes matches another shape geometrically                    \\ \hline
-  4 Faces              & Face pictures                         & Decide which of two faces matches another face emotionally                        \\ \hline
-  5 Random             & \multirow{2}{*}{Videos with objects}  & \multirow{2}{*}{Decide whether the objects act randomly or intentionally} \\ \cline{1-1}
-  6 Theory of mind     &                                       &                                                                                   \\ \hline
-  7 Mathematics        & Spoken numbers                        & Complete addition and subtraction problems                                        \\ \hline
-  8 Language           & Auditory stories                      & Choose answer about the topic of the story                                        \\ \hline
-  9 Tongue movement    & \multirow{3}{*}{Visual cues}          & Move tongue                                                                       \\ \cline{1-1} \cline{3-3} 
-  10 Food movement     &                                       & Squeezing of the left or right toe                                                \\ \cline{1-1} \cline{3-3} 
-  11 Hand movement     &                                       & Tapping of the left or right finger                                               \\ \hline
-  12 Matching          & \multirow{2}{*}{Shapes with textures} & Decide whether two objects match in shape or texture                             \\ \cline{1-1} \cline{3-3} 
-  13 Relations         &                                       & Decide whether object pairs differ both along either shape or texture             \\ \hline
-  14 View Bodies       & Pictures                              & Passive watching                                                                   \\ \hline
-  15 View Faces        & Pictures                              & Passive watching                                                                   \\ \hline
-  16 View Places       & Pictures                              & Passive watching                                                                   \\ \hline
-  17 View Tools        & Pictures                              & Passive watching                                                                   \\ \hline
-  18 Two-Back          & Various pictures                      & Indicate whether current stimulus is the same as two items earlier                \\ \hline
-  \end{tabular}
-}
-\vspace{-0.2cm}
-\caption{\textbf{Description of psychological tasks to predict.}}
-\label{table_tasks}
-\end{table}
-
 \end{document}

### 2016-11-23 srne_plot_roc.py

@@ -108,17 +108,18 @@ plt.show()
 plt.savefig(op.join(READ_DIR, 'ROC_ALL_perclf.png'))
 
 # summary AUC plot: per task
-my_width = 3
-colors = ['k', 'y', 'b', 'g', 'r', 'm']
+my_width = 5
+colors = ['r', 'y', 'b', 'g', 'k', 'c']
 plt.figure()
 for i_r, c in zip([0, 1, 2, 3, 4, 5], colors):
     plt.plot(np.arange(n_classes),
              auc_mat[i_r, :] * 100,
-             label=REGS_STR[i_r], color=c,
+             label=REGS_STR[i_r] + ' (mean AUC=%.1f)' % np.mean(auc_mat[i_r, :] * 100),
+             color=c,
              linewidth=my_width)
 i_r = 0
 plt.plot(np.arange(n_classes),
-    auc_mat[i_r, :] * 100, color='k',
+    auc_mat[i_r, :] * 100, color='r',
     linewidth=my_width)
 plt.ylim([35., 102.])
 plt.xticks(np.arange(n_classes), np.arange(n_classes) + 1)

### 2016-11-23 srne_plot_sparsity.py

@@ -44,12 +44,13 @@ for i_c, c in enumerate(contrasts_names):
 
 
 # REGS = ['tree-l2', 'l1']
-REGS = ['tree-l2',
-    'group-lasso-l2', 'sparse-group-lasso-l2',
-    'l1', 'elastic-net',
-    'trace-norm']
+REGS = ['tree-l2', 'l1', 
+    # 'group-lasso-l2', 'sparse-group-lasso-l2',
+    # 'elastic-net',
+    # 'trace-norm'
+    ]
 # dataratios = np.linspace(20, 100, 5)
-dataratios = [100]
+dataratios = [20]
 
 for ratio in dataratios:
     READ_DIR = 'srne_benchmark_dataratioFIXED%i_zerobrainlevel_weighted'

### 2016-11-23 paper/ipmi2017/paper.tex
some news

@@
 We capitalize on hierarchical group lasso
-\cite{jenatton2012multi} to create a set of convex sparse penalty terms.
+to create a set of convex sparse penalty terms.
 These conjointly acknowledge local specialization and 
@@
 
-Major brain networks already emerge in human individuals around birth
+Major brain networks emerge in human individuals around birth
 \cite{doria2010}.
-In adults,
-the regions that compose
-a given cohesive network have more
+Their nodes have more
 similar functional profiles than nodes from different networks
 \cite{anderson2013}.
-As a well-established method for network estimation,
+As a popular method for network extraction,
 ICA \cite{beckmann2005} yields continuous brain maps with
 weights for each voxel. The region nodes of ICA
-networks are spatially disjoint sets of voxel groups that
+network are spatially disjoint sets of voxel groups that
 agree with boundaries of brain atlases.
@@
 spatially constrained clustering \cite{crad12}
-allow constructing a hierarchy of global ICA networks with their
+allowed constructing a hierarchy of global ICA networks with their
 assigned local cluster regions
 (Figure \ref{fig_priors}).
-The ensuing network-region tree is used as a structural prior
+The ensuing network-region tree was used as a frequentist prior
 of expected weight distributions
-that guide supervised model fitting.
-
-This tree structure can be plugged into
+to advantageously bias supervised model fitting.
+
+Specifically, this tree structure was plugged into
 hierarchical sparsity penalty terms
@@
 %
-As a consequence of this region-network sparsity tree,
+Induced by the region-network sparsity tree,
 a child node enters the set of relevant voxel variables only
@@
 Moreover,
-the coefficient of all region or all network groups can
+the coefficients of all region or all network groups can
 be weighed individually.
 Trading off the voxel penalties of the network level against the
-voxel penalties of the region level,
+voxel penalties of the region level
 we can design distinct estimation regimes.
@@
 %
-This region-network equilibrium allows inspecting the relative contributions
-of the region and network levels
-of the hierarchical tree prior.
+% This region-network equilibrium allows inspecting the relative contributions
+% of the region and network levels
+% of the hierarchical tree prior.
 
@@
 images of \(p > 0\) voxels.
-%
 We then minimize the risk \(\mathcal L(\hat y, y)\) with
@@
 where \(\lambda > 0\) and \(\Omega\) is the regularizer.
-
 Brain \textit{regions} are defined as disjoint groups of voxels. Let \(\mathcal G\)
@@
 \quad\forall i\not=j\]
-
 Brain \textit{networks} consist of one or several brain regions.
@@
 network-weighted models against each other.
-
 Decreasing \(\alpha\) leads to less 
@@
 %
-A-priori knowledge of both region and network neighborhoods
+Simultaneous knowledge of both region and network neighborhoods
 was hence most beneficial for predicting
-various psychological tasks from brain maps.
+tasks from neural activity.
 }

### 2016-12-06 paper/ipmi2017/paper.tex
last cuts

@@
 \textit{sparsity} assumptions
-\cite{hastie2015statistical}.
+\cite{bach2012optimization}.
 They act as regularizer by encouraging zero coefficients
@@
 The goal is to estimate a good predictor of psychological tasks
-given a single brain image. Let the set \(\mathcal X\in\R^{n \times p}\) represent brain
+given a single brain image. Let the set \(\mathcal X\in\mathbb{R}^{n \times p}\) represent brain
 images of \(p > 0\) voxels.
@@
 
-For a brain image \(w\in\R^p\) and a group \(g\), the vector 
-\(w_g\in\R^{|g|}\) is defined as the restriction of \(w\) to the coordinates
+For a brain image \(w\in\mathbb{R}^p\) and a group \(g\), the vector 
+\(w_g\in\mathbb{R}^{|g|}\) is defined as the restriction of \(w\) to the coordinates
  in \(g\). The penalty structured by network
@@
 \[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
-if \(y\in\{-1, 1\}\) and with \(x_i\in\R^p\) the training sample brain images.
+if \(y\in\{-1, 1\}\) and with \(x_i\in\mathbb{R}^p\) the training sample brain images.
 We optimize parameters \(w\) using an iterative forward-backward
@@
 \includegraphics[width=0.60\textwidth]{../figures/ROC_ALL_perclass.png}
-\vspace{-0.6cm}
+\vspace{-0.65cm}
 \caption{\textbf{Prediction performance across sparsity priors.}
@@
 % \paragraph{Data.}
-As the currently biggest open-access dataset in brain imagingf5,
+As the currently biggest open-access dataset in brain imaging,
 we chose brain data from the HCP
@@
 were selected that are known to elicit reliable neural activity
-across participants
-(see appendix for detailed descriptions of dataset and tasks).
+across participants.
+% (see appendix for detailed descriptions of dataset and tasks).
 % across participants (Table \ref{table_tasks}).
 The HCP data incorporated $n$ = 8650 first-level activity maps
-from 18 diverse paradigms administered to 498 participants (2 removed
-due to incomplete data).
-All maps were warped into a common $60\times72\times60$ space of
-3mm isotropic voxels and gray-matter masked (at least 10\% tissue
-probability).
+from 18 diverse paradigms in a common $60\times72\times60$ space of
+3mm isotropic gray-matter voxels.
 Hence,
-the present experiments were based on task-labeled HCP maps of neural
-activity with
-$p$ = 79,941 voxels of interest that represent z-scored-values in gray matter.
+the present analyses were based on task-labeled HCP maps of neural
+activity with z-scored $p$ = 79,941 voxels.
 
@@
 % \end{table*}
-
 \section{Experimental Results}
-
 % \paragraph{Benchmarking hierarchical tree sparsity against
@@
 \begin{figure*}
-  \vspace{-0.6cm}
+  \vspace{-0.3cm}
   \begin{centering}
@@
 \begin{table*}[]
+  \vspace{-0.6cm}
   \centering
   \caption{Out-of-sample performance by region-network emphasis}
+  \vspace{-0.3cm}
   \begin{tabular}{l|l|l|l|l|l|l|l|l|l|l|l|l|l|l|l}
@@
 \section{Conclusion}
-
-Relevant structure in neuroimaging data has long been investigated
+Relevant structure in brain recordings has long been investigated
 according to two separate organizational principles:
@@
 is shown to enhance
-model interpretability and generalization performance,
-although these two goals are typically in conflict
-\cite{hastie2015statistical}.
+model interpretability and generalization performance.
 
@@
 the neuroimaging data to harness the curse of dimensionality.
-They often resort to preliminary pooling functions within regions
+They often resort to preliminary pooling functions based on region atlases
 or regression against network templates
-for subsequent supervised learning on the aggregated feature space.
+for subsequent supervised learning on the ensuing aggregated features.
 Such lossy approaches of
 feature engineering and subsequent inference
-\textit{i)} can only satisfy the specialization or
-integration account of brain organization,
+\textit{i)} can only satisfy either the specialization or
+the integration account of brain organization,
 \textit{ii)} depend on the ground truth being either a region or network effect,
 and
-\textit{iii)} cannot issue individual coefficients for every brain voxel.
+\textit{iii)} cannot issue individual coefficients for every voxel of the brain.
 %
@@
 increase in model bias.
-Viewed from the Vapnik-Chervonenkis dimensions,
-this entailed a healthy decrease in the complexity capacity of the prediction model
-with a higher chance of extrapolating to unobserved data samples.
+% Viewed from the Vapnik-Chervonenkis dimensions,
+% this entailed a healthy decrease in the complexity capacity of the prediction model
+% with a higher chance of extrapolating to newly acquired data samples.
 
@@
 region-network sparsity priors could be incorporated into various
-pattern-learning methods in systems neuroscience.
+pattern-learning methods applied in systems neuroscience.
 %
@@
 from the spatial activity domain to
-priors of coherent spatiotemporal activity structure
-\cite{gramfort2011tracking}.
+priors of coherent spatiotemporal activity structure.
 %
@@
 sparse selection of overcomplete region-network dictionaries.
-Advanced but non-hierarchical penalty terms will probably allow for
-more complex structured sparsity that
-go beyond the recently enabled parent-children dependencies.
+% Advanced but non-hierarchical penalty terms will probably allow for
+% more complex structured sparsity that
+% go beyond the recently enabled parent-children dependencies.
 %

### 2016-12-06 paper/ipmi2017/paper.tex
interm

@@
     %
-    As an extension to imaging neuroscience,
+    As an extension to medical imaging,
     the present work incorporates
@@
     Local and global priors of neurobiological knowledge
-    are thus demonstrated to enhance
-    generalization performance, sample complexity, and domain interpretability.
+    are thus demonstrated to offer advantages in
+    generalization performance, sample complexity,
+    and domain interpretability.
 \end{abstract}
@@
 \cite{bach2012optimization}.
-They act as regularizer by encouraging zero coefficients
+Those act as regularizer by encouraging zero coefficients
 in model selection.
@@
 \nopagebreak
-\section*{Methods}
-This paper contributes a domain adaptation of hierarchical structured
+\section{Methods}
+This paper contributes a neuroscience adaptation of hierarchical structured
 tree penalties to jointly incorporate region 
@@
 We capitalize on hierarchical group lasso
-to create a set of convex sparse penalty terms.
+to create a new class of convex sparse penalty terms.
 These conjointly acknowledge local specialization and 
-global connectivity when discriminating defined psychological tasks
+global integration when discriminating defined psychological tasks
 from neural activity maps.
@@
 by independent comparisons of task pairs,
-this study simultaneously infers
+this approach simultaneously infers
 a set of psychological tasks from brain activity maps
@@
 \end{figure*}
+%
+\begin{wrapfigure}{r}{0.45\textwidth}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{../figures/level_schematic_crop.pdf}
+\end{centering}
+\vspace{-0.7cm}
+  \caption{\textbf{Hierarchical Tree Prior.}
+  % Abc
+  % \textit{Left:} Def
+  }
+\label{fig_prior_penalty}
+\end{wrapfigure}
 
@@
 ICA \cite{beckmann2005} yields continuous brain maps with
-weights for each voxel. The region nodes of ICA
+voxel-level resolution. The region nodes of ICA
 network are spatially disjoint sets of voxel groups that
@@
 Each network node in turn descends into a second hierarchical level with
-brain regions of neighboring voxels.
+brain regions of neighboring voxels
+(Figure \ref{fig_prior_penalty}).
 %
@@
 The goal is to estimate a good predictor of psychological tasks
-given a single brain image. Let the set \(\mathcal X\in\mathbb{R}^{n \times p}\) represent brain
+given a single brain image. Let the set
+\(\mathbf{X}\in\mathbb{R}^{n \times p}\) represent brain
 images of \(p > 0\) voxels.
 We then minimize the risk \(\mathcal L(\hat y, y)\) with
-\(\hat y = f(X\hat w + \hat b)\), where \(f\) is a link function 
+\(\hat y = f(\mathbf{X} \mathbf{\hat w} + \mathbf{\hat b})\), where \(f\) is a link function 
 (e.g., sigmoid for logistic regression, identity for linear regression),
@@
 We incorporate an informative prior through regularization:
-\[\argmin_{w, b} \mathcal L(f(Xw + b), y) + \lambda\Omega(w),\]
+\[ \mathbf{\hat{w}, \hat{b}} = \argmin_{w, b} \mathcal L(f(\mathbf{X}\mathbf{w} + \mathbf{b}), y) + \lambda\Omega(\mathbf{w}),\]
 where \(\lambda > 0\) and \(\Omega\) is the regularizer.
@@
 A root node is added to contain all voxels.
-
-For a brain image \(w\in\mathbb{R}^p\) and a group \(g\), the vector 
-\(w_g\in\mathbb{R}^{|g|}\) is defined as the restriction of \(w\) to the coordinates
+For a brain image \(\mathbf{w}\in\mathbb{R}^p\) and a group \(g\), the vector 
+\(\mathbf{w}_g\in\mathbb{R}^{|g|}\) is defined as the restriction of \(\mathbf{w}\) to the coordinates
  in \(g\). The penalty structured by network
 and region information can then be written as
-\[\Omega(w) = \alpha\sum_{h\in\mathcal H}\eta_h\|w_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|w_g\|_2.\]
+\[\Omega(\mathbf{w}) = \alpha\sum_{h\in\mathcal H}\eta_h\|\mathbf{w}_h\|_2 + \beta\sum_{g\in\mathcal G}\eta_g\|\mathbf{w}_g\|_2.\]
 As originally recommended \cite{yuan2006model},
@@
 Its loss can be written as
-\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, w\rangle)) + \lambda\Omega(w),\]
+\[\sum_{i=1}^n\log(1 + \exp(-y_i\langle x_i, \mathbf{w}\rangle)) + \lambda\Omega(\mathbf{w}),\]
 if \(y\in\{-1, 1\}\) and with \(x_i\in\mathbb{R}^p\) the training sample brain images.
-We optimize parameters \(w\) using an iterative forward-backward
+We optimize parameters \(\mathbf{w}\) using an iterative forward-backward
 scheme analogous to the FISTA solver for the lasso \cite{beck2009}.
@@
 the present analyses were based on task-labeled HCP maps of neural
-activity with z-scored $p$ = 79,941 voxels.
+activity with $p$ = 79,941 z-scored voxels.
 
@@
 in distinguishing unseen neural activity maps from 18 psychological tasks
-(89.7\% multi-class accuracy, mean AUC 94.8 [+/- 9.1 standard deviation]
+(89.7\% multi-class accuracy, mean AUC 0.948 [+/- 0.091 standard deviation]
 mean precision 0.87, mean recall 0.92).
@@
 structured by trace-norm regularization
-(89.4\%, mean AUC 90.8 [+/- 14.8],
+(89.4\%, mean AUC 0.908 [+/- 0.148],
 precision 0.86, recall 0.91).
 Lasso featured an average performance comparing to the other sparse estimators
-(88.6\%, mean AUC 94.3 [+/- 9.3],
+(88.6\%, mean AUC 0.943 [+/- 0.093],
 precision 0.86, recall 0.90).
@@
 average performance comparing to the other sparse estimators
-(88.1\%, mean AUC 94.1 [+/- 10.2],
+(88.1\%, mean AUC 0.941 [+/- 0.102],
 precision 0.85, recall 0.84).
@@
 by sparse group sparsity
-(87.9\%, mean AUC 93.9 [+/- 10.1], precision 0.85, recall 0.90)
+(87.9\%, mean AUC 0.939 [+/- 0.101], precision 0.85, recall 0.90)
 and
 by group sparsity
-(87.9\%, mean AUC 84.7 [+/- 17.3], precision 0.85, recall 0.90)
+(87.9\%, mean AUC 0.847 [+/- 0.173], precision 0.85, recall 0.90)
 performed worst.

### 2016-12-06 paper/ipmi2017/paper.tex
finished Bertrands comments

@@
 \begin{centering}
-\includegraphics[width=0.45\textwidth]{../figures/level_schematic_crop.pdf}
+\includegraphics[width=0.45\textwidth]{../figures/level_schematic_crop.jpg}
 \end{centering}
@@
 ($\alpha = 1, \beta = 1$)
-was empirically estimated and quantitatively compared
+was empirically evaluated and quantitatively compared
 (Figure \ref{fig_dataratio}).
@@
 The $\ell_1$-penalized logistic regression
-yielded the mean (+/- standard deviation) sparsities
-50.0 (+/- 2.6), 45.4 (+/- 2.3), 40.0 (+/- 2.4), 30.9 (+/- 2.0), and 24.0 (+/- 2.3)
+yielded the mean sparsities
+50.0, 45.4, 40.0, 30.9, and 24.0
 after model fitting with 20\% to 100\% training data.
@@
 yield the sparsities
-163.2 (+/- 0.7), 160.2 (+/- 1.8), 132.1 (+/- 3.3), 116.2 (+/- 4.4), and 88.4 (+/- 8.4)
+163.2, 160.2, 132.1, 116.2, and 88.4
 after fitting 20\% to 100\% of the training data.
@@
 $\ell_1$-penalized versus hierarchical-tree-penalized logistic regression
-achieved a mean correlation $r$ (+/- standard deviation) of
-0.10 (+/- 0.03) versus 0.13 (+/- 0.04),
-0.11 (+/- 0.03) versus 0.13 (+/- 0.05),
-0.13 (+/- 0.04) versus 0.17 (+/- 0.05),
-0.16 (+/- 0.04) versus 0.22 (+/- 0.05), and
-0.19 (+/- 0.05) versus 0.29 (+/- 0.06) across classes
+achieved a mean correlation $r$ of
+0.10 versus 0.13,
+0.11 versus 0.13,
+0.13 versus 0.17,
+0.16 versus 0.22, and
+0.19 versus 0.29 across classes
 based on 20\% to 100\% training data.
@@
     region and network emphasis.}
-    The relative impact of the region and network priors
-    on model selection
+    The relative strength of the region and network priors
+    on the regularization
     is systematically varied against each other
@@
 \end{figure*}
+
+%
+Three observations have been made.
+First,
+in the data-scarce scenario (i.e., 1/5 of available training data),
+hierarchical tree sparsity achieved the biggest advantage
+in out-of-sample performance by 5.1\% as well as
+better support recovery with weight maps already much closer
+to the respective class averages
+\cite{varoquaux2012small}.
+In the case of scarce training data, which is typical for the brain imaging domain,
+regularization by region-network priors thus allowed for
+more effective extraction of classification-relevant structure
+from the neural activity maps.
 \begin{table*}[]
@@
 \end{table*}
-
-%
-Three observations have been made.
-First,
-in the data-scarce scenario (i.e., 1/5 of available training data),
-hierarchical tree sparsity achieved the biggest advantage
-in out-of-sample performance by 5.1\% as well as
-better support recovery with weight maps already much closer
-to the respective class averages
-\cite{varoquaux2012small}.
-In the case of scarce training data, which is typical for the brain imaging domain,
-regularization by region-network priors thus allowed for
-more effective extraction of classification-relevant structure
-from the neural activity maps.
 %
@@
 suggests that \textit{class-specific region-network tradeoffs}
-enables more performant and more interpretable classification models
-for future neuroimaging analyses.
+enable more performant and more interpretable classification models
+for neuroimaging analyses.
 
